### 2020-02-06 README.Rmd
Packaging it into an R package.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oolong <img src="man/figures/oolong_logo.png" align="right" height="150" />

<!-- badges: start -->
<!-- badges: end -->

The goal of oolong (烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia. It is very popular in Taiwan, Japan and Hong Kong) is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chainsawriot/oolong")
```

## Example

`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm` and Wrap LDA models from `text2vec`.

```{r example}
library(oolong)
library(stm)
newsgroup_stm
```

To create an oolong test, use the function `create_oolong_test`.

```{r createtest}
oolong_test <- create_oolong(newsgroup_stm)
oolong_test
```

As instructed, use the method `$do_word_intrusion_test()` to start coding. If you are running this in RStudio, you should see a test screen similar to this:

<img src="man/figures/oolong_demo.gif" align="center" />

After the coding, you can look at the accuracy rate by printing the oolong test.

```{r, eval = FALSE}
oolong_test
```

### 2020-02-06 README.Rmd
Adjust the size of the logo.
experimetal examination of topic-intrusion

@@
 
-# oolong <img src="man/figures/oolong_logo.png" align="right" height="150" />
+# oolong <img src="man/figures/oolong_logo.png" align="right" height="200" />
 
@@
 
-The goal of oolong (烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia.
-It is very popular in Taiwan, Japan and Hong Kong) is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
+The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia.
+It is very popular in Taiwan, Japan and Hong Kong] is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
 

### 2020-02-06 topic.R

@@ -1,0 +1,43 @@
+require(oolong)
+require(tidyverse)
+require(stm)
+
+
+.sample_corpus <- function(corpus, exact_n = 30, frac = NULL) {
+    sample(seq_len(length(corpus)), exact_n)
+}
+
+.insert <- function(good_terms, intruder, position) {
+    length_test_items <- length(c(good_terms, intruder))
+    res <- rep(NA, length_test_items)
+    res[position] <- intruder
+    res[setdiff(1:length_test_items, position)] <- sample(good_terms)
+    return(tibble::tibble(position = position, candidates = list(res)))
+}
+
+.generate_topic_frame <- function(i, target_text, target_theta, model_terms, k = k, n_top_topics = 3, n_top_words = 8) {
+    text <- target_text[i]
+    theta_rank <- rank(target_theta[i,])
+    theta_pos <- which(theta_rank > (k - n_top_topics))
+    intruder_pos <- sample(setdiff(seq_len(k), theta_pos), 1)
+    position <- sample(seq_len(n_top_topics + 1), 1)
+    topic_frame <- .insert(theta_pos, intruder_pos, position)
+    topic_frame$text <- text
+    topic_frame$topic_labels <- list(apply(model_terms[topic_frame$candidates[[1]],], 1, paste0, collapse = ", "))
+    topic_frame$thetas <- list(target_theta[i, topic_frame$candidates[[1]]])
+    topic_frame$answer <- NA
+    colnames(topic_frame)[1] <- "intruder"
+    return(topic_frame)
+}
+
+.generate_topic_instrusion_test <- function(model, corpus, exact_n = 30, frac = NULL, n_top_topics = 3, n_top_words = 8, difficulty = 0.8) {
+    sample_vec <- .sample_corpus(corpus, exact_n)
+    model_terms <- stm::labelTopics(model, n = n_top_words, frexweight = difficulty)$frex
+    target_theta <- model$theta[sample_vec, ]
+    k <- ncol(target_theta)
+    target_text <- corpus[sample_vec]
+    test_content <- purrr::map_dfr(seq_len(exact_n), .generate_topic_frame, target_text = target_text, target_theta = target_theta, model_terms = model_terms, k = k, n_top_topics = n_top_topics, n_top_words = n_top_words)
+    return(test_content)
+}
+
+topic_test_content <- .generate_topic_instrusion_test(newsgroup_stm, newsgroup5$text)

### 2020-02-07 README.Rmd
Fix typos

@@
 The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia.
-It is very popular in Taiwan, Japan and Hong Kong] is to generate and adminstrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
+It is very popular in Taiwan, Japan and Hong Kong] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
 

### 2020-02-07 topic.R

@@ -15,6 +15,10 @@ require(stm)
     return(tibble::tibble(position = position, candidates = list(res)))
 }
 
+.get_intruder_by_position <- function(candidates, position) {
+    candidates[position]
+}
+
 .generate_topic_frame <- function(i, target_text, target_theta, model_terms, k = k, n_top_topics = 3, n_top_words = 8) {
     text <- target_text[i]
     theta_rank <- rank(target_theta[i,])
@@ -26,7 +30,7 @@ require(stm)
     topic_frame$topic_labels <- list(apply(model_terms[topic_frame$candidates[[1]],], 1, paste0, collapse = ", "))
     topic_frame$thetas <- list(target_theta[i, topic_frame$candidates[[1]]])
     topic_frame$answer <- NA
-    colnames(topic_frame)[1] <- "intruder"
+    topic_frame$intruder <- map2_int(topic_frame$candidates, topic_frame$position, .get_intruder_by_position)
     return(topic_frame)
 }
 

### 2020-02-07 README.Rmd
Add experimental support for topic intrusion tests

@@
 
+### Word intrusion test
+
 `newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package.
@@
 
-After the coding, you can look at the accuracy rate by printing the oolong test.
+After the coding, you can look at the model precision by printing the oolong test.
 
@@
 ```
+
+### Topic intrusion test
+
+For example, `newsgroup_stm` was generated with the corpus `newsgroup5$text`
+
+```{r newgroup5}
+library(tibble)
+newsgroup5
+```
+
+Create the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.
+
+```{r createtest2}
+oolong_test <- create_oolong(newsgroup_stm, newsgroup5$text)
+oolong_test
+```

### 2020-02-07 R/oolong.R

@@ -143,50 +143,6 @@
     return(test_content)
 }
 
-.do_oolong_test <- function(test_content) {
-    test_content$answer <- .code_oolong(test_content)
-    return(test_content)
-}
-
-Oolong_test <- R6::R6Class(
-    "oolong_test",
-    public = list(
-        initialize = function(model, n_top_terms = 5, bottom_terms_percentile = 0.6, difficulty = 0.8) {
-            private$test_content <- .generate_word_intrusion_test(model, n_top_terms = n_top_terms, bottom_terms_percentile = bottom_terms_percentile, difficulty = difficulty)
-            private$hash <- digest::digest(private$test_content, algo = "sha1")
-        },
-        print = function() {
-            cat(paste0("An oolong test object with k = ", nrow(private$test_content), ", ", sum(!is.na(private$test_content$answer)), " coded. (", round(.cal_oolong_correct(private$test_content), 3),"%  precision)\n Use the method $do_word_intrusion_test() to start word intrusion test.\n"))
-        },
-        do_word_intrusion_test = function() {
-            private$test_content <- .do_oolong_test(private$test_content)
-        }
-    ),
-    private = list(
-        hash = NULL,
-        test_content = NULL
-    )
-)
-
-#' Generate a oolong test for a topic model
-#'
-#' Currently, this function generates a oolong test object that contains a word intrusion test. Future version will provide additional tests such as topic intrusion test.
-#'
-#' @param model a STM or WrapLDA object
-#' @param n_top_terms integer, number of top topic words to be included in the candidates
-#' @param bottm_terms_percentile double, a term is considered to be an intruder when its theta less than the percentile of this theta, must be within the range of 0 to 1.
-#' @param difficulty double, to adjust the difficulty of the test. Higher value indicates higher difficulty, must be within the range of 0 to 1.
-#' @export
-create_oolong <- function(model, n_top_terms = 5, bottom_terms_percentile = 0.6, difficulty = 0.8) {
-    return(Oolong_test$new(model, n_top_terms, bottom_terms_percentile, difficulty))
-}
-
-
-#' Newsgroup text dataset
-#'
-#' This is a subset of the famous "newsgroup 20" dataset.
-"newsgroup5"
-
 
 .sample_corpus <- function(corpus, exact_n = 30, frac = NULL) {
     if (!is.null(frac)) {
[…]

### 2020-02-08 R/oolong.R
Implemented a rudimentary lock system.

@@ -187,10 +187,25 @@
     return(test_content)
 }
 
+### print the ... if boolean_test is true
+.cp <- function(boolean_test, ...) {
+    if (boolean_test) {
+        cat(paste0(..., "\n"))
+    }
+}
+
+### stop if boolean_test is true and print the ...
+.cstop <- function(boolean_test, ...) {
+    if (boolean_test) {
+        stop(...)
+    }
+}
+
 Oolong_test <- R6::R6Class(
     "oolong_test",
     public = list(
         initialize = function(model, corpus = NULL, n_top_terms = 5, bottom_terms_percentile = 0.6, exact_n = 15, frac = NULL, n_top_topics = 3, n_top_words = 8, difficulty = 0.8) {
+            ### TODO: spin off these to make it testable.
             private$test_content$word <- .generate_word_intrusion_test(model, n_top_terms = n_top_terms, bottom_terms_percentile = bottom_terms_percentile, difficulty = difficulty)
             if (is.null(corpus)) {
                 private$test_content$topic <- NULL
@@ -200,24 +215,36 @@ Oolong_test <- R6::R6Class(
             private$hash <- digest::digest(private$test_content, algo = "sha1")
         },
         print = function() {
-            cat(paste0("An oolong test object with k = ", nrow(private$test_content$word), ", ", sum(!is.na(private$test_content$word$answer)), " coded. (", round(.cal_oolong_correct(private$test_content$word), 3),"%  precision)\n Use the method $do_word_intrusion_test() to start word intrusion test.\n"))
-            if (!is.null(private$test_content$topic)) {
-                cat(paste0("With ", nrow(private$test_content$topic) , " cases of topic intrusion test. ", sum(!is.na(private$test_content$topic$answer)), " coded. Use the method $do_topic_intrusion_test() to start topic intrusion test.\n"))
-            }
+            .cp(TRUE, "An oolong test object with k = ", nrow(private$test_content$word), ", ", sum(!is.na(private$test_content$word$answer)), " coded.")
+            .cp(private$finalized, round(.cal_oolong_correct(private$test_content$word), 3),"%  precision")
+            .cp(!private$finalized, "Use the method $do_word_intrusion_test() to do word intrusion test.")
+            .cp(!is.null(private$test_content$topic), "With ", nrow(private$test_content$topic) , " cases of topic intrusion test. ", sum(!is.na(private$test_content$topic$answer)), " coded.")
[…]

### 2020-02-08 README.Rmd
Implemented a rudimentary lock system.
Added use_frex_words argument, fully compatible with Chang et al. fix #2

@@
 
-After the coding, you can look at the model precision by printing the oolong test.
+After the coding, you need to first finalize the test. Then, you can look at the model precision by printing the oolong test.
 
 ```{r, eval = FALSE}
+oolong_test$finalize()
 oolong_test
@@
 
-Create the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.
+Creating the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.
 

### 2020-02-09 R/oolong.R
finalize() is a reserved word for R6. Must change it to () to prevent future problem.

@@ -219,6 +219,10 @@
     return(test_content)
 }
 
+.check_test_content_complete <- function(test_content) {
+    all(purrr::map_lgl(test_content, ~all(!is.na(.$answer))))
+}
+
 Oolong_test <- R6::R6Class(
     "oolong_test",
     public = list(
@@ -232,14 +236,13 @@ Oolong_test <- R6::R6Class(
             .cp(!private$finalized, "Use the method $do_word_intrusion_test() to do word intrusion test.")
             .cp(!is.null(private$test_content$topic), "With ", nrow(private$test_content$topic) , " cases of topic intrusion test. ", sum(!is.na(private$test_content$topic$answer)), " coded.")
             .cp(!is.null(private$test_content$topic) & !private$finalized, "Use the method $do_topic_intrusion_test() to do topic intrusion test.")
-            .cp(!private$finalized, "Use the method $finalize() to finalize this object and see the results.")
+            .cp(!private$finalized, "Use the method $lock() to finalize this object and see the results.")
         },
-        finalize = function(force = FALSE) {
-            ### TODO, implement force
+        lock = function(force = FALSE) {
+            if (!.check_test_content_complete(private$test_content) & !force) {
+                stop("Not all tests are completed. Do all the tests or use $lock(force = TRUE) to bypass this.")
+            }
             private$finalized <- TRUE
-        },
-        finalise = function() {
-            self$finalize()
         },
         do_word_intrusion_test = function() {
             private$check_finalized()

### 2020-02-09 tests/testthat/test-generate_test_content.R

@@ -1,6 +1,23 @@
+context("check helper functions")
+
 test_that("generate_test_content", {
     x <- oolong:::.generate_test_content(newsgroup_stm)
     expect_null(x$topic)
     x <- oolong:::.generate_test_content(newsgroup_stm, quanteda::corpus(newsgroup5$text))
     expect_false(is.null(x$topic))
+})
+
+test_that("check_complete", {
+    x <- oolong:::.generate_test_content(newsgroup_stm)
+    expect_false(oolong:::.check_test_content_complete(x))
+    x$word$answer <- 1
+    expect_true(oolong:::.check_test_content_complete(x))
+    y <- oolong:::.generate_test_content(newsgroup_stm, newsgroup5$text)
+    expect_false(oolong:::.check_test_content_complete(y))
+    y$topic$answer <- 1
+    expect_false(oolong:::.check_test_content_complete(y))
+    y$word$answer <- 1
+    expect_true(oolong:::.check_test_content_complete(y))
+    z <- create_oolong(newsgroup_stm)
+    expect_error(z$lock())
 })

### 2020-02-09 README.Rmd
finalize() is a reserved word for R6. Must change it to () to prevent future problem.
calculate TLO, fix #4

@@
 
-After the coding, you need to first finalize the test. Then, you can look at the model precision by printing the oolong test.
+After the coding, you need to first lock the test. Then, you can look at the model precision by printing the oolong test.
 
 ```{r, eval = FALSE}
-oolong_test$finalize()
+oolong_test$lock()
 oolong_test
@@
 ```
+
+Similarly, use the `$do_topic_intrusion_test` to code the test cases, lock the test with `$lock()` and then you can look at the TLO (topic log odds) value by printing the oolong test.
+
+```{r, eval = FALSE}
+oolong_test$lock()
+oolong_test
+```
+
+## References
+
+1.
+Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J.
+L., & Blei, D.
+M.
+(2009).
+Reading tea leaves: How humans interpret topic models.
+In Advances in neural information processing systems (pp.
+288-296).

### 2020-02-10 README.Rmd
Support Warp LDA and correct all typos of 'WrapLDA'. fix #3

@@
 `newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm` and Wrap LDA models from `text2vec`.
+Currently, this package supports structural topic models / correlated topic models from `stm` and Warp LDA models from `text2vec`.
 
@@
 
+## About Warp LDA
+
+There is a subtle difference between the support for `stm` and for `text2vec`.
+
+`newsgroup_warplda` is a Warp LDA object trained with the same dataset as the `newsgroup_stm`
+
+```{r warplda}
+newsgroup_warplda
+```
+
+All the API endpoints are the same, except the one for the creation of topic intrusion test cases. You must supply also the `input_dfm`.
+
+```{r warplda2}
+### Just word intrusion test.
+oolong_test <- create_oolong(newsgroup_warplda)
+oolong_test
+```
+
+```{r warplda3}
+newsgroup5_dfm
+```
+
+```{r warplda4}
+oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
+oolong_test
+```
+
 ## References
@@
 288-296).
+
+---

### 2020-02-10 README.Rmd
Partial version of summarize_oolong

@@
 
+## Suggested workflow
+
+The test makes more sense if more than one coder is involved.
+A suggested workflow is to create the test, then clone the oolong object.
+Ask multiple coders to do the test(s) and then summarize the results.
+
+Create a new oolong object.
+
+```{r step1}
+oolong_test_rater1 <- create_oolong(newsgroup_stm)
+```
+
+Clone the oolong object to be used by other raters.
+
+```{r step2}
+oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
+```
+
+Ask different coders to code each object and then lock the object.
+
+```{r, eval = FALSE}
+## Let rater 1 do the test.
+oolong_test_rater1$do_word_intrusion_test()
+oolong_test_rater1$lock()
+
+## Let rater 2 do the test.
+oolong_test_rater2$do_word_intrusion_test()
+oolong_test_rater2$lock()
+```
+
+```{r, include = FALSE}
+### Mock this process
+oolong_test_rater1$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater1$.__enclos_env__$private$test_content$word$intruder
+oolong_test_rater1$lock()
+oolong_test_rater2$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater2$.__enclos_env__$private$test_content$word$intruder
+oolong_test_rater2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
+oolong_test_rater2$lock()
+```
+
+Get a summary of the two objects.
+
+```{r, step3}
+summarize_oolong(oolong_test_rater1, oolong_test_rater2)
+```
+
 ## About Warp LDA

### 2020-02-10 tests/testthat/test-warplda.R

@@ -8,3 +8,4 @@ test_that("generate_test_content", {
     x <- oolong:::.generate_test_content(newsgroup_warplda, quanteda::corpus(newsgroup5$text), input_dfm = newsgroup5_dfm)
     expect_true(!is.null(x$topic))
 })
+

### 2020-02-11 README.Rmd
summarize_oolong is ready, fix #6. First minor version.

@@
   )
+set.seed(42)
 ```
@@
 
-As instructed, use the method `$do_word_intrusion_test()` to start coding. If you are running this in RStudio, you should see a test screen similar to this:
+As instructed, use the method `$do_word_intrusion_test()` to start coding.
+
+```{r, eval = FALSE}
+oolong_test$do_word_intrusion_test()
+```
+
+If you are running this in RStudio, you should see a test screen similar to this:
 
@@
 
-```{r, eval = FALSE}
+```{r, include = FALSE}
+### Mock this process
+oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
+oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
+```
+
+```{r lock}
 oolong_test$lock()
@@
 ```{r, eval = FALSE}
+oolong_test$do_topic_intrusion_test()
 oolong_test$lock()
+```
+
+```{r, include = FALSE}
+genius_topic <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    return(obj1)
+}
+genius_word <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    return(obj1)
+}
+oolong_test <- genius_word(genius_topic(oolong_test))
+oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
+oolong_test$lock()
+```
+
+```{r topic_res}
 oolong_test
@@
 Ask multiple coders to do the test(s) and then summarize the results.
+
+Train a topic model.
+
+```{r step0, eval = FALSE}
+require(quanteda)
+require(stm)
+dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
+docvars(newsgroup5_dfm, "title") <- newsgroup5$title
+newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
+newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
+```
 

### 2020-02-11 R/oolong_summary.R

@@ -62,9 +62,20 @@ summarize_oolong <- function(...) {
     all_word_answers <- purrr::map_dfc(obj_list, ~ .$.__enclos_env__$private$test_content$word$answer)
     word_intruder <- obj_list[[1]]$.__enclos_env__$private$test_content$word$intruder
     correction_matrix <- all_word_answers == word_intruder
-    ##res$kripp_alpha <- irr::kripp.alpha(t(ifelse(correction_matrix, 2, 1)))$value
+    if (length(obj_list) == 1) {
+        res$kripp_alpha <- NA
+    } else {
+        res$kripp_alpha <- irr::kripp.alpha(t(ifelse(correction_matrix, 2, 1)))$value
+    }
     res$k_precision <- apply(correction_matrix, 1, sum) / ncol(correction_matrix)
     res$rater_precision <- as.vector(apply(correction_matrix, 2, sum) / nrow(correction_matrix))
+    res$n_models <- length(obj_list)
+    all_topic_test_content <- purrr::map(obj_list, ~ .$.__enclos_env__$private$test_content$topic)
+    if (any(purrr::map_lgl(all_topic_test_content, is.null))) {
+        res$tlo <- NA
+    } else {
+        res$tlo <- .cal_tlo(purrr::map_dfr(all_topic_test_content, ~.), mean_value = FALSE) ### it should not be just the mean.
+    }
     class(res) <- append(class(res), "oolong_summary")
     return(res)
 }
@@ -72,7 +83,9 @@ summarize_oolong <- function(...) {
 #' @export
 print.oolong_summary <- function(oolong_summary) {
     .cp(TRUE, "Mean model precision: ", mean(oolong_summary$rater_precision))
-    .cp(TRUE, "Quantiles of Model precision: ", paste(quantile(oolong_summary$rater_precision), collapse = ", "))
-    ##.cp(TRUE, "Krippendorf's alpha: ", oolong_summary$kripp_alpha)
+    .cp(oolong_summary$n_models > 1, "Quantiles of Model precision: ", paste(quantile(oolong_summary$rater_precision), collapse = ", "))
+    .cp(oolong_summary$n_models > 1, "Krippendorff's alpha: ", oolong_summary$kripp_alpha)
     .cp(TRUE, "K Precision: ", paste(round(oolong_summary$k_precision, 1), collapse = ", "))
[…]

### 2020-02-11 tests/testthat/test-multiple_objs.R

@@ -1,21 +1,43 @@
 context("check_correctness")
-test_that("check_calculation", {
+
+genius_word <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    return(obj1)
+}
+
+genius_topic <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    return(obj1)
+}
+
+test_that("defensive programming", {
+    obj1 <- create_oolong(newsgroup_stm)
+    obj2 <- clone_oolong(obj1)
+    ### Not lock
+    expect_error(summarize_oolong(obj1))
+    obj1 <- genius_word(obj1)
+    obj1$lock()
+    ### Obj2 is not lock
+    expect_error(summarize_oolong(obj1, obj2))
+})
+
+test_that("check_calculation_word_intrusion", {
     obj1 <- create_oolong(newsgroup_stm)
     obj2 <- clone_oolong(obj1)
     obj3 <- clone_oolong(obj1)
     ## Mocking coding
-
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1 <- genius_word(obj1)
     obj1$lock()
-    obj2$.__enclos_env__$private$test_content$word$answer <- obj2$.__enclos_env__$private$test_content$word$intruder
+    obj2 <- genius_word(obj2)
     obj2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
-obj2$lock()
-    obj3$.__enclos_env__$private$test_content$word$answer <- obj3$.__enclos_env__$private$test_content$word$intruder
+    obj2$lock()
+    obj3 <- genius_word(obj3)
     obj3$.__enclos_env__$private$test_content$word$answer[1:4] <- "wronganswer"
     obj3$lock()
     res <- summarize_oolong(obj1, obj2, obj3)
     expect_length(res$rater_precision, 3)
     expect_length(res$k_precision, 10)
+    ### Single object
     res <- summarize_oolong(obj1)
     expect_length(res$rater_precision, 1)
 })

### 2020-02-11 newsgroup.R
added support for topicmodels. ref #5

@@ -3,6 +3,7 @@ require(quanteda)
 require(stm)
 require(oolong)
 
+
 ##newsgroup <- rio::import("20_newsgroup.csv") %>% as_tibble
 
 ## set.seed(42)
@@ -33,3 +34,24 @@ newsgroup_warplda <- lda_model
 
 
 usethis::use_data(newsgroup_warplda)
+
+###
+require(topicmodels)
+
+newsgroup5_tm <- convert(newsgroup5_dfm, to = "topicmodels")
+
+newsgroup_lda <- LDA(newsgroup5_tm, k = 10)
+
+saveRDS(newsgroup_lda, "newsgroup_topicmodels.RDS")
+
+terms(newsgroup_lda)
+
+K <- newsgroup_lda@k
+theta <- posterior(newsgroup_lda)$topic
+V <- length(newsgroup_lda@terms)
+
+
+####
+devtools::load_all()
+
+oolong_test <- create_oolong(newsgroup_topicmodels)

### 2020-02-13 README.Rmd
added support for topicmodels. ref #5
Fixed a inconsistency in README.Rmd
Providing statistical test for median TLO, fix #7

@@
 `newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm` and Warp LDA models from `text2vec`.
+Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.
 
@@
 ```{r step1}
-oolong_test_rater1 <- create_oolong(newsgroup_stm)
+oolong_test_rater1 <- create_oolong(newsgroup_stm, newsgroup5$text)
 ```
@@
 oolong_test_rater1$do_word_intrusion_test()
+oolong_test_rater1$do_topic_intrusion_test()
 oolong_test_rater1$lock()
@@
 oolong_test_rater2$do_word_intrusion_test()
+oolong_test_rater2$do_topic_intrusion_test()
 oolong_test_rater2$lock()
@@
 ### Mock this process
-oolong_test_rater1$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater1$.__enclos_env__$private$test_content$word$intruder
+set.seed(46709394)
+oolong_test_rater1 <- oolong:::.monkey_test(oolong_test_rater1, intelligent = 0.3)
+oolong_test_rater2 <- oolong:::.monkey_test(oolong_test_rater2, intelligent = 0)
 oolong_test_rater1$lock()
-oolong_test_rater2$.__enclos_env__$private$test_content$word$answer <- oolong_test_rater2$.__enclos_env__$private$test_content$word$intruder
-oolong_test_rater2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
 oolong_test_rater2$lock()
@@
 ```
+
+## About the p-values
+
+The test for model precision (MP) is based on the one-tailed, one-sample binomial test for each rater.
+In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a.
+Fisher's omnibus test).
+
+H0: MP is not better than 1/ n\_top\_terms
+
+H1: MP is better than 1/ n\_top\_terms
+
+The test for the median of TLO is based on a resampling under the null hypothesis method.
+
+H0: Median TLO is not better than random guess.
+
+H1: Median TLO is better than random guess.
+
+One must notice that the two statistical tests are testing the bear minimum.
+A significant test only indicates the topic model performs better than random guess.
+It is not an indication of good topic interpretability.
+Also, one should use a very conservative significant level, e.g.
+$\alpha < 0.001$.
 

### 2020-02-13 tests/testthat/test-multiple_objs.R

@@ -60,8 +60,4 @@ test_that("check_calculation_word_intrusion", {
     ### Single object
     res <- summarize_oolong(obj1)
     expect_length(res$rater_precision, 1)
-    res <- summarize_oolong(obj1, obj2, obj3)
-    res2 <- summarise_oolong(obj1, obj2, obj3)
-    expect_equal(res, res2)
 })
-

### 2020-02-14 README.Rmd
fix the description of TLO test in README. fixes #9

@@
 
-The test for model precision (MP) is based on the one-tailed, one-sample binomial test for each rater.
+The test for model precision (MP) is based on an one-tailed, one-sample binomial test for each rater.
 In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a.
@@
 
-The test for the median of TLO is based on a resampling under the null hypothesis method.
+The test for the median of TLO is based on a permutation test.
 
@@
 One must notice that the two statistical tests are testing the bear minimum.
-A significant test only indicates the topic model performs better than random guess.
+A significant test only indicates the topic model can make the rater(s) perform better than random guess.
 It is not an indication of good topic interpretability.

### 2020-02-14 README.Rmd
Reformat README to cater for the future addition of content about validating dictionary-based methods
Make create_oolong die when input_model and input_corpus are NULL.

@@
 
+The validation test is called "oolong test" (for reading tea leaves).
+Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`.
+The most important parameters are `input_model` and `input_corpus`.
+Setting each of them to `NULL` generates different tests.
+
+| input\_model | input\_corpus | output                                                                          |
+|--------------|:-------------:|---------------------------------------------------------------------------------|
+| Not NULL     | NULL          | oolong test for a topic model with word intrusion test                          |
+| Not NULL     | Not NULL      | oolong test for a topic model with word intrusion test and topic intrusion test |
+| NULL         | Not NULL      | oolong test for creating gold standard                                          |
+| NULL         | NULL          | error                                                                           |
+
 ## Installation
@@
 
-## Example
+## Validating Topic Models
 
-### Word intrusion test
+#### Word intrusion test
 
@@
 
-### Topic intrusion test
+#### Topic intrusion test
 
@@
 
-## Suggested workflow
+### Suggested workflow
 
@@
 
-## About the p-values
+### About the p-values
 
@@
 
-## About Warp LDA
+### About Warp LDA
 
@@
 
+## Validating Dictionary-based Methods
+
+### Creating gold standard
+
+`trump2k` is a dataset of 2,000 tweets from @realdonaldtrump.
+
 ## References

### 2020-02-14 R/oolong.R

@@ -43,6 +43,9 @@ Oolong_test <- R6::R6Class(
 #' @param input_dfm a dfm object used for training the input_model, if input_model is a WarpLDA object
 #' @export
 create_oolong <- function(input_model = NULL, input_corpus = NULL, n_top_terms = 5, bottom_terms_percentile = 0.6, exact_n = NULL, frac = 0.01, n_top_topics = 3, n_topiclabel_words = 8, use_frex_words = FALSE, difficulty = 1, input_dfm = NULL, target_value = NULL, construct = "positive") {
+    if (is.null(input_model) & is.null(input_corpus)) {
+        stop("input_model and input_corpus cannot be both NULL.")
+    }
     if (!is.null(input_model)) {
         return(Oolong_test_tm$new(input_model = input_model, input_corpus = input_corpus, n_top_terms = n_top_terms, bottom_terms_percentile = bottom_terms_percentile, exact_n = exact_n, frac = frac, n_top_topics = n_top_topics, n_topiclabel_words = n_topiclabel_words, difficulty = difficulty, use_frex_words = use_frex_words, input_dfm = input_dfm))
     } else {

### 2020-02-14 tests/testthat/test-defensive_programming.R

@@ -10,6 +10,10 @@ genius_topic <- function(obj1) {
     return(obj1)
 }
 
+test_that("precondiction", {
+    expect_error(create_oolong())
+    expect_error(create_oolong(input_model = NULL, input_corpus = NULL))
+})
 
 test_that("locking", {
     ## premature locking

### 2020-02-14 README.Rmd
Reorganizing README

@@
 | input\_model | input\_corpus | output                                                                                                                           |
-|--------------|:-------------:|---------------------------------------------------------------------------------|
-| Not NULL     | NULL          | oolong test for a topic model with word intrusion test                          |
-| Not NULL     | Not NULL      | oolong test for a topic model with word intrusion test and topic intrusion test |
-| NULL         | Not NULL      | oolong test for creating gold standard                                          |
+|--------------|:-------------:|----------------------------------------------------------------------------------------------------------------------------------|
+| Not NULL     | NULL          | oolong test for a topic model with [word intrusion test](#word-intrusion-test)                                                   |
+| Not NULL     | Not NULL      | oolong test for a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
+| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                |
 | NULL         | NULL          | error                                                                                                                            |

### 2020-02-14 README.Rmd
Make the grammar in README great again.

--- 2020-02-14 README.Rmd
@@
 | input\_model | input\_corpus | output                                                                                                                                      |
-|--------------|:-------------:|---------------------------------------------------------------------------------|
-| Not NULL     | NULL          | oolong test for a topic model with word intrusion test                          |
-| Not NULL     | Not NULL      | oolong test for a topic model with word intrusion test and topic intrusion test |
-| NULL         | Not NULL      | oolong test for creating gold standard                                          |
+|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
+| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
+| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
+| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
 | NULL         | NULL          | error                                                                                                                                       |

### 2020-02-14 README.Rmd
Rudimentary support for validting dictionary-based methods

@@
 
+```{r trump2k}
+tibble(text = trump2k)
+```
+
+For example, you are interested in studying the sentiment of these tweets.
+One can use tools such as AFINN to automatically extract sentiment in these tweets.
+However, oolong recommends to generate gold standard by human coding first using a subset.
+By default, oolong selects 1% of the origin corpus as test cases.
+The parameter `construct` should be an adjective, e.g.
+positive, liberal, populistic, etc.
+
+```{r goldstandard}
+oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive")
+oolong_test
+```
+
+As instructed, use the method `$do_gold_standard_test()` to start coding.
+
+```{r, eval = FALSE}
+oolong_test$do_gold_standard_test()
+```
+
+The test screen should be similar to this:
+
+<img src="man/figures/trump_coding.png" align="center" />
+
+After the coding, you need to first lock the test and then the `$turn_gold()` method is available.
+
+```{r, include = FALSE}
+oolong_test <- readRDS("trump_coded.RDS")
+```
+
+```{r gs_locking}
+oolong_test$lock()
+oolong_test
+```
+
+A locked oolong test can be converted into a quanteda corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.
+
+```{r}
+oolong_test$turn_gold()
+```
+
+```{r}
+require(quanteda)
+require(dplyr)
+gold_standard <- oolong_test$turn_gold()
+dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>% mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1) + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5), base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>% pull(afinn_score) -> all_afinn_score
+all_afinn_score
+```
+
+```{r}
+cor(all_afinn_score, docvars(gold_standard, "answer"))
+```
+
+```{r cor_afinn}
+plot( docvars(gold_standard, "answer"), all_afinn_score)
+```
+
+Future version will provide `summarize_oolong` to summarize multiple oolong objects and simplify the validation process.
+
 ## References

### 2020-02-14 trump.R

@@ -1,6 +1,6 @@
 devtools::load_all()
 
-oolong_test <- create_oolong(input_corpus = trump2k, exact_n = 5, construct = "positive")
+oolong_test <- create_oolong(input_corpus = trump2k, exact_n = 20, construct = "positive")
 
 require(quanteda)
 

### 2020-02-14 R/oolong_dictionary.R
Hijack the quanteda::corpus object

@@ -60,7 +60,15 @@
     res <- quanteda::corpus(test_content$gold_standard$text)
     quanteda::docvars(res, "answer") <- test_content$gold_standard$answer
     quanteda::docvars(res, "target_value") <- test_content$gold_standard$target_value
+    class(res) <- append("oolong_gold_standard", class(res))
     return(res)
+}
+
+
+#' @export
+print.oolong_gold_standard <- function(obj) {
+    quanteda:::print.corpus(obj)
+    .cp(TRUE, "Access the answer from the coding with quanteda::docvars(obj, 'answer')")
 }
 
 Oolong_test_gs <-

### 2020-02-14 README.Rmd
Hijack the quanteda::corpus object
Streamline the validation process

@@
 
-A locked oolong test can be converted into a quanteda corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.
+A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.
 
@@
 gold_standard <- oolong_test$turn_gold()
-dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>% mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1) + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5), base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>% pull(afinn_score) -> all_afinn_score
+dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
+    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
+           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
+           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
+    pull(afinn_score) -> all_afinn_score
 all_afinn_score
@@
 ```{r}
-cor(all_afinn_score, docvars(gold_standard, "answer"))
-```
-
-```{r cor_afinn}
-plot( docvars(gold_standard, "answer"), all_afinn_score)
+docvars(gold_standard, "target_value") <- all_afinn_score
+summarize_gold_standard(gold_standard)
 ```

### 2020-02-14 R/oolong_dictionary.R

@@ -69,6 +69,15 @@
 print.oolong_gold_standard <- function(obj) {
     quanteda:::print.corpus(obj)
     .cp(TRUE, "Access the answer from the coding with quanteda::docvars(obj, 'answer')")
+    .cp(TRUE, "Put back the test score you would like to validate into quanteda::docvars(obj, 'target_value')")
+}
+
+#' @export
+summarize_gold_standard <- function(obj) {
+    if (all(is.na(quanteda::docvars(obj, "target_value")))) {
+        stop("target_value is not available.")
+    }
+    cor(quanteda::docvars(obj, "target_value"), quanteda::docvars(obj, "answer"))
 }
 
 Oolong_test_gs <-

### 2020-02-14 README.Rmd
Better clarification of the validation process.

@@
 
+### Example: Validating AFINN using the gold standard
+
 A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.
@@
 ```
+
+As instructed, put back the score you would like to validate into the `docvars` "target_value".
+In this example, we calculate the AFINN score for each tweet using quanteda.
+The dictionary `afinn` is bundle with this package.
 
@@
 ```
+
+Put back the vector of AFINN score into the respective `docvars` and study the correlation between the gold standard and AFINN.
 

### 2020-02-14 README.Rmd
Updating

@@
 
+### Inadvisable workflow
+
+*NOTE: This workflow is not recommended!*
+
+This workflow violates the "validation first" principle. You can supply the `target_value` at the creation of oolong test.
+
+```{r}
+dfm(trump2k, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
+    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
+           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
+           base = ntoken(trump2k, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
+    pull(afinn_score) -> trump2k_afinn_score
+oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive", target_value = trump2k_afinn_score)
+oolong_test
+```
+
+```{r, eval = FALSE}
+oolong_test$do_gold_standard_test()
+```
+
+```{r, include = FALSE}
+oolong_test$.__enclos_env__$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
+```
+
+```{r}
+oolong_test$lock()
+oolong_test$
+```
+
 ## References

### 2020-02-17 README.Rmd
unfinished summary_dictionary

@@
 
-```{r example}
+```{r echo = FALSE}
 library(oolong)
 library(stm)
+library(quanteda)
+library(dplyr)
+```
+
+```{r example}
 newsgroup_stm
@@
 ```{r step0, eval = FALSE}
-require(quanteda)
-require(stm)
 dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
@@
 ```{r}
-require(quanteda)
-require(dplyr)
 gold_standard <- oolong_test$turn_gold()
@@
 
+```{r, include = FALSE}
+set.seed(46709394)
+```
+
 ```{r}
@@
 ```{r, include = FALSE}
-oolong_test$.__enclos_env__$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
+oolong_test$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
 ```
@@
 oolong_test$lock()
-oolong_test$
+gold_standard <- oolong_test$turn_gold()
+docvars(gold_standard, "target_value")
+```
+
+```{r}
+summarize_gold_standard(gold_standard)
 ```

### 2020-02-17 oolong_summary_dictionary.R

@@ -1,0 +1,54 @@
+devtools::load_all()
+
+summarize_oolong_diction <- function(...) {
+    obj_list <- list(...)
+    answers <- purrr::map_dfc(obj_list, ~.$.__enclos_env__$private$test_content$gold_standard$answer)
+    colnames(answers) <- paste0("answer", seq_len(ncol(answers)))
+    avg_answer <- apply(answers, 1, mean)
+    answers$avg_answer <- avg_answer
+    return(answers)
+}
+
+trump <- create_oolong(input_corpus = trump2k)
+trump2 <- clone_oolong(trump)
+
+.monkey_dictionary <- function(oolong, n = 20) {
+    oolong$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, size = n, replace = TRUE)
+    return(oolong)
+}
+
+trump <- .monkey_dictionary(trump)
+trump2 <- .monkey_dictionary(trump2)
+
+
+trump$lock()
+trump2$lock()
+
+gold_standard <- trump$turn_gold()
+
+dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
+    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
+           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
+           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
+    pull(afinn_score) -> target_value
+
+answers <- summarize_oolong_diction(trump, trump2)
+
+require(ggplot2)
+
+tibble(target_value, avg_answer = answers$avg_answer) %>% mutate(minmax_target = (target_value - min(target_value)) / (max(target_value) - min(target_value)), minmax_answer = (avg_answer - min(avg_answer)) / (max(avg_answer) - min(avg_answer))) %>% ggplot(aes(x = minmax_target, y = minmax_answer)) + geom_point() + geom_smooth(method = lm)
+
+### Correlation
[…]

### 2020-02-18 README.Rmd
Summary for gs oolongs

@@
 
-```{r warplda4}
+```{r warplda4, eval = FALSE}
 oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
@@
 
-Future version will provide `summarize_oolong` to summarize multiple oolong objects and simplify the validation process.
+### Suggested workflow
+
+Create an oolong object, clone it for another coder.
+
+```{r}
+trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
+trump2 <- clone_oolong(trump)
+```
+
+Instruct two coders to code the tweets and lock the objects.
+
+```{r, eval = FALSE}
+trump$do_gold_standard_test()
+trump2$do_gold_standard_test()
+trump$lock()
+trump2$lock()
+```
+
+```{r, include = FALSE}
+trump_coded <- readRDS("trump_eval.RDS")
+trump <- trump_coded[[1]]
+trump2 <- trump_coded[[2]]
+```
+
+Calculate the target value (in this case, the AFINN score) by turning one object into a corpus.
+
+```{r}
+gold_standard <- trump$turn_gold()
+dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
+    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
+           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
+           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
+    pull(afinn_score) -> target_value
+```
+
+Summarize all oolong objects with the target value.
+
+```{r}
+res <- summarize_oolong_gold_standard(trump, trump2, target_value = target_value)
+```
+
+Read the results. The diagnostic plot consists of 4 subplots.
+
+* Subplot (top left): Raw correction between human judgement and target value. One should want to have a good correlation between the two.
+* Subplot (top right): Bland-Altman plot.
+One should want to have no correlation.
+Also, the dots should be randomly scattering around the mean value.
+If it is so, the two measurements (human judgement * and target value) are in good agreement.
+* Subplot (bottom left): Raw correlation between target value and content length. One should want to have no correlation, as an indication of good reliability against the influence of content length.
+* Subplot (bottom right): Cook's distance of all data point.
+One should want to have no dot (or at least very few dots) above the threshold.
+It is an indication of how the raw correction between human judgement and target value can or cannot be influenced by extreme values in your data.
+
+The textual output contains the Krippendorff's alpha of the codings by your raters.
+In order to claim validity of your target value, you must first establish the reliability of your gold standard.
+(See Song et al.
+[Forthcoming])
+
+```{r}
+res
+```
 
@@
 
-```{r}
+```{r diagnosis}
 summarize_gold_standard(gold_standard)
@@
 288-296).
+2.
+Song et al.
+(2020) In validations we trust?
+The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis.
+Political Communication.
+[link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
+3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
 

### 2020-02-18 R/oolong_summary_dictionary.R

@@ -1,0 +1,73 @@
+.minmax <- function(x) {
+    (x - min(x)) / (max(x) - min(x)) 
+}
+
+.corr_plot <- function(answers, target_value) {
+    tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer)) %>% ggplot2::ggplot(ggplot2::aes(x = avg_answer, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Human judgement") + ggplot2::ylab("Target value") -> correlation_plot
+    return(correlation_plot)
+}
+
+.ba_plot <- function(answers, target_value) {
+    plot_data <- tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer))
+    plot_data$diffxy <- plot_data$target_value - plot_data$avg_answer
+    plot_data$meanxy <- (plot_data$target_value + plot_data$avg_answer) / 2
+    mean_diff_xy <- mean(plot_data$diffxy)
+    sd_diff_xy <- sd(plot_data$diffxy)
+    ggplot2::ggplot(plot_data, ggplot2::aes(x = meanxy, y = diffxy)) + ggplot2::geom_point() + ggplot2::geom_hline(yintercept = mean_diff_xy) + ggplot2::geom_hline(yintercept = mean_diff_xy - 1.96 * sd_diff_xy, linetype = 2) + ggplot2::geom_hline(yintercept = mean_diff_xy + 1.96 * sd_diff_xy, linetype = 2) + ggplot2::xlab("Mean of two values") + ggplot2::ylab("Difference between two values")
+}
+
+.length_plot <- function(oolong, target_value, ...) {
+    gold <- oolong$turn_gold()
+    nwords <- ntoken(gold, ...)
+    plot_data <- tibble::tibble(target_value = .minmax(target_value), word_length = nwords)
+    ggplot2::ggplot(plot_data, ggplot2::aes(x = word_length, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Number of words") + ggplot2::ylab("Target value")
+}
+
+.cook_plot <- function(answers, target_value) {
+    lmobj <- lm(answers$avg_answer ~ target_value)
+    cutoff <- 4 / (length(target_value) - 2 - 1)
[…]

### 2020-02-18 README.Rmd
Fixed a stupid typo in README

@@
 
-* Subplot (top left): Raw correction between human judgement and target value. One should want to have a good correlation between the two.
+* Subplot (top left): Raw correlation between human judgement and target value. One should want to have a good correlation between the two.
 * Subplot (top right): Bland-Altman plot.
@@
 If it is so, the two measurements (human judgement * and target value) are in good agreement.
-* Subplot (bottom left): Raw correlation between target value and content length. One should want to have no correlation, as an indication of good reliability against the influence of content length.
+* Subplot (bottom left): Raw correlation between target value and content length.
+One should want to have no correlation, as an indication of good reliability against the influence of content length.
+(See Chan et al.)
 * Subplot (bottom right): Cook's distance of all data point.
@@
 3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
+4. Chan et al. (2020) It is not listed here, because it is still under review.
 

### 2020-02-18 README.Rmd
Fix the typos
Make Song's suggestions more prominent.

@@
 
-Create an oolong object, clone it for another coder.
+Create an oolong object, clone it for another coder. According to Song et al. (Forthcoming), you should at least draw 1% of your data.
 
@@
 
-Read the results. The diagnostic plot consists of 4 subplots.
+Read the results. The diagnostic plot consists of 4 subplots. It is a good idea to read Bland & Altman (1986) on the difference between correlation and agreement.
 
@@
 Also, the dots should be randomly scattering around the mean value.
-If it is so, the two measurements (human judgement * and target value) are in good agreement.
+If it is so, the two measurements (human judgement and target value) are in good agreement.
 * Subplot (bottom left): Raw correlation between target value and content length.
@@
 In order to claim validity of your target value, you must first establish the reliability of your gold standard.
-(See Song et al.
-[Forthcoming])
+Song et al.
+[Forthcoming] suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.
 
@@
 3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
-4. Chan et al. (2020) It is not listed here, because it is still under review.
+4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!
 

### 2020-02-19 README.Rmd
More stupid typos
Clean up the UI
Clean up the UI

@@
 
-```{r warplda4, eval = FALSE}
+```{r warplda4}
 oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
@@
 ```{r}
-res <- summarize_oolong_gold_standard(trump, trump2, target_value = target_value)
+res <- summarize_oolong(trump, trump2, target_value = target_value)
 ```
@@
 One should want to have no dot (or at least very few dots) above the threshold.
-It is an indication of how the raw correction between human judgement and target value can or cannot be influenced by extreme values in your data.
+It is an indication of how the raw correlation between human judgement and target value can or cannot be influenced by extreme values in your data.
 
@@
 res
+```
+
+```{r diagnosis}
+plot(res)
 ```
@@
 
-```{r diagnosis}
+```{r}
 summarize_gold_standard(gold_standard)

### 2020-02-19 R/oolong_summary.R

@@ -1,103 +1,25 @@
-.check_hash_dot <- function(...) {
-    length(unique(purrr::map_chr(list(...), ~ .$.__enclos_env__$private$hash))) == 1
-}
-
-.check_lock_dot <- function(...) {
-    all(purrr::map_lgl(list(...), ~ .$.__enclos_env__$private$finalized))
-}
-
-
-.check_finished <- function(oolong) {
-    if (!is.null(oolong$.__enclos_env__$private$test_content$word) & any(is.na(oolong$.__enclos_env__$private$test_content$word$answer))) {
-        return(FALSE)
-    }
-    if (!is.null(oolong$.__enclos_env__$private$test_content$topic) & any(is.na(oolong$.__enclos_env__$private$test_content$topic$answer))) {
-        return(FALSE)
-    }
-    return(TRUE)
-}
-
-.check_finished_dot <- function(...) {
-    all(purrr::map_lgl(list(...), ~ .check_finished(.)))
-}
-
-### check whether the oolong object is in a new state. (i.e. Not yet coded in either word and topic tests.)
-.check_new <- function(oolong) {
-    word_clean <- is.null(oolong$.__enclos_env__$private$test_content$word) | (!is.null(oolong$.__enclos_env__$private$test_content$word) & all(is.na(oolong$.__enclos_env__$private$test_content$word$answer)))
-    topic_clean <- is.null(oolong$.__enclos_env__$private$test_content$topic) | (!is.null(oolong$.__enclos_env__$private$test_content$topic) & all(is.na(oolong$.__enclos_env__$private$test_content$topic$answer)))
-    return(word_clean & topic_clean)
-}
-
-#' Clone a oolong object.
-#'
-#' Clone a new oolong object. The oolong must not be locked and ever coded.
-#' @param oolong an oolong object.
-#' @export
-clone_oolong <- function(oolong) {
-    if (oolong$.__enclos_env__$private$finalized) {
-        stop("oolong is locked.")
-    }
-    if (!.check_new(oolong)) {
-        stop("oolong is partially coded.")
-    }
-    oolong$clone(deep = FALSE)
-}
-
-#' Summarize multiple oolong objects.
-#'
-#' Summarise multiple oolong objects.
-#' 
-#' @export
-summarize_oolong <- function(...) {
-    if(!.check_hash_dot(...)) {
-        stop("Not all oolong object(s) are created with the same conditions.")
-    }
[…]

### 2020-02-19 R/oolong_summary_dictionary.R

@@ -1,73 +1,0 @@
-.minmax <- function(x) {
-    (x - min(x)) / (max(x) - min(x)) 
-}
-
-.corr_plot <- function(answers, target_value) {
-    tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer)) %>% ggplot2::ggplot(ggplot2::aes(x = avg_answer, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Human judgement") + ggplot2::ylab("Target value") -> correlation_plot
-    return(correlation_plot)
-}
-
-.ba_plot <- function(answers, target_value) {
-    plot_data <- tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer))
-    plot_data$diffxy <- plot_data$target_value - plot_data$avg_answer
-    plot_data$meanxy <- (plot_data$target_value + plot_data$avg_answer) / 2
-    mean_diff_xy <- mean(plot_data$diffxy)
-    sd_diff_xy <- sd(plot_data$diffxy)
-    ggplot2::ggplot(plot_data, ggplot2::aes(x = meanxy, y = diffxy)) + ggplot2::geom_point() + ggplot2::geom_hline(yintercept = mean_diff_xy) + ggplot2::geom_hline(yintercept = mean_diff_xy - 1.96 * sd_diff_xy, linetype = 2) + ggplot2::geom_hline(yintercept = mean_diff_xy + 1.96 * sd_diff_xy, linetype = 2) + ggplot2::xlab("Mean of two values") + ggplot2::ylab("Difference between two values")
-}
-
-.length_plot <- function(oolong, target_value, ...) {
-    gold <- oolong$turn_gold()
-    nwords <- ntoken(gold, ...)
-    plot_data <- tibble::tibble(target_value = .minmax(target_value), word_length = nwords)
-    ggplot2::ggplot(plot_data, ggplot2::aes(x = word_length, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Number of words") + ggplot2::ylab("Target value")
-}
-
-.cook_plot <- function(answers, target_value) {
-    lmobj <- lm(answers$avg_answer ~ target_value)
-    cutoff <- 4 / (length(target_value) - 2 - 1)
[…]

### 2020-02-19 R/oolong_summary_gs.R

@@ -1,0 +1,63 @@
+.minmax <- function(x) {
+    (x - min(x)) / (max(x) - min(x)) 
+}
+
+.corr_plot <- function(answers, target_value) {
+    tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer)) %>% ggplot2::ggplot(ggplot2::aes(x = avg_answer, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Human judgement") + ggplot2::ylab("Target value") -> correlation_plot
+    return(correlation_plot)
+}
+
+.ba_plot <- function(answers, target_value) {
+    plot_data <- tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer))
+    plot_data$diffxy <- plot_data$target_value - plot_data$avg_answer
+    plot_data$meanxy <- (plot_data$target_value + plot_data$avg_answer) / 2
+    mean_diff_xy <- mean(plot_data$diffxy)
+    sd_diff_xy <- sd(plot_data$diffxy)
+    ggplot2::ggplot(plot_data, ggplot2::aes(x = meanxy, y = diffxy)) + ggplot2::geom_point() + ggplot2::geom_hline(yintercept = mean_diff_xy) + ggplot2::geom_hline(yintercept = mean_diff_xy - 1.96 * sd_diff_xy, linetype = 2) + ggplot2::geom_hline(yintercept = mean_diff_xy + 1.96 * sd_diff_xy, linetype = 2) + ggplot2::xlab("Mean of two values") + ggplot2::ylab("Difference between two values")
+}
+
+.length_plot <- function(oolong, target_value, ...) {
+    gold <- oolong$turn_gold()
+    nwords <- ntoken(gold, ...)
+    plot_data <- tibble::tibble(target_value = .minmax(target_value), word_length = nwords)
+    ggplot2::ggplot(plot_data, ggplot2::aes(x = word_length, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Number of words") + ggplot2::ylab("Target value")
+}
+
+.cook_plot <- function(answers, target_value) {
+    lmobj <- lm(answers$avg_answer ~ target_value)
+    cutoff <- 4 / (length(target_value) - 2 - 1)
[…]

### 2020-02-19 experimental/oolong_summary_dictionary.R

@@ -1,75 +1,0 @@
-devtools::load_all()
-
-.minmax <- function(x) {
-    (x - min(x)) / (max(x) - min(x)) 
-}
-
-.corr_plot <- function(answers, target_value) {
-    tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer)) %>% ggplot2::ggplot(ggplot2::aes(x = avg_answer, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Human judgement") + ggplot2::ylab("Target value") -> correlation_plot
-    return(correlation_plot)
-}
-
-.ba_plot <- function(answers, target_value) {
-    plot_data <- tibble::tibble(target_value = .minmax(target_value), avg_answer = .minmax(answers$avg_answer))
-    plot_data$diffxy <- plot_data$target_value - plot_data$avg_answer
-    plot_data$meanxy <- (plot_data$target_value + plot_data$avg_answer) / 2
-    mean_diff_xy <- mean(plot_data$diffxy)
-    sd_diff_xy <- sd(plot_data$diffxy)
-    ggplot2::ggplot(plot_data, ggplot2::aes(x = meanxy, y = diffxy)) + ggplot2::geom_point() + ggplot2::geom_hline(yintercept = mean_diff_xy) + ggplot2::geom_hline(yintercept = mean_diff_xy - 1.96 * sd_diff_xy, linetype = 2) + ggplot2::geom_hline(yintercept = mean_diff_xy + 1.96 * sd_diff_xy, linetype = 2) + ggplot2::xlab("Mean of two values") + ggplot2::ylab("Difference between two values")
-}
-
-.length_plot <- function(oolong, target_value, ...) {
-    gold <- oolong$turn_gold()
-    nwords <- ntoken(gold, ...)
-    plot_data <- tibble::tibble(target_value = .minmax(target_value), word_length = nwords)
-    ggplot2::ggplot(plot_data, ggplot2::aes(x = word_length, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Number of words") + ggplot2::ylab("Target value")
-}
-
-.cook_plot <- function(answers, target_value) {
-    lmobj <- lm(answers$avg_answer ~ target_value)
-    cutoff <- 4 / (length(target_value) - 2 - 1)
[…]

### 2020-02-19 README.Rmd
remove target_value at creation
Fixing the problem of oolong_tm without topic intrusion tests

Removal of inadviable workflow

@@
 
-A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer' and 'target_value'.
+A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer'.
 
@@
 
-As instructed, put back the score you would like to validate into the `docvars` "target_value".
-In this example, we calculate the AFINN score for each tweet using quanteda.
-The dictionary `afinn` is bundle with this package.
+In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.
 
@@
 ```{r}
-docvars(gold_standard, "target_value") <- all_afinn_score
-summarize_gold_standard(gold_standard)
+summarize_oolong(oolong_test, target_value = all_afinn_score)
 ```
@@
 
-### Inadvisable workflow
-
-*NOTE: This workflow is not recommended!*
-
-This workflow violates the "validation first" principle. You can supply the `target_value` at the creation of oolong test.
-
-```{r, include = FALSE}
-set.seed(46709394)
-```
-
-```{r}
-dfm(trump2k, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
-    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
-           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
-           base = ntoken(trump2k, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
-    pull(afinn_score) -> trump2k_afinn_score
-oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive", target_value = trump2k_afinn_score)
-oolong_test
-```
-
-```{r, eval = FALSE}
-oolong_test$do_gold_standard_test()
-```
-
-```{r, include = FALSE}
-oolong_test$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, 20, replace = TRUE)
-```
-
-```{r}
-oolong_test$lock()
-gold_standard <- oolong_test$turn_gold()
-docvars(gold_standard, "target_value")
-```
-
-```{r}
-summarize_gold_standard(gold_standard)
-```
-
 ## References

### 2020-02-19 R/oolong_gs.R

@@ -3,7 +3,7 @@
 ### data structures: use singular, except list-column.
 
 
-.generate_gold_standard <- function(input_corpus, exact_n = NULL, frac = 0.01, target_value  = NULL) {
+.generate_gold_standard <- function(input_corpus, exact_n = NULL, frac = 0.01) {
     if ("corpus" %in% class(input_corpus)) {
         input_corpus <- quanteda::texts(input_corpus)
     }
@@ -13,13 +13,7 @@
     }
     sample_vec <- .sample_corpus(input_corpus, exact_n)
     target_text <- input_corpus[sample_vec]
-    if (!is.null(target_value)) {
-        warning("Specifying target_value before coding is not recommended.")
-        target_value <- target_value[sample_vec]
-    } else {
-        target_value <- NA
-    }
-    test_content <- tibble::tibble(case = seq_len(exact_n), text = target_text, answer = NA, target_value = target_value)
+    test_content <- tibble::tibble(case = seq_len(exact_n), text = target_text, answer = NA)
     return(test_content)
 }
 
@@ -59,25 +53,14 @@
 .turn_gold <- function(test_content) {
     res <- quanteda::corpus(test_content$gold_standard$text)
     quanteda::docvars(res, "answer") <- test_content$gold_standard$answer
-    quanteda::docvars(res, "target_value") <- test_content$gold_standard$target_value
     class(res) <- append("oolong_gold_standard", class(res))
     return(res)
 }
-
 
 #' @export
 print.oolong_gold_standard <- function(obj) {
     quanteda:::print.corpus(obj)
     .cp(TRUE, "Access the answer from the coding with quanteda::docvars(obj, 'answer')")
-    .cp(TRUE, "Put back the test score you would like to validate into quanteda::docvars(obj, 'target_value')")
-}
-
-#' @export
-summarize_gold_standard <- function(obj) {
-    if (all(is.na(quanteda::docvars(obj, "target_value")))) {
-        stop("target_value is not available.")
-    }
-    cor(quanteda::docvars(obj, "target_value"), quanteda::docvars(obj, "answer"))
 }
 
 Oolong_test_gs <-
@@ -86,7 +69,7 @@ Oolong_test_gs <-
             inherit = Oolong_test,
             public = list(
                 initialize = function(input_corpus, exact_n = NULL, frac = 0.01, target_value  = NULL, construct = "positive") {
-                    private$test_content$gold_standard <- .generate_gold_standard(input_corpus, exact_n, frac, target_value)
[…]

### 2020-02-19 R/oolong_summary_gs.R

@@ -35,7 +35,11 @@
     colnames(answers) <- paste0("answer", seq_len(ncol(answers)))
     avg_answer <- apply(answers, 1, mean)
     answers$avg_answer <- avg_answer
-    kripp <- irr::kripp.alpha(t(as.matrix(answers[,grepl("^answer", colnames(answers))])), method = "ordinal")
+    if (length(obj_list) > 1) {
+        kripp <- irr::kripp.alpha(t(as.matrix(answers[,grepl("^answer", colnames(answers))])), method = "ordinal")
+    } else {
+        kripp <- NA
+    }
     res <- list()
     res$kripp <- kripp
     if (is.null(target_value)) {

### 2020-02-19 R/oolong.R
Increase test coverage, and fixing the UI

@@ -47,12 +47,29 @@ create_oolong <- function(input_model = NULL, input_corpus = NULL, n_top_terms =
         stop("input_model and input_corpus cannot be both NULL.")
     }
     if (!is.null(input_model)) {
+        if (!.is_topic_model(input_model)) {
+            stop("input_model is not a topic model. If you want to create gold standard with an input_corpus, use: create_oolong(input_corpus = input_corpus)")
+        }
+    }
+    if (!is.null(input_model)) {
         return(Oolong_test_tm$new(input_model = input_model, input_corpus = input_corpus, n_top_terms = n_top_terms, bottom_terms_percentile = bottom_terms_percentile, exact_n = exact_n, frac = frac, n_top_topics = n_top_topics, n_topiclabel_words = n_topiclabel_words, difficulty = difficulty, use_frex_words = use_frex_words, input_dfm = input_dfm))
     } else {
         return(Oolong_test_gs$new(input_corpus = input_corpus, exact_n = exact_n, frac = frac, target_value = target_value, construct = construct))
     }
 }
 
+.is_topic_model <- function(x) {
+    if (any(class(x) %in% c("WarpLDA", "STM"))) {
+        return(TRUE)
+    }
+    if (is.null(attr(class(x), "package"))) {
+        return(FALSE)
+    }
+    if ("topicmodels" == attr(class(x), "package")) {
+        return(TRUE)
+    }
+    return(FALSE)
+}
 
 #' Newsgroup text dataset
 #'

### 2020-02-19 R/oolong_summary_gs.R

@@ -18,7 +18,7 @@
 
 .length_plot <- function(oolong, target_value, ...) {
     gold <- oolong$turn_gold()
-    nwords <- ntoken(gold, ...)
+    nwords <- quanteda::ntoken(gold, ...)
     plot_data <- tibble::tibble(target_value = .minmax(target_value), word_length = nwords)
     ggplot2::ggplot(plot_data, ggplot2::aes(x = word_length, y = target_value)) + ggplot2::geom_point() + ggplot2::geom_smooth(method = lm) + ggplot2::xlab("Number of words") + ggplot2::ylab("Target value")
 }
@@ -44,7 +44,8 @@
     res$kripp <- kripp
     if (is.null(target_value)) {
         warning("target_value is NULL, only the reliability of the answers from the coder(s) are studied.")
-        class(res) <- append(class(res), "oolong_res_gs")
+        class(res) <- append(class(res), "oolong_summary")
+        res$type <- "gs"
         return(res)
     }
     p1 <- .corr_plot(answers, target_value)

### 2020-02-19 tests/testthat/test-topicmodels.R

@@ -32,7 +32,6 @@ test_that("check_complete", {
     expect_error(z$lock())
 })
 
-
 test_that("github issue #8 - word", {
     library(topicmodels)
     data("AssociatedPress")
@@ -49,4 +48,3 @@ test_that("github issue #8 - topic", {
     lda <- LDA(topicmodels_dfm, k = 5)
     expect_error(create_oolong(lda, newsgroup5$text[1:10], exact_n = 5), NA)
 })
-

### 2020-02-20 README.Rmd
Increase test coverage, and fixing the UI
adding travis

@@
 <!-- badges: start -->
+[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
 <!-- badges: end -->
@@
 
-```{r echo = FALSE}
+```{r}
 library(oolong)

### 2020-02-20 README.Rmd
Replacing the very large newsgroup data with some abstracts.

@@
 
-`newsgroup_stm` is an example topic model trained with the data `newsgroup5` using the `stm` package.
+`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
 Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.
@@
 ```{r example}
-newsgroup_stm
+abstracts_stm
 ```
@@
 ```{r createtest}
-oolong_test <- create_oolong(newsgroup_stm)
+oolong_test <- create_oolong(abstracts_stm)
 oolong_test
@@
 
-For example, `newsgroup_stm` was generated with the corpus `newsgroup5$text`
+For example, `abstracts_stm` was generated with the corpus `abstracts$text`
 
@@
 library(tibble)
-newsgroup5
+abstracts
 ```
@@
 ```{r createtest2}
-oolong_test <- create_oolong(newsgroup_stm, newsgroup5$text)
+oolong_test <- create_oolong(abstracts_stm, abstracts$text)
 oolong_test
@@
 ```{r step0, eval = FALSE}
-dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
-docvars(newsgroup5_dfm, "title") <- newsgroup5$title
-newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
-newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
+dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
+docvars(abstracts_dfm, "title") <- abstracts$title
+abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
+abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
 ```
@@
 ```{r step1}
-oolong_test_rater1 <- create_oolong(newsgroup_stm, newsgroup5$text)
+oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
 ```
@@
 
-`newsgroup_warplda` is a Warp LDA object trained with the same dataset as the `newsgroup_stm`
+`abstracts_warplda` is a Warp LDA object trained with the same dataset as the `abstracts_stm`
 
 ```{r warplda}
-newsgroup_warplda
+abstracts_warplda
 ```
@@
 ### Just word intrusion test.
-oolong_test <- create_oolong(newsgroup_warplda)
+oolong_test <- create_oolong(abstracts_warplda)
 oolong_test
@@
 ```{r warplda3}
-newsgroup5_dfm
+abstracts_dfm
 ```
@@
 ```{r warplda4}
-oolong_test <- create_oolong(newsgroup_warplda, newsgroup5$text, input_dfm = newsgroup5_dfm)
+oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
 oolong_test

### 2020-02-20 R/doc_data.R

@@ -1,0 +1,6 @@
+
+#' Abstracts of communication journals dataset
+#'
+#' This is a dataset of all abstracts of papers published in Journal of Communication, Communication Research, Journal of Computer-mediated Communication, Political Communication and Communication Monographs from 2000 to 2017.
+"abstracts"
+

### 2020-02-20 newsgroup.R

@@ -1,103 +1,0 @@
-require(tidyverse)
-require(quanteda)
-require(stm)
-require(oolong)
-
-
-##newsgroup <- rio::import("20_newsgroup.csv") %>% as_tibble
-
-## set.seed(42)
-## newsgroup %>% select(text, title) %>% mutate(ntoken = ntoken(text)) %>% sample_frac(1) %>% filter(text != "" & ntoken > 150) -> newsgroup5
-## saveRDS(newsgroup5, "newsgroup5.RDS")
-corpus(newsgroup5)
-
-require(textclean)
-
-clean_text <- replace_non_ascii(newsgroup5$text)
-
-saveRDS(clean_text, "clean_text.RDS")
-
-x <- readRDS("clean_text.RDS")
-
-small_x <- purrr::map_chr(x, ~substr(., 1, 800))
-saveRDS(newsgroup5, "clean__small.RDS")
-
-usethis::use_data(newsgroup5, overwrite = TRUE)
-newsgroup5$text <- small_x
-
-
-dfm(newsgroup5$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> newsgroup5_dfm
-docvars(newsgroup5_dfm, "title") <- newsgroup5$title
-
-###saveRDS(newsgroup5_dfm, "newgroup5_dfm.RDS")
-
-usethis::use_data(newsgroup5_dfm)
-
-newsgroup5_dfm %>% convert(to = "stm", omit_empty = FALSE) -> newsgroup5_stm
-
-newsgroup_stm <- stm(newsgroup5_stm$documents, newsgroup5_stm$vocab, data =newsgroup5_stm$meta, K = 10, seed = 42)
-
-
-usethis::use_data(newsgroup_stm, overwrite = TRUE)
-
-require(text2vec)
-lda_model <- LDA$new(n_topics = 10, doc_topic_prior = 0.1, topic_word_prior = 0.01)
-
-theta <- lda_model$fit_transform(x = newsgroup5_dfm, convergence_tol = 0.001, n_check_convergence = 25)
-
-newsgroup_warplda <- lda_model
-
[…]

### 2020-02-20 tests/testthat/test-generate_test_content.R

@@ -1,30 +1,30 @@
 context("check helper functions")
 
 test_that("generate_test_content", {
-    x <- oolong:::.generate_test_content(newsgroup_stm)
+    x <- oolong:::.generate_test_content(abstracts_stm)
     expect_null(x$topic)
-    x <- oolong:::.generate_test_content(newsgroup_stm, quanteda::corpus(newsgroup5$text))
+    x <- oolong:::.generate_test_content(abstracts_stm, quanteda::corpus(abstracts$text))
     expect_false(is.null(x$topic))
 })
 
 test_that("check_complete", {
-    x <- oolong:::.generate_test_content(newsgroup_stm)
+    x <- oolong:::.generate_test_content(abstracts_stm)
     expect_false(oolong:::.check_test_content_complete(x))
     x$word$answer <- 1
     expect_true(oolong:::.check_test_content_complete(x))
-    y <- oolong:::.generate_test_content(newsgroup_stm, newsgroup5$text)
+    y <- oolong:::.generate_test_content(abstracts_stm, abstracts$text)
     expect_false(oolong:::.check_test_content_complete(y))
     y$topic$answer <- 1
     expect_false(oolong:::.check_test_content_complete(y))
     y$word$answer <- 1
     expect_true(oolong:::.check_test_content_complete(y))
-    z <- create_oolong(newsgroup_stm)
+    z <- create_oolong(abstracts_stm)
     expect_error(z$lock())
 })
 
 test_that("generate_topic_content", {
     ## reference issue #8
     ## frac too small!
-    expect_error(oolong:::.generate_test_content(newsgroup_topicmodels, newsgroup5$text[1:10], frac = 0.1))
-    expect_warning(oolong:::.generate_test_content(newsgroup_topicmodels, newsgroup5$text[1:10], exact_n = 12))
+    expect_error(oolong:::.generate_test_content(abstracts_topicmodels, abstracts$text[1:10], frac = 0.1))
+    expect_warning(oolong:::.generate_test_content(abstracts_topicmodels, abstracts$text[1:10], exact_n = 12))
 })

### 2020-02-20 tests/testthat/test-multiple_objs.R

@@ -11,7 +11,7 @@ genius_topic <- function(obj1) {
 }
 
 test_that("defensive programming", {
-    obj1 <- create_oolong(newsgroup_stm)
+    obj1 <- create_oolong(abstracts_stm)
     obj2 <- clone_oolong(obj1)
     ### Not lock
     expect_error(summarize_oolong(obj1))
@@ -21,10 +21,10 @@ test_that("defensive programming", {
     expect_error(summarize_oolong(obj1, obj2))
     ### Testing checking hash.
     set.seed(1212112)
-    obj1 <- create_oolong(newsgroup_stm)
+    obj1 <- create_oolong(abstracts_stm)
     obj2 <- clone_oolong(obj1)
     set.seed(12121999)
-    obj3 <- create_oolong(newsgroup_stm)
+    obj3 <- create_oolong(abstracts_stm)
     obj1 <- genius_word(obj1)
     obj2 <- genius_word(obj2)
     obj3 <- genius_word(obj3)
@@ -36,7 +36,7 @@ test_that("defensive programming", {
     ## obj2 is a clone of obj1
     expect_error(summarise_oolong(obj1, obj2), NA)
     ## Warning about premature locking
-    obj1 <- create_oolong(newsgroup_stm)
+    obj1 <- create_oolong(abstracts_stm)
     obj1$lock(force = TRUE)
     expect_warning(summarize_oolong(obj1))
 })

### 2020-02-20 tests/testthat/test-printing.R

@@ -11,12 +11,12 @@ genius_topic <- function(obj1) {
 }
 
 test_that("gs_creation", {
-    output1 <- capture_output({ x <- create_oolong(input_corpus = newsgroup5$text); x }, print = TRUE)
+    output1 <- capture_output({ x <- create_oolong(input_corpus = abstracts$text); x }, print = TRUE)
     expect_true(stringr::str_detect(output1, "gold standard generation"))
 })
 
 test_that("gs_turngold", {
-    output2 <- capture_output({ x <- create_oolong(input_corpus = newsgroup5$text); x$lock(force = TRUE); x$turn_gold() }, print = TRUE)
+    output2 <- capture_output({ x <- create_oolong(input_corpus = abstracts$text); x$lock(force = TRUE); x$turn_gold() }, print = TRUE)
     ## quanteda output
     expect_true(stringr::str_detect(output2, "Corpus consisting"))
     ## oolong output

### 2020-02-20 tests/testthat/test-topicmodels.R

@@ -11,24 +11,24 @@ genius_topic <- function(obj1) {
 }
 
 test_that("generate_test_content", {
-    x <- oolong:::.generate_test_content(newsgroup_topicmodels)
+    x <- oolong:::.generate_test_content(abstracts_topicmodels)
     expect_null(x$topic)
-    x <- oolong:::.generate_test_content(newsgroup_topicmodels, quanteda::corpus(newsgroup5$text))
+    x <- oolong:::.generate_test_content(abstracts_topicmodels, quanteda::corpus(abstracts$text))
     expect_false(is.null(x$topic))
 })
 
 test_that("check_complete", {
-    x <- oolong:::.generate_test_content(newsgroup_topicmodels)
+    x <- oolong:::.generate_test_content(abstracts_topicmodels)
     expect_false(oolong:::.check_test_content_complete(x))
     x$word$answer <- 1
     expect_true(oolong:::.check_test_content_complete(x))
-    y <- oolong:::.generate_test_content(newsgroup_topicmodels, newsgroup5$text)
+    y <- oolong:::.generate_test_content(abstracts_topicmodels, abstracts$text)
     expect_false(oolong:::.check_test_content_complete(y))
     y$topic$answer <- 1
     expect_false(oolong:::.check_test_content_complete(y))
     y$word$answer <- 1
     expect_true(oolong:::.check_test_content_complete(y))
-    z <- create_oolong(newsgroup_topicmodels)
+    z <- create_oolong(abstracts_topicmodels)
     expect_error(z$lock())
 })
 
@@ -42,9 +42,9 @@ test_that("github issue #8 - word", {
 test_that("github issue #8 - topic", {
     library(topicmodels)
     library(quanteda)
-    test_corpus <- corpus(newsgroup5[1:10,], text_field = "text")
+    test_corpus <- corpus(abstracts[1:10,], text_field = "text")
     test_dfm <- dfm(test_corpus)
     topicmodels_dfm <- convert(test_dfm, to = "topicmodels")
     lda <- LDA(topicmodels_dfm, k = 5)
-    expect_error(create_oolong(lda, newsgroup5$text[1:10], exact_n = 5), NA)
+    expect_error(create_oolong(lda, abstracts$text[1:10], exact_n = 5), NA)
 })

### 2020-02-21 README.Rmd
Fixed S3 generic consistency issues, ref #15

@@
 [![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
+[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
 <!-- badges: end -->
@@
 The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia.
-It is very popular in Taiwan, Japan and Hong Kong] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
+It is very popular in Taiwan, Japan and Hong Kong.
+In Cantonese and Taiwanese Mandarin, the same word can also mean "confused".
+It perfectly captures the spirit of human-in-the-loop validation.
+] is to generate and administrate validation tests easily for typical automated content analysis tools such as topic models and dictionary-based tools.
 

### 2020-02-21 R/oolong_gs.R

@@ -58,8 +58,8 @@
 }
 
 #' @export
-print.oolong_gold_standard <- function(obj) {
-    quanteda:::print.corpus(obj)
+print.oolong_gold_standard <- function(x, ...) {
+    quanteda:::print.corpus(x)
     .cp(TRUE, "Access the answer from the coding with quanteda::docvars(obj, 'answer')")
 }
 

### 2020-02-22 README.Rmd
reorganization

@@
 
-The validation test is called "oolong test" (for reading tea leaves).
-Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`.
-The most important parameters are `input_model` and `input_corpus`.
-Setting each of them to `NULL` generates different tests.
-
-| input\_model | input\_corpus | output                                                                                                                                      |
-|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
-| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
-| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
-| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
-| NULL         | NULL          | error                                                                                                                                       |
-
-## Installation
-
-You can install the development version from [GitHub](https://github.com/) with:
-
-``` r
-# install.packages("devtools")
-devtools::install_github("chainsawriot/oolong")
-```
-
-## Validating Topic Models
-
-#### Word intrusion test
-
-`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.
-
-```{r}
-library(oolong)
-library(stm)
-library(quanteda)
-library(dplyr)
-```
-
-```{r example}
-abstracts_stm
-```
-
-To create an oolong test, use the function `create_oolong_test`.
-
-```{r createtest}
-oolong_test <- create_oolong(abstracts_stm)
-oolong_test
-```
-
-As instructed, use the method `$do_word_intrusion_test()` to start coding.
-
-```{r, eval = FALSE}
-oolong_test$do_word_intrusion_test()
-```
-
-If you are running this in RStudio, you should see a test screen similar to this:
-
-<img src="man/figures/oolong_demo.gif" align="center" />
-
-After the coding, you need to first lock the test. Then, you can look at the model precision by printing the oolong test.
-
-```{r, include = FALSE}
-### Mock this process
-oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
-oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
-```
-
-```{r lock}
-oolong_test$lock()
-oolong_test
-```
-
-#### Topic intrusion test
-
-For example, `abstracts_stm` was generated with the corpus `abstracts$text`
-
-```{r newgroup5}
-library(tibble)
-abstracts
-```
-
-Creating the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.
-
-```{r createtest2}
-oolong_test <- create_oolong(abstracts_stm, abstracts$text)
-oolong_test
-```
-
-Similarly, use the `$do_topic_intrusion_test` to code the test cases, lock the test with `$lock()` and then you can look at the TLO (topic log odds) value by printing the oolong test.
-
-```{r, eval = FALSE}
-oolong_test$do_topic_intrusion_test()
-oolong_test$lock()
-```
-
-```{r, include = FALSE}
-genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
-    return(obj1)
-}
-genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
-    return(obj1)
-}
-oolong_test <- genius_word(genius_topic(oolong_test))
-oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
-oolong_test$lock()
-```
-
-```{r topic_res}
-oolong_test
-```
-
-### Suggested workflow
-
-The test makes more sense if more than one coder is involved.
-A suggested workflow is to create the test, then clone the oolong object.
-Ask multiple coders to do the test(s) and then summarize the results.
-
-Train a topic model.
-
-```{r step0, eval = FALSE}
-dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
-docvars(abstracts_dfm, "title") <- abstracts$title
-abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
-abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
-```
-
-Create a new oolong object.
-
-```{r step1}
-oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
-```
-
-Clone the oolong object to be used by other raters.
-
-```{r step2}
-oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
-```
-
-Ask different coders to code each object and then lock the object.
-
-```{r, eval = FALSE}
-## Let rater 1 do the test.
-oolong_test_rater1$do_word_intrusion_test()
-oolong_test_rater1$do_topic_intrusion_test()
-oolong_test_rater1$lock()
-
-## Let rater 2 do the test.
-oolong_test_rater2$do_word_intrusion_test()
-oolong_test_rater2$do_topic_intrusion_test()
-oolong_test_rater2$lock()
-```
-
-```{r, include = FALSE}
-### Mock this process
-set.seed(46709394)
-oolong_test_rater1 <- oolong:::.monkey_test(oolong_test_rater1, intelligent = 0.3)
-oolong_test_rater2 <- oolong:::.monkey_test(oolong_test_rater2, intelligent = 0)
-oolong_test_rater1$lock()
-oolong_test_rater2$lock()
-```
-
-Get a summary of the two objects.
-
-```{r, step3}
-summarize_oolong(oolong_test_rater1, oolong_test_rater2)
-```
-
-### About the p-values
-
-The test for model precision (MP) is based on an one-tailed, one-sample binomial test for each rater.
-In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a.
-Fisher's omnibus test).
-
-H0: MP is not better than 1/ n\_top\_terms
-
-H1: MP is better than 1/ n\_top\_terms
-
-The test for the median of TLO is based on a permutation test.
-
-H0: Median TLO is not better than random guess.
-
-H1: Median TLO is better than random guess.
-
-One must notice that the two statistical tests are testing the bear minimum.
-A significant test only indicates the topic model can make the rater(s) perform better than random guess.
-It is not an indication of good topic interpretability.
-Also, one should use a very conservative significant level, e.g.
-$\alpha < 0.001$.
-
-### About Warp LDA
-
-There is a subtle difference between the support for `stm` and for `text2vec`.
-
-`abstracts_warplda` is a Warp LDA object trained with the same dataset as the `abstracts_stm`
-
-```{r warplda}
-abstracts_warplda
-```
-
-All the API endpoints are the same, except the one for the creation of topic intrusion test cases. You must supply also the `input_dfm`.
-
-```{r warplda2}
-### Just word intrusion test.
-oolong_test <- create_oolong(abstracts_warplda)
-oolong_test
-```
-
-```{r warplda3}
-abstracts_dfm
-```
-
-```{r warplda4}
-oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
-oolong_test
-```
-
-## Validating Dictionary-based Methods
-
-### Creating gold standard
-
-`trump2k` is a dataset of 2,000 tweets from @realdonaldtrump.
-
-```{r trump2k}
-tibble(text = trump2k)
-```
-
-For example, you are interested in studying the sentiment of these tweets.
-One can use tools such as AFINN to automatically extract sentiment in these tweets.
-However, oolong recommends to generate gold standard by human coding first using a subset.
-By default, oolong selects 1% of the origin corpus as test cases.
-The parameter `construct` should be an adjective, e.g.
-positive, liberal, populistic, etc.
-
-```{r goldstandard}
-oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive")
-oolong_test
-```
-
-As instructed, use the method `$do_gold_standard_test()` to start coding.
-
-```{r, eval = FALSE}
-oolong_test$do_gold_standard_test()
-```
-
-The test screen should be similar to this:
-
-<img src="man/figures/trump_coding.png" align="center" />
-
-After the coding, you need to first lock the test and then the `$turn_gold()` method is available.
-
-```{r, include = FALSE}
-oolong_test <- readRDS("trump_coded.RDS")
-```
-
-```{r gs_locking}
-oolong_test$lock()
-oolong_test
-```
-
-### Example: Validating AFINN using the gold standard
-
-A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer'.
-
-```{r}
-oolong_test$turn_gold()
-```
-
-In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.
-
-```{r}
-gold_standard <- oolong_test$turn_gold()
-dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
-    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
-           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
-           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
-    pull(afinn_score) -> all_afinn_score
-all_afinn_score
-```
-
-Put back the vector of AFINN score into the respective `docvars` and study the correlation between the gold standard and AFINN.
-
-```{r}
-summarize_oolong(oolong_test, target_value = all_afinn_score)
-```
-
-### Suggested workflow
-
-Create an oolong object, clone it for another coder. According to Song et al. (Forthcoming), you should at least draw 1% of your data.
-
-```{r}
-trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
-trump2 <- clone_oolong(trump)
-```
-
-Instruct two coders to code the tweets and lock the objects.
-
-```{r, eval = FALSE}
-trump$do_gold_standard_test()
-trump2$do_gold_standard_test()
-trump$lock()
-trump2$lock()
-```
-
-```{r, include = FALSE}
-trump_coded <- readRDS("trump_eval.RDS")
-trump <- trump_coded[[1]]
-trump2 <- trump_coded[[2]]
-```
-
-Calculate the target value (in this case, the AFINN score) by turning one object into a corpus.
-
-```{r}
-gold_standard <- trump$turn_gold()
-dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
-    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
-           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
-           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
-    pull(afinn_score) -> target_value
-```
-
-Summarize all oolong objects with the target value.
-
-```{r}
-res <- summarize_oolong(trump, trump2, target_value = target_value)
-```
-
-Read the results. The diagnostic plot consists of 4 subplots. It is a good idea to read Bland & Altman (1986) on the difference between correlation and agreement.
-
-* Subplot (top left): Raw correlation between human judgement and target value. One should want to have a good correlation between the two.
-* Subplot (top right): Bland-Altman plot.
-One should want to have no correlation.
-Also, the dots should be randomly scattering around the mean value.
-If it is so, the two measurements (human judgement and target value) are in good agreement.
-* Subplot (bottom left): Raw correlation between target value and content length.
-One should want to have no correlation, as an indication of good reliability against the influence of content length.
-(See Chan et al.)
-* Subplot (bottom right): Cook's distance of all data point.
-One should want to have no dot (or at least very few dots) above the threshold.
-It is an indication of how the raw correlation between human judgement and target value can or cannot be influenced by extreme values in your data.
-
-The textual output contains the Krippendorff's alpha of the codings by your raters.
-In order to claim validity of your target value, you must first establish the reliability of your gold standard.
-Song et al.
-[Forthcoming] suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.
-
-```{r}
-res
-```
-
-```{r diagnosis}
-plot(res)
-```
-
-## References
-
-1.
-Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J.
-L., & Blei, D.
-M.
-(2009).
-Reading tea leaves: How humans interpret topic models.
-In Advances in neural information processing systems (pp.
-288-296).
-2.
-Song et al.
-(2020) In validations we trust?
-The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis.
-Political Communication.
-[link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
-3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
-4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!
-
----
+Please refer to the [overview of this package](vignettes/overview.md).

### 2020-02-22 R/oolong.R

@@ -2,6 +2,13 @@
 ### function names: use full name, except ren for render
 ### data structures: use singular, except list-column.
 
+#' oolong: create and administrate validation tests for typical automated content analysis tools
+#'
+#' The oolong package makes it very easy to create, adminstrate and evaluate typical automated analysis tools by providing a framework for creating human-in-the-loop validation tests. For topic models, oolong can generate tests such as word intrusion test and topic intrusion test (Chang et al.). For dictionary-based methods, oolong can generate standardized interface for making gold standard ('Ground truth') data. There are only two core functions of this package: \code{\link{create_oolong}} and \code{\link{summarize_oolong}}.
+#' @docType package
+#' @name oolong
+NULL
+
 Oolong_test <- R6::R6Class(
     "oolong_generic",
     public = list(
@@ -24,7 +31,6 @@ Oolong_test <- R6::R6Class(
     )
 )
 
-
 #' Generate a oolong test
 #'
 #' This function generates a oolong test object that can either be used for validating a topic model or for creating ground truth (gold standard) of a text corpus. 
@@ -38,10 +44,11 @@ Oolong_test <- R6::R6Class(
 #' @param n_top_topics (tm) integer, number of most relevant topics to be shown alongside the intruder topic
 #' @param n_topiclabel_words (tm) integer, number of topic words to be shown as the topic label
 #' @param use_frex_words (tm) logical, for a STM object, use FREX words if TRUE, use PROB words if FALSE
-#' @param difficulty (tm) double, to adjust the difficulty of the test. Higher value indicates higher difficulty, must be within the range of 0 to 1, no effect for STM if use_frex_words is FALSE. Ignore for topicmodels objects.
+#' @param difficulty (tm) double, adjust the difficulty of the test. Higher value indicates higher difficulty and must be within the range of 0 to 1, no effect for STM if use_frex_words is FALSE. Ignore for topicmodels objects.
 #' @param input_dfm (tm) a dfm object used for training the input_model, if input_model is a WarpLDA object
 #' @param construct (gs) string, an adjective to describe the construct you want your coders to code the the gold standard test cases.
 #' @return An oolong test object.
+#' @author Chung-hong Chan
 #' @examples
 #' ## Creation of oolong test with only word intrusion test
 #' oolong_test <- create_oolong(input_model = abstracts_stm)

### 2020-02-22 R/oolong_summary.R

@@ -1,6 +1,6 @@
 #' Print and plot oolong summary
 #'
-#' This function prints or plots a useful summary of the results from summarize_oolong().
+#' These functions print or plot a useful summary of the results from \code{\link{summarize_oolong}}.
 #' @param x an oolong_summary
 #' @param ... other parameters
 #' @method print oolong_summary

### 2020-02-24 overview_gh.Rmd
Add a Makefile to generate the documentation. ref #16

---
title: "An overview of the oolong package."
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
set.seed(42)
```
The validation test is called "oolong test" (for reading tea leaves). Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`. The most important parameters are `input_model` and `input_corpus`. Setting each of them to `NULL` generates different tests.

| input\_model | input\_corpus | output                                                                                                                                      |
|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
| NULL         | NULL          | error                                                                                                                                       |

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("chainsawriot/oolong")
```

## Validating Topic Models

#### Word intrusion test

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

```{r}
library(oolong)
library(stm)
library(quanteda)
library(dplyr)
```

```{r example}
abstracts_stm
```

To create an oolong test, use the function `create_oolong_test`.

```{r createtest}
oolong_test <- create_oolong(abstracts_stm)
oolong_test
```

As instructed, use the method `$do_word_intrusion_test()` to start coding.

```{r, eval = FALSE}
oolong_test$do_word_intrusion_test()
```

After the coding, you need to first lock the test. Then, you can look at the model precision by printing the oolong test.

```{r, include = FALSE}
### Mock this process
oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
```

```{r lock}
oolong_test$lock()
oolong_test
```

#### Topic intrusion test

For example, `abstracts_stm` was generated with the corpus `abstracts$text`

```{r newgroup5}
library(tibble)
abstracts
```

Creating the oolong test object with the corpus used for training the topic model will generate topic intrusion test cases.

```{r createtest2}
oolong_test <- create_oolong(abstracts_stm, abstracts$text)
oolong_test
```

Similarly, use the `$do_topic_intrusion_test` to code the test cases, lock the test with `$lock()` and then you can look at the TLO (topic log odds) value by printing the oolong test.

```{r, eval = FALSE}
oolong_test$do_topic_intrusion_test()
oolong_test$lock()
```

```{r, include = FALSE}
genius_topic <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
    return(obj1)
}
genius_word <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
    return(obj1)
}
oolong_test <- genius_word(genius_topic(oolong_test))
oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
oolong_test$lock()
```

```{r topic_res}
oolong_test
```

### Suggested workflow

The test makes more sense if more than one coder is involved. A suggested workflow is to create the test, then clone the oolong object. Ask multiple coders to do the test(s) and then summarize the results.

Train a topic model.

```{r step0, eval = FALSE}
dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
docvars(abstracts_dfm, "title") <- abstracts$title
abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
```

Create a new oolong object.

```{r step1}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
```

Clone the oolong object to be used by other raters.

```{r step2}
oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
```

Ask different coders to code each object and then lock the object.

```{r, eval = FALSE}
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

```{r, include = FALSE}
### Mock this process
set.seed(46709394)
oolong_test_rater1 <- oolong:::.monkey_test(oolong_test_rater1, intelligent = 0.3)
oolong_test_rater2 <- oolong:::.monkey_test(oolong_test_rater2, intelligent = 0)
oolong_test_rater1$lock()
oolong_test_rater2$lock()
```

Get a summary of the two objects.

```{r, step3}
summarize_oolong(oolong_test_rater1, oolong_test_rater2)
```

### About the p-values

The test for model precision (MP) is based on an one-tailed, one-sample binomial test for each rater. In a multiple-rater situation, the p-values from all raters are combined using the Fisher's method (a.k.a. Fisher's omnibus test).

H0: MP is not better than 1/ n\_top\_terms

H1: MP is better than 1/ n\_top\_terms

The test for the median of TLO is based on a permutation test.

H0: Median TLO is not better than random guess.

H1: Median TLO is better than random guess.

One must notice that the two statistical tests are testing the bear minimum. A significant test only indicates the topic model can make the rater(s) perform better than random guess. It is not an indication of good topic interpretability. Also, one should use a very conservative significant level, e.g. $\alpha < 0.001$.

### About Warp LDA

There is a subtle difference between the support for `stm` and for `text2vec`.

`abstracts_warplda` is a Warp LDA object trained with the same dataset as the `abstracts_stm`

```{r warplda}
abstracts_warplda
```

All the API endpoints are the same, except the one for the creation of topic intrusion test cases. You must supply also the `input_dfm`.

```{r warplda2}
### Just word intrusion test.
oolong_test <- create_oolong(abstracts_warplda)
oolong_test
```

```{r warplda3}
abstracts_dfm
```

```{r warplda4}
oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
oolong_test
```

## Validating Dictionary-based Methods

### Creating gold standard

`trump2k` is a dataset of 2,000 tweets from \@realdonaldtrump.

```{r trump2k}
tibble(text = trump2k)
```

For example, you are interested in studying the sentiment of these tweets. One can use tools such as AFINN to automatically extract sentiment in these tweets. However, oolong recommends to generate gold standard by human coding first using a subset. By default, oolong selects 1% of the origin corpus as test cases. The parameter `construct` should be an adjective, e.g. positive, liberal, populistic, etc.

```{r goldstandard}
oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive")
oolong_test
```

As instructed, use the method `$do_gold_standard_test()` to start coding.

```{r, eval = FALSE}
oolong_test$do_gold_standard_test()
```

After the coding, you need to first lock the test and then the `$turn_gold()` method is available.

```{r, include = FALSE}
oolong_test$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
))
```

```{r gs_locking}
oolong_test$lock()
oolong_test
```

### Example: Validating AFINN using the gold standard

A locked oolong test can be converted into a quanteda-compatible corpus for further analysis. The corpus contains two `docvars`, 'answer'.

```{r}
oolong_test$turn_gold()
```

In this example, we calculate the AFINN score for each tweet using quanteda. The dictionary `afinn` is bundle with this package.

```{r}
gold_standard <- oolong_test$turn_gold()
dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> all_afinn_score
all_afinn_score
```

Put back the vector of AFINN score into the respective `docvars` and study the correlation between the gold standard and AFINN.

```{r}
summarize_oolong(oolong_test, target_value = all_afinn_score)
```

### Suggested workflow

Create an oolong object, clone it for another coder. According to Song et al. (Forthcoming), you should at least draw 1% of your data.

```{r}
trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
trump2 <- clone_oolong(trump)
```

Instruct two coders to code the tweets and lock the objects.

```{r, eval = FALSE}
trump$do_gold_standard_test()
trump2$do_gold_standard_test()
trump$lock()
trump2$lock()
```

```{r, include = FALSE}
trump$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))

trump2$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(5L, 3L, 2L, 5L, 3L, 1L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))
trump$lock()
trump2$lock()
```

Calculate the target value (in this case, the AFINN score) by turning one object into a corpus.

```{r}
gold_standard <- trump$turn_gold()
dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>% quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) + (neg3 * -3) + (neg2 * -2) + (neg1 * -1)
           + (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) + (pos4 * 4) + (pos5 * 5),
           base = ntoken(gold_standard, remove_punct = TRUE), afinn_score = matching_word_valence / base) %>%
    pull(afinn_score) -> target_value
```

Summarize all oolong objects with the target value.

```{r}
res <- summarize_oolong(trump, trump2, target_value = target_value)
```

Read the results. The diagnostic plot consists of 4 subplots. It is a good idea to read Bland & Altman (1986) on the difference between correlation and agreement.

* Subplot (top left): Raw correlation between human judgement and target value. One should want to have a good correlation between the two.
* Subplot (top right): Bland-Altman plot. One should want to have no correlation. Also, the dots should be randomly scattering around the mean value. If it is so, the two measurements (human judgement and target value) are in good agreement.
* Subplot (bottom left): Raw correlation between target value and content length. One should want to have no correlation, as an indication of good reliability against the influence of content length. (See Chan et al.)
* Subplot (bottom right): Cook's distance of all data point. One should want to have no dot (or at least very few dots) above the threshold. It is an indication of how the raw correlation between human judgement and target value can or cannot be influenced by extreme values in your data.

The textual output contains the Krippendorff's alpha of the codings by your raters. In order to claim validity of your target value, you must first establish the reliability of your gold standard. Song et al. [Forthcoming] suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.

```{r}
res
```

```{r diagnosis}
plot(res)
```

## References

1. Chang, J., Gerrish, S., Wang, C., Boyd-Graber, J. L., & Blei, D. M. (2009). Reading tea leaves: How humans interpret topic models. In Advances in neural information processing systems (pp. 288-296).
2. Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication. [link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!

---

### 2020-02-24 vig_body.Rmd
Add a Makefile to generate the documentation. ref #16

--- 2020-02-24 overview_gh.Rmd
@@
----
-title: "An overview of the oolong package."
-output: github_document
-author:
-  - Chung-hong Chan ^[University of Mannheim]
----
-
-```{r, include = FALSE}
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  fig.path = "man/figures/README-",
-  out.width = "100%"
-  )
-set.seed(42)
-```
 The validation test is called "oolong test" (for reading tea leaves).

### 2020-06-11 overview_gh.Rmd
Minor fix of documentation. Really ready to go.
Update documentation for BTM #21 ref #19

@@
 oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
+oolong_test
+```
+
+## About Biterm Topic Model
+
+Currently, oolong cannot generate topic intrusion tests for Biterm Topic Model.
+
+```{r btm1}
+require(BTM)
+oolong_test <- create_oolong(abstracts_btm)
+oolong_test
+```
+
+```{r btm2}
+oolong_test <- create_oolong(abstracts_btm, abstracts$text)
 oolong_test
@@
 4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!
+5. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903.
 

### 2020-06-11 R/oolong_data_misc.R

@@ -15,6 +15,9 @@
 #' @rdname abstracts_stm
 "abstracts_warplda"
 
+#' @rdname abstracts_stm
+"abstracts_btm"
+
 #' AFINN dictionary
 #'
 #' This is the AFINN sentiment dictionary in quanteda::dictionary format.

### 2020-06-14 overview_gh.Rmd

@@
 `abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.
+Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels` and Biterm Topic Models from `BTM`.
 

### 2020-06-26 btm.Rmd
Add BTM topic intrusion test

---
title: "Biterm Topic Model"
output: github_document
author:
  - Chung-hong Chan ^[University of Mannheim]
---

The package BTM by Jan Wijffels et al. finds "topics in collections of short text". Compared to other topic model packages, BTM requires a special data format for training. Oolong has no problem generating word intrusion tests with BTM. However, that special data format can make creation of topic intrusion tests very tricky.

This guide provides our recommendations on how to use BTM, so that the model can be used for generating topic intrusion tests.

# Requirement #1: Keep your quanteda corpus

It is because every document has a unique document id.

```{r}
require(BTM)
require(quanteda)
devtools::load_all()
trump_corpus <- corpus(trump2k)
```

And then you can do regular text cleaning, stemming procedure with `quanteda`. Instead of making the product a `DFM` object, make it a `token` object. You may read [this issue](https://github.com/quanteda/quanteda/issues/1404) by Benoit et al.

```{r}
tokens(trump_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, split_hyphens = TRUE, remove_url = TRUE) %>% tokens_tolower() %>% tokens_remove(stopwords("en")) %>% tokens_remove("@*")  -> trump_toks
```

# Requirement #2: Keep your data frame

Use this function to convert the `token` object to a data frame.

```{r}
as.data.frame.tokens <- function(x) {
  data.frame(
    doc_id = rep(names(x), lengths(x)),
    tokens = unlist(x, use.names = FALSE)
  )
}

trump_dat <- as.data.frame.tokens(trump_toks)
```

Train a BTM model

```{r}
trump_btm <- BTM(trump_dat, k = 8, iter = 500, trace = 10)
```

## Pecularities of BTM

This is how you should generate $\theta_{t}$ . However, there are many NaN and there are only 1994 rows (`trump2k` has 2000 tweets) due to empty documents.

```{r}
theta <- predict(trump_btm, newdata = trump_dat)
dim(theta)
```

```{r}
setdiff(docid(trump_corpus), row.names(theta))
```

```{r}
trump_corpus[604]
```

Also, the row order is messed up.

```{r}
head(row.names(theta), 100)
```

# Oolong's support for BTM

Oolong has no problem generating word intrusion test for BTM like you do with other topic models.

```{r}
oolong <- create_oolong(trump_btm)
oolong
```

For generating topic intrusion tests, however, you must provide the data frame you used for training (in this case `trump_dat`). Your `input_corpus` must be a quanteda corpus too.

```{r}
oolong <- create_oolong(trump_btm, trump_corpus, btm_dataframe = trump_dat)
oolong
```

### 2020-06-26 tests/testthat/test-btm.R

@@ -11,21 +11,31 @@ genius_topic <- function(obj1) {
 }
 
 test_that("generate_test_content", {
-    skip_on_cran()
     x <- oolong:::.generate_test_content(abstracts_btm)
     expect_null(x$topic)
 })
 
-test_that("check_complete", {
-    skip_on_cran()
+test_that("BTM word intrusion", {
     x <- oolong:::.generate_test_content(abstracts_btm)
     expect_false(oolong:::.check_test_content_complete(x))
     x$word$answer <- 1
     expect_true(oolong:::.check_test_content_complete(x))
-    ### topic intrusion test not supportted,
-    expect_warning(oolong:::.generate_test_content(abstracts_btm, abstracts$text))
     z <- create_oolong(abstracts_btm)
     expect_error(z$lock())
-    expect_warning(z1 <- create_oolong(abstracts_btm, abstracts$text))
-    expect_null(z1$topic)
+})
+
+test_that("BTM topic intrusion", {
+    library(quanteda)
+    abstracts_corpus <- corpus(abstracts$text)
+    tokens(abstracts_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, split_hyphens = TRUE) %>%  tokens_tolower() %>% tokens_remove(stopwords("en")) %>% tokens_wordstem() -> toks_q
+    as.data.frame.tokens <- function(x) {
+        data.frame(
+            doc_id = rep(names(x), lengths(x)),
+            tokens = unlist(x, use.names = FALSE)
+        )
+    }
+    abstracts_df <- as.data.frame.tokens(toks_q)
+    expect_error(create_oolong(abstracts_btm, abstracts_corpus))
+    expect_error(create_oolong(abstracts_btm, abstracts$text, btm_dataframe = abstract_df))
+    expect_error(create_oolong(abstracts_btm, abstracts_corpus, btm_dataframe = abstract_df))
 })

### 2020-07-01 overview_gh.Rmd
Add BTM topic intrusion test
Add keyATM support, fix #17

--- 2020-06-11 overview_gh.Rmd
@@
 `abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.
+Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM` and Keyword Assisted Topic Models from `keyATM`.
 
@@
 
-```{r btm2}
+```{r btm2, error = TRUE}
 oolong_test <- create_oolong(abstracts_btm, abstracts$text)

### 2020-07-01 R/oolong_keyatm.R

@@ -1,0 +1,16 @@
+.extract_ingredients.input_model_s3_keyatm <- function(input_model_s3, n_top_terms = 5, need_topic = FALSE, n_topiclabel_words = 8,...) {
+    input_model <- input_model_s3$model
+    K <- ncol(input_model$theta)
+    V <- input_model$V
+    terms <- t(as.matrix(keyATM::top_words(input_model, n = V, show_keyword = FALSE)))
+    all_terms <- unique(as.vector(terms[,seq_len(n_top_terms)]))
+    if (need_topic) {
+        model_terms <- t(as.matrix(keyATM::top_words(input_model, n = n_topiclabel_words, show_keyword = FALSE)))
+        dimnames(model_terms)[[1]] <- NULL
+        theta <- input_model$theta
+    } else {
+        model_terms <- NULL
+        theta <- NULL
+    }
+    return(list(K = K, V = V, terms = terms, all_terms = all_terms, model_terms = model_terms, theta = theta))
+}

### 2020-07-01 abstract.R

@@ -64,3 +64,34 @@ predict(abstracts_btm, newdata = as.data.frame.tokens(toks_q))
 abstracts_btm
 
 usethis::use_data(abstracts_btm, overwrite = TRUE)
+
+###
+
+require(keyATM)
+require(quanteda)
+## 0.2.2
+
+abstracts_dfm
+
+abstracts_dictionary <- list(jstudies = c("frame", "news", "journalist", "newspap", "agenda"),
+     polcomm = c("polit", "elect", "campaign", "candid", "opinion", "civil", "partisan", "ideolog"),
+     healthcomm = c("health", "patient", "medic", "literaci", "hiv", "attitud", "perceiv", "risk", "messag", "smoke", "campaign", "alcohol", "food", "obes"),
+     scicomm = c("scienc", "scientif", "public", "climat"),
+     game = c("game", "player", "video", "gamer", "mmorpg", "violenc", "violent"),
+     cmc = c("internet", "onlin", "sns", "twitter", "facebook", "comput", "cmc", "virtual", "technolog", "share", "privaci", "web", "search", "network", "digit"),
+     culture = c("racial", "white", "black", "african", "communiti", "cultur", "postcoloni"),
+     survey_meth = c("measur", "valid", "variabl", "instrument", "reliabl", "psychometr", "survey", "respond", "interview", "test", "item", "questionnair"),
+     mediapsy = c("emot", "experiment", "behavior", "affect", "percept", "exposur", "influenc", "experi", "cognit"),
+     lang = c("discours", "languag", "interact", "talk", "construct", "convers", "action", "ident"))
+
+abstracts_keyatm <- keyATM(keyATM_read(abstracts_dfm), no_keyword_topics = 0, keywords = abstracts_dictionary, model = "base", options = list(seed = 46709394))
+top_words(abstracts_keyatm, show_keyword = FALSE, n = 30)
+
+usethis::use_data(abstracts_keyatm, overwrite = TRUE)
+usethis::use_data(abstracts_dictionary, overwrite = TRUE)
+
+oolong <- create_oolong(abstracts_keyatm)
+
+oolong$do_word_intrusion_test()
+
+oolong <- create_oolong(abstracts_keyatm, abstracts$text, exact_n = 10)

### 2020-07-01 overview_gh.Rmd

@@
 
-Currently, oolong cannot generate topic intrusion tests for Biterm Topic Model.
-
-```{r btm1}
-require(BTM)
-oolong_test <- create_oolong(abstracts_btm)
-oolong_test
-```
-
-```{r btm2, error = TRUE}
-oolong_test <- create_oolong(abstracts_btm, abstracts$text)
-oolong_test
-```
+Please refer to the vignette about BTM.
 

### 2020-07-01 btm.Rmd
Update doc, add BTM Vignette

@@
----
-title: "Biterm Topic Model"
-output: github_document
-author:
-  - Chung-hong Chan ^[University of Mannheim]
----
-
 The package BTM by Jan Wijffels et al.
@@
 require(quanteda)
-devtools::load_all()
+require(oolong)
 trump_corpus <- corpus(trump2k)
@@
 ```
+
+`btm_dataframe` must not be NULL.
+
+```{r, error = TRUE}
+oolong <- create_oolong(trump_btm, trump_corpus)
+```
+
+`input_corpus` must be a quanteda corpus.
+
+```{r, error = TRUE}
+oolong <- create_oolong(trump_btm, trump2k, btm_dataframe = trump_dat)
+```

### 2020-07-01 R/oolong_data_misc.R
Fix Vignette problem

@@ -37,8 +37,7 @@
 #' This is a random sample of 2000 tweets from @realdonaldtrump account before his assumption of duty as the president of the United States.
 "trump2k"
 
-
-#' @importFrom stats cooks.distance cor.test lm median pchisq quantile sd
+#' @importFrom stats cooks.distance cor.test lm median pchisq quantile sd predict
 #' @importFrom utils head
 #' @importFrom quanteda print corpus
 NULL

### 2020-07-03 paper/paper.rmd
Adding a JOSS paper ref #25

---
title: 'oolong: An R package for validating  automated content analysis tools'
tags:
  - R
  - text analysis
  - topic model
  - sentiment analysis
  - validation
authors:
  - name: Chung-hong Chan
    orcid: 0000-0003-0872-7098
    affiliation: 1
  - name: Marius Sältzer
    orcid: 0000-0002-8604-4666
    affiliation: 1
affiliations:
 - name: Mannheimer Zentrum für Europäische Sozialforschung, Universität Mannheim
   index: 1
citation_author: Chan & Sältzer.
date: 3 July 2020
year: 2020
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

# Summary

Oolong is an R package providing functions for validating common automated content analysis techniques such as topic modeling and dictionary-based methods. This package is designed for R users needing to validate these methods. Typical users of oolong are communication and political scientists, among others.

Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content]. Validation of automated methods has been called for by many scholars, e.g. @grimmer2013text; @ribeiro2016sentibench; @van2018communication. However, the method for validating these automated methods is unstandardized.

Oolong makes it easy to generate standard validation tests suggested by @chang2009reading and @song2020validations.

# Validating topic models

Topic models can be validated by word intrusion test and topic intrusion test [@chang2009reading]. In these tests, a human rater is asked to pick an odd word from a bunch of words (word intrusion test) or pick an odd topic from a bunch of topics for a document (topic intrusion test). Oolong provides an easy-to-use Shiny interface for these tests (Figure 1).

```{r, echo = FALSE, out.width="50%", fig.cap = "A screenshot of word intrusion test"}
knitr::include_graphics("paper_files/fig1.png")
```

Currently, oolong supports a variety of topic models, e.g. structural topic models / correlated topic models from `stm` [@roberts2019stm], warp-LDA models from `text2vec` [@selivanov2020tex2vec], latent dirichlet allocation / correlated-topic models from `topicmodels` [@bettina2011topicmodels], biterm topic models from `BTM` [@wijffels2020btm] and keyword-assisted topic models from `keyATM` [@eshima2020keyatm].

For instance, `abstracts_stm` is a structural topic model trained with the text data from `abstracts$text` [@chan2020high].

```{r, message = FALSE}
library(stm)
library(tibble)
library(dplyr)
library(quanteda)
library(oolong)
```

```{r}
abstracts_stm
```

```{r}
abstracts
```

The function `create_oolong` creates a test object with both word intrusion test and topic intrusion test.

```{r}
oolong_test <- create_oolong(input_model = abstracts_stm,
                             input_corpus = abstracts$text)
oolong_test
```

The tests can be administered with methods `do_word_intrusion_test` and `do_topic_intrusion_test`.

```r
oolong_test$do_word_intrusion_test()
oolong_test$do_topic_intrusion_test()
```

After both tests has been done by a human rater, the test object must be locked and then accuracy metrics such as model precision (MP) and TLO (topic log odd) are displayed.

```{r, include = FALSE}
genius_topic <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
    return(obj1)
}
genius_word <- function(obj1) {
    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
    return(obj1)
}
oolong_test <- genius_word(genius_topic(oolong_test))
oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"

oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
```

```{r lock}
oolong_test$lock()
oolong_test
```

The suggested workflow is to have at least two human raters to do the same set of tests. Test object can be cloned to allow multiple raters to do the test. More than one test object can be studied together using the function `summarize_oolong()`.

```{r}
oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
```

```r
## Let rater 1 do the test.
oolong_test_rater1$do_word_intrusion_test()
oolong_test_rater1$do_topic_intrusion_test()
oolong_test_rater1$lock()

## Let rater 2 do the test.
oolong_test_rater2$do_word_intrusion_test()
oolong_test_rater2$do_topic_intrusion_test()
oolong_test_rater2$lock()
```

```{r, include = FALSE}
### Mock this process
set.seed(46709394)
oolong_test_rater1 <- oolong:::.monkey_test(oolong_test_rater1, intelligent = 0.3)
oolong_test_rater2 <- oolong:::.monkey_test(oolong_test_rater2, intelligent = 0)
oolong_test_rater1$lock()
oolong_test_rater2$lock()
```

Get a summary of the two objects.

```{r, step3}
summarize_oolong(oolong_test_rater1, oolong_test_rater2)
```

# Validating dictionary-based methods

Dictionary-based methods such as AFINN [@nielsen2011new] can be validated by creating a gold standard dataset [@song2020validations]. Oolong provides a workflow for generating such gold standard dataset.

For example, you are interested in studying the sentiment of tweets from Donald Trump. `trump2k` is a random subset of 2,000 tweets from Donald Trump. And you would like to use AFINN to extract sentiment from these tweets. In this analysis, AFINN sentiment score is the *target value*.

```{r}
tibble(text = trump2k)
```

A test object can be generated also with `create_oolong`. The argument `construct` should be an adjective, e.g. "positive" or "liberal".

```{r}
trump <- create_oolong(input_corpus = trump2k,
                       construct = "positive",
                       exact_n = 20)
trump
```

Similarly, we suggest to have at least two human coders to do the same set of tests.

```{r}
trump2 <- clone_oolong(trump)
```

Instruct two coders to code the tweets and lock the objects.

```r
trump$do_gold_standard_test()
trump2$do_gold_standard_test()
trump$lock()
trump2$lock()
```

```{r, include = FALSE}
trump$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(4L, 4L, 2L, 5L, 3L, 2L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))

trump2$.__enclos_env__$private$test_content$gold_standard <- 
structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
"\"@bobby990r_1: @realDonaldTrump would lead polls the second he announces candidacy! America is waiting for him to LEAD us out of this mess!", 
"\"@KdanielsK: @misstcassidy @AllAboutTheTea_ @realDonaldTrump My money is on Kenya getting fired first.\"", 
"Thank you for a great afternoon Birmingham, Alabama! #Trump2016 #MakeAmericaGreatAgain https://t.co/FrOkqCzBoD", 
"\"@THETAINTEDT: @foxandfriends @realDonaldTrump Trump 2016 http://t.co/UlQWGKUrCJ\"", 
"People believe CNN these days almost as little as they believe Hillary....that's really saying something!", 
"It was great being in Michigan. Remember, I am the only presidential candidate who will bring jobs back to the U.S.and protect car industry!", 
"\"@DomineekSmith: @realDonaldTrump is the best Republican presidential candidate of all time.\"  Thank you.", 
"Word is that little Morty Zuckerman’s @NYDailyNews loses more than $50 million per year---can that be possible?", 
"\"@Chevy_Mama: @realDonaldTrump I'm obsessed with @celebrityapprenticeNBC. Honestly,  Mr Trump, you are very inspiring\"", 
"President Obama said \"ISIL continues to shrink\" in an interview just hours before the horrible attack in Paris. He is just so bad! CHANGE.", 
".@HillaryClinton loves to lie. America has had enough of the CLINTON'S! It is time to #DrainTheSwamp! Debates https://t.co/3Mz4T7qTTR", 
"\"@jerrimoore: @realDonaldTrump awesome. A treat to get to see the brilliant Joan Rivers once more #icon\"", 
"\"@shoegoddesss: @realDonaldTrump Will definitely vote for you. Breath of fresh air. America needs you!\"", 
"Ted is the ultimate hypocrite. Says one thing for money, does another for votes. \nhttps://t.co/hxdfy0mjVw", 
"\"@Lisa_Milicaj: Truth be told, I  never heard of The National Review until they \"tried\" to declare war on you. No worries, you got my vote!\"", 
"THANK YOU Daytona Beach, Florida!\n#MakeAmericaGreatAgain https://t.co/IAcLfXe463", 
"People rarely say that many conservatives didn’t vote for Mitt Romney. If I can get them to vote for me, we win in a landslide.", 
"Trump National Golf Club, Washington, D.C. is on 600 beautiful acres fronting the Potomac River. A fantastic setting! http://t.co/pYtkbyKwt5", 
"\"@DRUDGE_REPORT: REUTERS 5-DAY ROLLING POLL: TRUMP 34%, CARSON 19.6%, RUBIO 9.7%, CRUZ 7.7%...\" Thank you - a great honor!"
), answer = c(5L, 3L, 2L, 5L, 3L, 1L, 4L, 5L, 2L, 4L, 1L, 1L, 
4L, 4L, 2L, 4L, 4L, 4L, 4L, 4L), target_value = c(NA, NA, NA, 
NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, 
NA)), row.names = c(NA, -20L), class = c("tbl_df", "tbl", "data.frame"
                                         ))
trump$lock()
trump2$lock()
```

The method `turn_gold` converts a test object into a quanteda corpus [@benoit2018quanteda].

```{r}
gold_standard <- trump$turn_gold()
gold_standard
```

This corpus can be used to calculate the target value, e.g. AFINN.

```{r}
dfm(gold_standard, remove_punct = TRUE) %>% dfm_lookup(afinn) %>%
    quanteda::convert(to = "data.frame") %>%
    mutate(matching_word_valence = (neg5 * -5) + (neg4 * -4) +
               (neg3 * -3) + (neg2 * -2) + (neg1 * -1) +
               (zero * 0) + (pos1 * 1) + (pos2 * 2) + (pos3 * 3) +
               (pos4 * 4) + (pos5 * 5),
           base = ntoken(gold_standard, remove_punct = TRUE),
           afinn_score = matching_word_valence / base) %>% 
		   pull(afinn_score) -> afinn_score
```

Summarize all oolong objects with the target value.

```{r, message = FALSE}
res <- summarize_oolong(trump, trump2, target_value = afinn_score)
```

Printing the summary shows Krippendorff's Alpha, an indicator of interrater reliability. The validity metrics of a text analytic method can be tinted by poor interrater reliability of manual annotations [@song2020validations]. It is important to ensure high interrater reliability first.

```{r}
res
```

Additional diagnostic plots can also be displayed.

```{r diagplot, fig.cap = "Diagnostic plots generated by oolong"}
plot(res)
```

The 4 subplots from left to right, top to bottom are: 1) correlation between human judgement and target value; 2) Bland-Altman plot; 3) correlation between target value and content length and 4) Cook's distance of all data point. These plots are helpful to determine criterion validity, agreement, robustness against content length and outliers of the target value.

# Acknowledgements

The development of oolong is partially supported by SAGE Concept Grant.

# References

### 2020-07-21 README.Rmd
More cleanup, ref #16
Add a Makefile to generate the documentation. ref #16
Update doc, add BTM Vignette
Inclde path for community contribution ref #31

@@
 
+<img src="man/figures/oolong_demo.gif" align="center" height="400" />
+
 The goal of oolong ^[/ˈuːlʊŋ/ 烏龍, literally means "Dark Dragon", is a semi-oxidized tea from Asia.
@@
 
-Please refer to the [overview of this package](vignettes/overview.md).
+Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
+
+## Contributing
+
+Contributions in the form of feedback, comments, code, and bug report are welcome.
+
+* Fork the source code, modify, and issue a [pull request](https://docs.github.com/en/github/collaborating-with-issues-and-pull-requests/creating-a-pull-request-from-a-fork).
+* Issues, bug reports: [File a Github issue](https://github.com/chainsawriot/oolong).
+* Github is not your thing? Contact Chung-hong Chan by e-mail, post, or other methods listed on this [page](https://www.mzes.uni-mannheim.de/d7/en/profiles/chung-hong-chan).
+
+## Code of Conduct
+
+Please note that the oolong project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
+By contributing to this project, you agree to abide by its terms.
+
+---

### 2020-07-21 abstract.R

@@ -10,6 +10,7 @@ devtools::load_all()
 
 ## usethis::use_data(abstracts, overwrite = TRUE)
 
+
 dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 3, max_docfreq = 500) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
 
 usethis::use_data(abstracts_dfm, overwrite = TRUE)

### 2020-07-21 paper/paper.rmd
Add statement of need to the paper. ref openjournals/joss-reviews#2437
Update paper to have a summary of the field, ref #31

@@
 
+# Statement of need
+
 Validity is a requirement of content analysis [@krippendorff2018content; @neuendorf2016content].
@@
 @grimmer2013text; @ribeiro2016sentibench; @van2018communication.
-However, the method for validating these automated methods is unstandardized.
 
 Oolong makes it easy to generate standard validation tests suggested by @chang2009reading and @song2020validations.
+
+# Validation of automated content analysis
+
+The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other.
+These three operations are: 1) *statistical* validation -- to see if the model results agree with the assumptions of the model.
+Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model.
+2) *semantic* validation -- to see if the model results are semantically meaningful.
+This procedure involves comparing model results with human judgment [@grimmer2011general].
+3) *predictive* validation -- to see if the model results can predict external events [@quinn2010analyze].
+For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.
+
+This package focuses on semantic validation.
+The reason is threefold.
+First, there are existing architecture for conducting statistical validation and predictive validation.
+Topic modeling packages such as `text2vec` [@selivanov2020tex2vec] and `topicmodels` [@bettina2011topicmodels] provide functions to calculate metrics such as perplexity.
+Packages such as `textmineR` [@jones2019textminer], `stminsights` [@schwemmer2018stminsights] and `LDAvis` [@sievert2015ldavis] offers additional methods for statistical validation and predictive validation.
+As of writing, `tosca` [@koppers2020tosca] is the only package dealing with semantic validation.
+But the text-based interface might pose challenges to human annotators and it can only support topic models from one package [@change2015lda].
+
+Second, results from statistical validation do not always agree with those from semantic validation.
+For example, topics from a topic model with a lower perplexity do not have a better interpretability [@chang2009reading].
+Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g.
+semantic coherence [@mimno2011optimizing].
+Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying.
+Nonetheless, conducting only statistical validation is not adequate because 3 validation operations supplement each other.
+
+Finally, predictive validation is dependent on research questions and thus it is difficult to be generalized as a reusable software framework.
+Additionally, the relationship between external (sociopolitical) events and the results from automated content analysis tools is usually what social scientists are eager to study, c.f.
+using topic models for information retrieval [@yi2008evaluating].
+We do not believe social scientists would forget to conduct any form of predictive validation for their topic models.
+
+Oolong focuses on semantic validation and the "human-in-the-loop" procedure for it has been standardized [@chang2009reading; @song2020validations].
+The procedure proposed by @chang2009reading has been adopted in subsequent social science studies as the gold standard to validate topic models, e.g.
+@bohr2020reporting, @chuang2015topiccheck, and @miller2017australia.
 

### 2020-07-21 paper/paper.rmd
fix small grammatical problems, ref #31

@@
 The reason is threefold.
-First, there are existing architecture for conducting statistical validation and predictive validation.
+First, there is existing architecture for conducting statistical validation and predictive validation.
 Topic modeling packages such as `text2vec` [@selivanov2020tex2vec] and `topicmodels` [@bettina2011topicmodels] provide functions to calculate metrics such as perplexity.
@@
 Second, results from statistical validation do not always agree with those from semantic validation.
-For example, topics from a topic model with a lower perplexity do not have a better interpretability [@chang2009reading].
+For example, a topic model with a lower perplexity does not have a better interpretability [@chang2009reading].
 Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g.

### 2020-07-21 paper/paper.rmd
port Marius's idea back to paper.rmd, ref #31

@@
 
-# Summary
+# Statement of need
 
-Oolong is an R package providing functions for validating common automated content analysis techniques such as topic modeling and dictionary-based methods.
-This package is designed for R users needing to validate these methods.
-Typical users of oolong are communication and political scientists, among others.
+Oolong is an R package providing functions for semantic validation of topic modeling and dictionary-based methods, two main tools for doing automated content analysis [@boumans2016taking;@gunther2016word].
 
-# Statement of need
+While the validation of statistical properties of topics models is well established, the substantive meaning of categories uncovered is often less clear and their interpretation reliant on "intuition" or "eyeballing".
+As @chang2009reading [p.
+1] put it: "qualitative evaluation of the latent space" or figuratively, reading tea leaves.
+
+The story for dictionary-based methods is not better.
+Researchers usually assume these dictionaries have built-in validity and use them directly in their research.
+However, multiple validation studies [@boukes2020whatsthetone;@gonzalez2015signals;@ribeiro2016sentibench] demonstrate these dictionaries have very limited criterion validity.
+
+Oolong provides a set of tools to objectively judge substantive interpretability to applied users in disciplines such as political science and communication science.
+It allows standardized content based testing of topic models as well as dictionary-based methods with clear numeric indicators of semantic validity.
+Oolong makes it easy to generate standard validation tests suggested by @chang2009reading and @song2020validations.
+
+# Validation of automated content analysis
 
@@
 @grimmer2013text; @ribeiro2016sentibench; @van2018communication.
-
-Oolong makes it easy to generate standard validation tests suggested by @chang2009reading and @song2020validations.
-
-# Validation of automated content analysis
-
 The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other.
@@
 
-This package focuses on semantic validation.
-The reason is threefold.
+This package focuses on semantic validation for three reasons: 
 First, there is existing architecture for conducting statistical validation and predictive validation.
-Topic modeling packages such as `text2vec` [@selivanov2020tex2vec] and `topicmodels` [@bettina2011topicmodels] provide functions to calculate metrics such as perplexity.
-Packages such as `textmineR` [@jones2019textminer], `stminsights` [@schwemmer2018stminsights] and `LDAvis` [@sievert2015ldavis] offers additional methods for statistical validation and predictive validation.
+Topic modeling packages such as `text2vec` [@selivanov2020tex2vec], `topicmodels` [@bettina2011topicmodels], and `textmineR` [@jones2019textminer] provide functions to calculate metrics such as perplexity and semantic coherence.
+Packages such as `stminsights` [@schwemmer2018stminsights] and `LDAvis` [@sievert2015ldavis] offer additional qualitative methods for predictive validation.
 As of writing, `tosca` [@koppers2020tosca] is the only package dealing with semantic validation.
-But the text-based interface might pose challenges to human annotators and it can only support topic models from one package [@change2015lda].
+But the text-based interface might pose challenges to human annotators and it can only support topic models from the `lda` package [@change2015lda].
 
@@
 Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying.
-Nonetheless, conducting only statistical validation is not adequate because 3 validation operations supplement each other.
+Nonetheless, conducting only statistical validation is not adequate because these three validation operations supplement each other.
 
@@
 using topic models for information retrieval [@yi2008evaluating].
-We do not believe social scientists would forget to conduct any form of predictive validation for their topic models.
+We do not believe social scientists would ignore conducting any form of predictive validation.
 
-Oolong focuses on semantic validation and the "human-in-the-loop" procedure for it has been standardized [@chang2009reading; @song2020validations].
+Oolong focuses on semantic validation.
+The package provides the "human-in-the-loop" semantic validation procedures suggested by @chang2009reading and @song2020validations.
 The procedure proposed by @chang2009reading has been adopted in subsequent social science studies as the gold standard to validate topic models, e.g.
@@
 
-# Validating topic models
+# Semantic validation of topic models
 
@@
 
-```{r, echo = FALSE, out.width="50%", fig.cap = "A screenshot of word intrusion test"}
-knitr::include_graphics("paper_files/fig1.png")
-```
-
 Currently, oolong supports a variety of topic models, e.g.
@@
 For instance, `abstracts_stm` is a structural topic model trained with the text data from `abstracts$text` [@chan2020high].
+
+```{r, echo = FALSE, out.width="50%", fig.cap = "A screenshot of word intrusion test"}
+knitr::include_graphics("paper_files/fig1.png")
+```
 
@@
 
-# Validating dictionary-based methods
+# Semantic validation of dictionary-based methods
 

### 2020-07-21 paper/paper.rmd
talk about @revelunt too, ref #31
fix punct issue, ref #31

@@
 The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other.
-These three operations are: 1) *statistical* validation -- to see if the model results agree with the assumptions of the model.
-Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model.
-2) *semantic* validation -- to see if the model results are semantically meaningful.
-This procedure involves comparing model results with human judgment [@grimmer2011general].
-3) *predictive* validation -- to see if the model results can predict external events [@quinn2010analyze].
+These three operations are: 1) *statistical* validation --to see if the model results agree with the assumptions of the model.
+Examples of statistical validation are calculation of pointwise mutual information, perplexity or semantic coherence of a topic model; 2) *semantic* validation --to see if the model results are semantically making sense.
+This procedure involves comparing model results with human judgment [@grimmer2011general]; 3) *predictive* validation --to see if the model results can predict external events [@quinn2010analyze].
 For example, one can study whether external events can explain surges in attention to a topic extracted by a topic model.
@@
 @bohr2020reporting, @chuang2015topiccheck, and @miller2017australia.
+The procedure proposed by @song2020validations emphasizes both criterion validity and interrater reliability.
 

### 2020-07-22 paper/paper.rmd
adding rhetorical question, ref #31
cf., ref #31

@@
 @grimmer2013text; @ribeiro2016sentibench; @van2018communication.
+But how to validate these methods?
 The paper by @dimaggio2013exploiting conceptualizes validation of automated methods as three different operations and the three operations supplement each other.
@@
 Finally, predictive validation is dependent on research questions and thus it is difficult to be generalized as a reusable software framework.
-Additionally, the relationship between external (sociopolitical) events and the results from automated content analysis tools is usually what social scientists are eager to study, c.f.
+Additionally, the relationship between external (sociopolitical) events and the results from automated content analysis tools is usually what social scientists are eager to study, cf.
 using topic models for information retrieval [@yi2008evaluating].

### 2020-07-24 paper/paper.rmd
Further update the paper

@@
 semantic coherence [@mimno2011optimizing].
-Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying.
+But this correlation is also dependent on the text material.
+For example, @fan2019assessing show that semantic coherence is weakly correlated at best with human assessment, when the text material used for training a topic model has some frequent terms.
+But still, calculation of semantic coherence is recommended in the best practice paper by @maier2018applying.
 Nonetheless, conducting only statistical validation is not adequate because these three validation operations supplement each other.

### 2020-10-13 overview_gh.Rmd
Update doc, add BTM Vignette
Fixing recommendation about which version to install, ref #31

@@
 ---
-title: "An overview of the oolong package."
+title: "Overview"
 output: github_document
@@
 
-You can install the development version from [GitHub](https://github.com/) with:
+Because the package is constantly changing, we suggest using the development version from [GitHub](https://github.com/):
 
@@
 devtools::install_github("chainsawriot/oolong")
+```
+
+You can also install the "stable" (but slightly older) version from CRAN:
+
+```r
+install.packages("oolong")
 ```

### 2020-10-13 overview_gh.Rmd
Update vignette to reflect acceptance of Chan et al. 2020

@@
 One should want to have no correlation, as an indication of good reliability against the influence of content length.
-(See Chan et al.)
+(See Chan et al.
+2020)
 * Subplot (bottom right): Cook's distance of all data point.
@@
 288-296).
+[link](https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models)
 2.
@@
 Political Communication.
-[link](http://www.hyunjinsong.com/supplements/PC_Song_et_al_2020.pdf)
+[link](https://doi.org/10.1080/10584609.2020.1723752)
 3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
-4. Chan et al. (2020) It is not listed here, because it is still under review. Do it faster! Reviewers!
-5. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903.
+4.
+Chan et al.
+(2020) Four best practices for measuring news sentiment using ‘off-the-shelf’ dictionaries: a large-scale p-hacking experiment.
+Computational Communication Research.
+[link](https://osf.io/preprints/socarxiv/np5wa/)
+5. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903. [link](https://arxiv.org/abs/1103.2903)
 

### 2020-10-14 R/oolong_summary.R
Making printing oolong summary smarter, ref #31

@@ -59,21 +59,21 @@ plot.oolong_summary <- function(x, ...) {
 .print_oolong_summary_tm <- function(oolong_summary) {
     .cp(TRUE, "Mean model precision: ", mean(oolong_summary$rater_precision))
     .cp(oolong_summary$n_models > 1, "Quantiles of model precision: ", paste(quantile(oolong_summary$rater_precision), collapse = ", "))
-    .cp(oolong_summary$n_models > 1, "P-value of the model precision (H0: Model precision is not better than random guess): ", oolong_summary$rater_precision_p_value)
-    .cp(oolong_summary$n_models > 1, "Krippendorff's alpha: ", oolong_summary$kripp_alpha)
-    .cp(TRUE, "K Precision: ", paste(round(oolong_summary$k_precision, 1), collapse = ", "))
+    .cp(oolong_summary$n_models > 1, "P-value of the model precision\n (H0: Model precision is not better than random guess): ", round(oolong_summary$rater_precision_p_value, 4))
+    .cp(oolong_summary$n_models > 1, "Krippendorff's alpha: ", round(oolong_summary$kripp_alpha, 3))
+    .cp(TRUE, "K Precision:\n", paste(round(oolong_summary$k_precision, 1), collapse = ", "))
     .cp(!is.na(oolong_summary$tlo[1]), "Mean TLO: ", round(mean(oolong_summary$tlo), 2))
     .cp(!is.na(oolong_summary$tlo[1]), "Median TLO: ", round(median(oolong_summary$tlo), 2))
-    .cp(!is.na(oolong_summary$tlo[1]), "Quantiles of TLO: ", paste(quantile(oolong_summary$tlo), collapse = ", "))
+    .cp(!is.na(oolong_summary$tlo[1]), "Quantiles of TLO: ", paste(round(quantile(oolong_summary$tlo), 2), collapse = ", "))
     if (!is.na(oolong_summary$tlo[1])) {
-        .cp(TRUE, "P-Value of the median TLO (H0: Median TLO is not better than random guess): ", oolong_summary$tlo_p_value)
+        .cp(TRUE, "P-Value of the median TLO \n(H0: Median TLO is not better than random guess): ", round(oolong_summary$tlo_p_value, 4))
     }
 }
 
 .print_oolong_summary_gs <- function(oolong_summary) {
[…]

### 2020-10-15 paper/paper.rmd
Fixing recommendation about which version to install, ref #31
Making printing oolong summary smarter, ref #31
Update paper to explain the diagnostic plot, ref #31

@@
 citation_author: Chan & Sältzer.
-date: 3 July 2020
+date: 15 October 2020
 year: 2020
@@
 
-```{r}
-abstracts
-```
-
 The function `create_oolong` creates a test object with both word intrusion test and topic intrusion test.
@@
 In this analysis, AFINN sentiment score is the *target value*.
-
-```{r}
-tibble(text = trump2k)
-```
 
@@
 
-Additional diagnostic plots can also be displayed.
+Additional diagnostic plots can also be displayed (Figure 2).
 
@@
 
-The 4 subplots from left to right, top to bottom are: 1) correlation between human judgement and target value; 2) Bland-Altman plot; 3) correlation between target value and content length and 4) Cook's distance of all data point.
-These plots are helpful to determine criterion validity, agreement, robustness against content length and outliers of the target value.
+The 4 subplots from left to right, top to bottom are:
+
+1. Correlation between human judgement and target value - A strong correlation between the two is an indicator of criterion validity of the target value.
+2. Bland-Altman plot - If the dots are randomly scattering around the mean value (solid line), it is an indicator of good agreement between human judgement and the target value.
+3.
+Correlation between target value and content length - If there is no strong correlation between the target value and content length, it is an indicator of robustness against the influence of content length [see @chan_4b].
+4. Cook's distance of all data points - if there are only a few dots above the threshold (dotted line), it is an indicator of robustness against the influence of outliers.
 

### 2020-10-15 paper/paper.rmd
paper: Interpretation of TLO etc. ref #31

@@
 
+```{r, include = FALSE}
+set.seed(46709394)
+```
+
 ```{r, step3}
@@
 ```
+
+Two key indicators of semantic validity are mean model precision and median TLO.
+Please interpret the magnitude of the two values [see @chang2009reading] rather than the two statisical tests.
+The two statistical tests are testing whether the raters did better than random guess.
+Therefore, rejection of the null hypothesis is just the bare minimum of topic interpretability, *not* an indicator of adquate semantic validity of the topic model.
+Besides, please a very conservative significant level, e.g.
+alpha < 0.001.
 

### 2020-11-10 README.Rmd
Correcting bib; update README also

@@
 [![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
+[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
+[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
 <!-- badges: end -->

### 2020-11-12 paper/paper.rmd
paper ORCID correction

@@
   - name: Chung-hong Chan
-    orcid: 0000-0003-0872-7098
+    orcid: 0000-0002-6232-7530
     affiliation: 1

### 2020-11-12 README.Rmd
Update README and citation info

--- 2020-07-21 README.Rmd
@@
 [![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
+[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
+[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
+[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
 <!-- badges: end -->
@@
 Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
+
+## Citation
+
+Please cite this package as:
+
+Chan et al., (2020).
+oolong: An R package for validating  automated content analysis tools.
+Journal of Open Source Software, 5(55), 2461, [https://doi.org/10.21105/joss.02461](https://doi.org/10.21105/joss.02461)
+
+For a BibTeX entry, use the output from `citation(package = "oolong")`.
 

### 2020-11-13 README.Rmd
Fix APA formatting in README
test github action

--- 2020-07-21 README.Rmd
@@
 [![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
+[![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
+[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
+[![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
+[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
 <!-- badges: end -->
@@
 Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
+
+## Citation
+
+Please cite this package as:
+
+Chan C-h.
+& Sältzer M., (2020).
+oolong: An R package for validating  automated content analysis tools.
+Journal of Open Source Software, 5(55), 2461, [https://doi.org/10.21105/joss.02461](https://doi.org/10.21105/joss.02461)
+
+For a BibTeX entry, use the output from `citation(package = "oolong")`.
 

### 2021-04-23 overview_gh.Rmd
Seededlda (#42)
Add support for seeded LDA. Ref #39 


Co-authored-by: msaeltzer <msaeltze@mail.uni-mannheim.de>

@@
 `abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM` and Keyword Assisted Topic Models from `keyATM`.
+Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM` and seeded LDA models from `seededlda`.
 

### 2021-04-23 R/oolong.R

@@ -50,7 +50,7 @@ Oolong_test <- R6::R6Class(
 #'   \item{\code{$turn_gold()}}{(gs) convert the oolong object into a quanteda compatible corpus.}
 #' }
 #' For more details, please see the overview vignette: \code{vignette("overview", package = "oolong")}
-#' @param input_model (gs/tm) a STM, WarpLDA, topicmodels or BTM object; if it is NULL, create_oolong assumes that you want to create gold standard.
+#' @param input_model (gs/tm) a STM, WarpLDA, topicmodels, KeyATM, seededlda or BTM object; if it is NULL, create_oolong assumes that you want to create gold standard.
 #' @param input_corpus (gs/tm) if input_model is not null, it should be the corpus (character vector or quanteda::corpus object) to generate the model object. If input_model and input_corpus are not NULL, topic intrusion test cases are generated. If input_model is a BTM object, this argument is ignored. If input_model is null, it generates gold standard test cases.
 #' @param n_top_terms (tm) integer, number of top topic words to be included in the candidates of word intrusion test. 
 #' @param bottom_terms_percentile (tm) double, a term is considered to be an word intruder when its theta less than the percentile of this theta, must be within the range of 0 to 1
@@ -80,7 +80,7 @@ Oolong_test <- R6::R6Class(
 #'   Song et al. (2020) In validations we trust? The impact of imperfect human annotations as a gold standard on the quality of validation of automated content analysis. Political Communication.
 #' 
 #' @export
-create_oolong <- function(input_model = NULL, input_corpus = NULL, n_top_terms = 5, bottom_terms_percentile = 0.6, exact_n = NULL, frac = 0.01, n_top_topics = 3, n_topiclabel_words = 8, use_frex_words = FALSE, difficulty = 1, input_dfm = NULL, construct = "positive", btm_dataframe = NULL) {
+create_oolong<-function(input_model = NULL, input_corpus = NULL, n_top_terms = 5, bottom_terms_percentile = 0.6, exact_n = NULL, frac = 0.01, n_top_topics = 3, n_topiclabel_words = 8, use_frex_words = FALSE, difficulty = 1, input_dfm = NULL, construct = "positive", btm_dataframe = NULL) {
     if (is.null(input_model) & is.null(input_corpus)) {
         stop("input_model and input_corpus cannot be both NULL.")
     }
[…]

### 2021-04-23 R/oolong_gs.R

@@ -1,7 +1,3 @@
-### CODING STYLE
-### function names: use full name, except ren for render
-### data structures: use singular, except list-column.
-
 
 .generate_gold_standard <- function(input_corpus, exact_n = NULL, frac = 0.01) {
     if ("corpus" %in% class(input_corpus)) {
@@ -19,17 +15,17 @@
 
 .UI_GOLD_STANDARD_TEST <-
     miniUI::miniPage(
-                miniUI::gadgetTitleBar("oolong"),
-                miniUI::miniContentPanel(
-                            shiny::uiOutput("current_topic"),
-                            shiny::uiOutput("text_content"),
-                            shiny::uiOutput("score_slider"),
-                            shiny::actionButton("confirm", "confirm"),
-                            shiny::actionButton("nextq", "skip"),
-                            shiny::actionButton("ff", "jump to uncoded item")
-                            
-                        )
-            )
+        miniUI::gadgetTitleBar("oolong"),
+        miniUI::miniContentPanel(
+            shiny::uiOutput("current_topic"),
+            shiny::uiOutput("text_content"),
+            shiny::uiOutput("score_slider"),
+            shiny::actionButton("confirm", "confirm"),
+            shiny::actionButton("nextq", "skip"),
+            shiny::actionButton("ff", "jump to uncoded item")
+            
+        )
+    )
 
 .ren_gold_standard_test <- function(output, test_content, res, construct = "positive") {
     .ren_choices <- function(test_content, res, construct) {        
@@ -84,37 +80,36 @@ print.oolong_gold_standard <- function(x, ...) {
 
 Oolong_test_gs <-
     R6::R6Class(
-            "oolong_test_gs",
-            inherit = Oolong_test,
-            public = list(
-                initialize = function(input_corpus, exact_n = NULL, frac = 0.01, construct = "positive") {
-                    private$test_content$gold_standard <- .generate_gold_standard(input_corpus, exact_n, frac)
-                    private$hash <- digest::digest(private$test_content, algo = "sha1")
-                    private$construct <- construct
-                },
-                print = function() {
-                    .cp(TRUE, "An oolong test object (gold standard generation) with ", nrow(private$test_content$gold_standard), " cases, ", sum(!is.na(private$test_content$gold_standard$answer)), " coded.")
-                    .cp(!private$finalized, "Use the method $do_gold_standard_test() to generate gold standard.")
[…]

### 2021-04-23 abstract.R

@@ -111,3 +111,9 @@ require(topicmodels)
 abstracts_topicmodels_small <- LDA(abstracts_tm, k = 3)
 
 saveRDS(abstracts_topicmodels_small, "./tests/testdata/abstracts_topicmodels_small.RDS")
+
+## seededlda
+require(seededlda)
+abstracts_seededlda <- textmodel_seededlda(x = abstracts_dfm, dictionary = dictionary(abstracts_dictionary), seeds = 46709394, verbose = TRUE)
+saveRDS(abstracts_seededlda, "./tests/testdata/abstracts_seededlda.RDS")
+usethis::use_data(abstracts_seededlda, overwrite = TRUE)

### 2021-05-11 overview_gh.Rmd
using cli to make nicer interface

@@
 ```{r step1}
-oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
+oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text, userid = "joe")
 ```
@@
 ```{r step2}
-oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
+oolong_test_rater2 <- clone_oolong(oolong_test_rater1, userid = "donald")
 ```
@@
 ```{r, eval = FALSE}
-## Let rater 1 do the test.
+## Let donald do the test.
 oolong_test_rater1$do_word_intrusion_test()
@@
 
-## Let rater 2 do the test.
+## Let joe do the test.
 oolong_test_rater2$do_word_intrusion_test()
@@
 ```{r}
-trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
-trump2 <- clone_oolong(trump)
+trump <- create_oolong(input_corpus = trump2k, exact_n = 40, userid = "joe")
+trump2 <- clone_oolong(trump, userid = "donald")
 ```

### 2021-05-11 R/oolong_gs.R

@@ -78,12 +78,24 @@ print.oolong_gold_standard <- function(x, ...) {
     .cp(TRUE, "Access the answer from the coding with quanteda::docvars(obj, 'answer')")
 }
 
-.print_oolong_test_gs <- function(private) {
+.print_oolong_test_gs <- function(private, userid) {
+    bool_finalized <- private$finalized
+    cli::cli_h1("oolong (gold standard generation)")
     .check_version(private)
-    .cp(TRUE, "An oolong test object (gold standard generation) with ", nrow(private$test_content$gold_standard), " cases, ", sum(!is.na(private$test_content$gold_standard$answer)), " coded.")
-    .cp(!private$finalized, "Use the method $do_gold_standard_test() to generate gold standard.")
-    .cp(private$finalized, "Use the method $turn_gold() to convert the test results into a quanteda corpus.")
-    .cp(!private$finalized, "Use the method $lock() to finalize this object and see the results.")
+    if (!is.na(userid)) {
+        cli::cli_text(cli::symbol$smiley, " ", userid)
+    }
+    cli::cli_alert_info("{.strong GS:} n = {nrow(private$test_content$gold_standard)}, {sum(!is.na(private$test_content$gold_standard$answer))} coded.")
+    cli::cli_alert_info("{.strong Construct:}  {private$construct}.")
+    cli::cli_h2("Methods")
+    cli::cli_ul()
+    if (bool_finalized) {
+        cli::cli_li("{.cls $turn_gold()}: convert the test results into a quanteda corpus")
+    } else {
+        cli::cli_li("{.cls $do_gold_standard_test()}: generate gold standard")
+        cli::cli_li("{.cls $lock()}: finalize this object and see the results")        
+    }
+    cli::cli_end()
 }
 
 Oolong_test_gs <-
@@ -99,8 +111,7 @@ Oolong_test_gs <-
                 private$meta <- .generate_meta()
             },
             print = function() {
-                .cp(!is.na(self$userid), "Current coder: ", self$userid, ".")
-                .print_oolong_test_gs(private)
+                .print_oolong_test_gs(private, self$userid)
             },
             do_gold_standard_test = function() {
                 private$check_finalized()

### 2021-05-11 R/oolong_tm.R

@@ -244,15 +244,36 @@
     return(res)
 }
 
-.print_oolong_test_tm <- function(private) {
+.print_oolong_test_tm <- function(private, userid) {
+    bool_word <- !is.null(private$test_content$word)
+    bool_topic <- !is.null(private$test_content$topic)
+    bool_finalized <- private$finalized
+    cli::cli_h1("oolong (topic model)")
     .check_version(private)
-    .cp(TRUE, "An oolong test object with k = ", nrow(private$test_content$word), ", ", sum(!is.na(private$test_content$word$answer)), " coded.")
-    .cp(private$finalized, round(.cal_model_precision(private$test_content$word), 3),"%  precision")
-    .cp(!private$finalized, "Use the method $do_word_intrusion_test() to do word intrusion test.")
-    .cp(!is.null(private$test_content$topic), "With ", nrow(private$test_content$topic) , " cases of topic intrusion test. ", sum(!is.na(private$test_content$topic$answer)), " coded.")
-    .cp(!is.null(private$test_content$topic) & !private$finalized, "Use the method $do_topic_intrusion_test() to do topic intrusion test.")
-    .cp(private$finalized & !is.null(private$test_content$topic), "TLO: ", round(.cal_tlo(private$test_content$topic, mean_value = TRUE), 3))
-    .cp(!private$finalized, "Use the method $lock() to finalize this object and see the results.")
+    cli::cli_text("{.sym_flip(bool_word)} WI {.sym_flip(bool_topic)} TI")
+    if (!is.na(userid)) {
+        cli::cli_text(cli::symbol$smiley, " ", userid)
+    }
+    if (bool_word) {
+        cli::cli_alert_info("{.strong WI:} k = {nrow(private$test_content$word)}, {sum(!is.na(private$test_content$word$answer))} coded.")
+    }
+    if (bool_topic) {
+        cli::cli_alert_info("{.strong TI:} n = {nrow(private$test_content$topic)}, {sum(!is.na(private$test_content$topic$answer))} coded.")
+    }
+    if (bool_finalized) {
+        cli::cli_h2("Results:")
+        .cp(bool_word, round(.cal_model_precision(private$test_content$word), 3),"%  precision")
+        .cp(bool_topic, "TLO: ", round(.cal_tlo(private$test_content$topic, mean_value = TRUE), 3))
+    } else {
+        cli::cli_h2("Methods")
+        cli::cli_ul()
+        cli::cli_li("{.cls $do_word_intrusion_test()}: do word intrusion test")
[…]

### 2021-05-11 tests/testthat/test-printing.R

@@ -20,4 +20,15 @@ test_that("gs_turngold", {
     expect_snapshot({ x <- create_oolong(input_corpus = abstracts$text); x$lock(force = TRUE); x$turn_gold() })
 })
 
-
+test_that("check_calculation_topic_intrusion_multiobject (Printing)", {
+    obj1 <- create_oolong(abstracts_stm, abstracts$text, exact_n = 10)
+    obj2 <- clone_oolong(obj1)
+    obj1 <- genius_word(obj1)
+    obj1 <- genius_topic(obj1)
+    obj1$lock()
+    obj2 <- genius_word(obj2)
+    obj2 <- genius_topic(obj2)
+    obj2$lock()
+    res <- summarize_oolong(obj1, obj2)
+    expect_snapshot(res)
+})

### 2021-05-11 tests/testthat/test-summarize_oolong.R

@@ -71,9 +71,6 @@ test_that("check_calculation_topic_intrusion_multiobject", {
     res <- summarize_oolong(obj1, obj2)
     expect_length(res$tlo_p_value, 1)
     expect_length(res$tlo, 20)
-    ## Might be better to move this to test-printing.
-    ## Travis - Don't like this
-    expect_snapshot(res)
     expect_error(plot(res))
 })
 

### 2021-05-12 btm_gh.Rmd
Update doc, add BTM Vignette
Make all vignettes not emitting constant changing information

--- 2020-07-01 btm.Rmd
@@
+---
+title: "BTM"
+output: github_document
+author:
+  - Chung-hong Chan ^[University of Mannheim]
+---
+
+```{r, include = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  fig.path = "man/figures/README-",
+  out.width = "100%"
+  )
+set.seed(42)
+```
+
 The package BTM by Jan Wijffels et al.
@@
 
-```{r}
+```{r, message = FALSE, results = 'hide', warning = FALSE}
 trump_btm <- BTM(trump_dat, k = 8, iter = 500, trace = 10)

### 2021-05-15 overview_gh.Rmd
Make all vignettes not emitting constant changing information
new ui, fix #26

--- 2021-04-23 overview_gh.Rmd
@@
 ```
-The validation test is called "oolong test" (for reading tea leaves).
-Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`.
-The most important parameters are `input_model` and `input_corpus`.
-Setting each of them to `NULL` generates different tests.
+The validation test is called "oolong test" (for reading tea leaves). This package provides several functions for generating different types of oolong test.
 
-| input\_model | input\_corpus | output                                                                                                                                      |
-|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
-| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
-| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
-| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
-| NULL         | NULL          | error                                                                                                                                       |
+| function | purpose                                                                                                                     |
+|---------:|:----------------------------------------------------------------------------------------------------------------------------|
+|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
+|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test)                                                 |
+| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
+|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard)                                                           |
+
+All of these tests can also be generated with the function [`create_oolong`](#backward-compatibility). As of version 0.3.20, it is no longer recommended.
 
@@
 
-To create an oolong test, use the function `create_oolong_test`.
+To create an oolong test with word intrusion test, use the function `wi`. It is recommended to provide a user id of coder who are going to be doing the test.
 
 ```{r createtest}
-oolong_test <- create_oolong(abstracts_stm)
+oolong_test <- wi(abstracts_stm, userid = "Hadley")
 oolong_test
@@
 ```{r createtest2}
-oolong_test <- create_oolong(abstracts_stm, abstracts$text)
+oolong_test <- ti(abstracts_stm, abstracts$text, userid = "Julia")
 oolong_test
@@
 ```{r step1}
-oolong_test_rater1 <- create_oolong(abstracts_stm, abstracts$text)
+oolong_test_rater1 <- witi(abstracts_stm, abstracts$text, userid = "Yihui")
 ```
@@
 ```{r step2}
-oolong_test_rater2 <- clone_oolong(oolong_test_rater1)
+oolong_test_rater2 <- clone_oolong(oolong_test_rater1, userid = "Jenny")
 ```
@@
 ```{r, eval = FALSE}
-## Let rater 1 do the test.
+## Let Yihui do the test.
 oolong_test_rater1$do_word_intrusion_test()
@@
 
-## Let rater 2 do the test.
+## Let Jenny do the test.
 oolong_test_rater2$do_word_intrusion_test()
@@
 ### Just word intrusion test.
-oolong_test <- create_oolong(abstracts_warplda)
+oolong_test <- ti(abstracts_warplda, userid = "Lionel")
 oolong_test
@@
 
-```{r warplda4}
-oolong_test <- create_oolong(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm)
+```{r warplda4, , message = FALSE, results = 'hide', warning = FALSE}
+oolong_test <- witi(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm, userid = "Mara")
+```
+
+```{r warplda5}
 oolong_test
@@
 ```{r goldstandard}
-oolong_test <- create_oolong(input_corpus = trump2k, construct = "positive")
+oolong_test <- gs(input_corpus = trump2k, construct = "positive", userid = "Joe")
 oolong_test
@@
 ```{r}
-trump <- create_oolong(input_corpus = trump2k, exact_n = 40)
-trump2 <- clone_oolong(trump)
+trump <- gs(input_corpus = trump2k, exact_n = 40, userid = "JJ")
+trump2 <- clone_oolong(trump, userid = "Winston")
 ```
@@
 
+## Backward compatibility
+
+Historically, oolong test objects could only be generated with only one function: `create_oolong`.
+It is no longer the case and no longer recommended anymore.
+It is still retained for backward compatibility purposes.
+If you still need to use  `create_oolong()`, the most important parameters are `input_model` and `input_corpus`.
+Setting each of them to `NULL` generates different tests.
+
+| input\_model | input\_corpus | output                                                                                                                                      |
+|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
+| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
+| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
+| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
+| NULL         | NULL          | error                                                                                                                                       |
+
 ## References

### 2021-05-15 vig_body.Rmd
Make all vignettes not emitting constant changing information
new ui, fix #26

--- 2021-04-23 vig_body.Rmd
@@
-The validation test is called "oolong test" (for reading tea leaves).
-Creating oolong test for topic models and dictionary-based uses the same function: `create_oolong()`.
-The most important parameters are `input_model` and `input_corpus`.
-Setting each of them to `NULL` generates different tests.
+The validation test is called "oolong test" (for reading tea leaves). This package provides several functions for generating different types of oolong test.
 
-| input\_model | input\_corpus | output                                                                                                                                      |
-|--------------|:-------------:|---------------------------------------------------------------------------------------------------------------------------------------------|
-| Not NULL     | NULL          | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
-| Not NULL     | Not NULL      | oolong test for validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
-| NULL         | Not NULL      | oolong test for [creating gold standard](#creating-gold-standard)                                                                           |
-| NULL         | NULL          | error                                                                                                                                       |
+| function | purpose                                                                                                                     |
+|---------:|:----------------------------------------------------------------------------------------------------------------------------|
+|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
+|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test)                                                 |
+| `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test) |
+|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard)                                                           |
+
+All of these tests can also be generated with the function [`create_oolong`](#backward-compatibility). As of version 0.3.20, it is no longer recommended.
 

### 2021-05-15 R/oolong.R

@@ -38,11 +38,14 @@ Oolong_test <- R6::R6Class(
 
 #' Generate an oolong test
 #'
-#' This function generates an oolong test object that can either be used for validating a topic model or for creating ground truth (gold standard) of a text corpus.
-#' 
+#' \code{create_oolong} generates an oolong test object that can either be used for validating a topic model or for creating ground truth (gold standard) of a text corpus. \code{wi} (word intrusion test), \code{ti} (topic intrusion test), \code{witi} (word and topic intrusion tests) and \code{gs} are handy wrappers to \code{create_oolong}. It is recommended to use these wrappers instead of \code{create_oolong}.
+#'
 #' @section Usage:
 #'
-#' This function generates an oolong test object based on \code{input_model} and \code{input_corpus}. If \code{input_model} is not NULL, it generates oolong test for a topic model (tm). If \code{input_model} is NULL but input_corpus is not NULL, it generates oolong test for generating gold standard (gs).
+#' Use \code{ti}, \code{ti}, \code{witi} or \code{gs} to generate an oolong test of your choice. It is recommended to supply also \code{userid} (current coder).
+#' @section About create_oolong:
+#'
+#' Because \code{create_oolong} is not intuitive to use, it is no longer recommended to use \code{create_oolong} to generate oolong test. \code{create_oolong} is retained only for backward compatibility purposes. This function generates an oolong test object based on \code{input_model} and \code{input_corpus}. If \code{input_model} is not NULL, it generates oolong test for a topic model (tm). If \code{input_model} is NULL but input_corpus is not NULL, it generates oolong test for generating gold standard (gs).
 #'
 #' @section Methods:
 #' An oolong object, depends on its purpose, has the following methods:
@@ -74,11 +77,19 @@ Oolong_test <- R6::R6Class(
 #' ## Creation of oolong test with only word intrusion test
 #' data(abstracts_stm)
 #' data(abstracts)
-#' oolong_test <- create_oolong(input_model = abstracts_stm)
+#' oolong_test <- wi(input_model = abstracts_stm, userid = "Hadley")
 #' ## Creation of oolong test with both word intrusion test and topic intrusion test
-#' oolong_test <- create_oolong(input_model = abstracts_stm, input_corpus = abstracts$text)
[…]

### 2021-05-15 tests/testthat/test-seededlda.R

@@ -59,3 +59,13 @@ test_that("unseeded lda: check_complete", {
     z <- create_oolong(abstracts_unseededlda)
     expect_error(z$lock())
 })
+
+## ui
+test_that("UI", {
+    expect_error(witi(abstracts_seededlda, abstracts$text), NA)
+    expect_error(witi(abstracts_unseededlda, abstracts$text), NA)
+    expect_error(ti(abstracts_seededlda, abstracts$text), NA)
+    expect_error(ti(abstracts_unseededlda, abstracts$text), NA)
+    expect_error(wi(abstracts_seededlda), NA)
+    expect_error(wi(abstracts_unseededlda), NA)
+})

### 2021-05-15 tests/testthat/test-ui.R

@@ -1,0 +1,140 @@
+## context("Support for topicmodels")
+
+genius_word <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    return(obj1)
+}
+
+genius_topic <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    return(obj1)
+}
+
+library(quanteda)
+library(BTM)
+abstracts_corpus <- corpus(abstracts$text)
+tokens(abstracts_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, split_hyphens = TRUE) %>%  tokens_tolower() %>% tokens_remove(stopwords("en")) %>% tokens_wordstem() -> toks_q
+as.data.frame.tokens <- function(x) {
+    data.frame(
+        doc_id = rep(names(x), lengths(x)),
+        tokens = unlist(x, use.names = FALSE)
+    )
+}
+abstracts_df <- as.data.frame.tokens(toks_q)
+
+
+test_that("wi basic", {
+    skip_on_cran()
+    expect_error(wi(abstracts_stm), NA)
+    expect_error(wi(abstracts_warplda), NA)
+    expect_error(wi(abstracts_btm), NA)
+    expect_error(wi(abstracts_keyatm), NA)
+})
+
+test_that("witi basic", {
+    skip_on_cran()
+    expect_error(witi(abstracts_stm, abstracts$text), NA)    
+    expect_error(witi(abstracts_warplda, abstracts$text))
+    expect_error(witi(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm), NA)
+    expect_error(witi(abstracts_btm, abstracts$text))
+    expect_error(witi(abstracts_btm, abstracts_corpus))
+    expect_error(witi(abstracts_btm, abstracts$text, btm_dataframe = abstracts_df))
+    expect_error(witi(abstracts_btm, abstracts_corpus, btm_dataframe = abstracts_df), NA)
+    expect_error(witi(abstracts_keyatm, abstracts$text), NA)
+})
+
+test_that("ti basic", {
+    skip_on_cran()
+    expect_error(ti(abstracts_stm, abstracts$text), NA)
+    expect_error(ti(abstracts_warplda, abstracts$text))
+    expect_error(ti(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm), NA)
[…]

### 2021-05-17 overview_gh.Rmd
add word set intrusion test, fix #33

@@
 | function | purpose                                                                                                                                |
-|---------:|:----------------------------------------------------------------------------------------------------------------------------|
-|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test)                                                   |
-|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test)                                                 |
+|---------:|:---------------------------------------------------------------------------------------------------------------------------------------|
+|   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test) (Chang et al., 2008)                                         |
+|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test) (Chang et al., 2008; aka "T8WSI" in Ying et al. forthcoming) |
 | `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test)            |
-|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard)                                                           |
+|  `wsi()` | validating a topic model with [word set intrusion test](#word-set-intrusion-test) (Ying et al. forthcoming)                              |
+|   `gs()` | oolong test for [creating gold standard](#creating-gold-standard) (see Song et al., 2020)                                              |
 
@@
 ```{r lock}
+oolong_test$lock()
+oolong_test
+```
+
+#### Word set intrusion test
+
+Word set intrusion test is a variant of word intrusion test (Ying et al., forthcoming), in which multiple word sets generated from top terms of one topic are juxtaposed with one intruder word set generated similarly from another topic.
+In Ying et al., this test is called "R4WSI" because 4 word sets are displayed.
+By default, oolong generates also R4WSI.
+However, it is also possible to generate R(N)WSI by setting the parameter `n_correct_ws` to N - 1.
+
+```{r wsi1}
+oolong_test <- wsi(abstracts_stm, userid = "Garrett")
+oolong_test
+```
+
+Use the method `$do_word_set_intrusion_test()` to start coding.
+
+```{r wsi2, eval = FALSE}
+oolong_test$do_word_set_intrusion_test()
+```
+
+```{r, include = FALSE}
+### Mock this process
+oolong_test$.__enclos_env__$private$test_content$wsi$answer <- oolong_test$.__enclos_env__$private$test_content$wsi$intruder
+oolong_test$.__enclos_env__$private$test_content$wsi$answer[1] <- "wronganswer"
+```
+
+```{r wsi3}
 oolong_test$lock()
@@
 [link](https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models)
-2.
+2. Ying, L., Montgomery, J. M., & Stewart, B. M. (Forthcoming). Inferring concepts from topics: Towards procedures for validating topics as measures. Political Analysis.
+3.
 Song et al.
@@
 [link](https://doi.org/10.1080/10584609.2020.1723752)
-3. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
-4.
+4. Bland, J. M., & Altman, D. (1986). Statistical methods for assessing agreement between two methods of clinical measurement. The lancet, 327(8476), 307-310.
+5.
 Chan et al.
@@
 [link](https://osf.io/preprints/socarxiv/np5wa/)
-5. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903. [link](https://arxiv.org/abs/1103.2903)
+6. Nielsen, F. Å. (2011). A new ANEW: Evaluation of a word list for sentiment analysis in microblogs. arXiv preprint arXiv:1103.2903. [link](https://arxiv.org/abs/1103.2903)
 

### 2021-05-17 R/oolong.R

@@ -4,7 +4,7 @@
 
 #' Oolong: create and administrate validation tests for typical automated content analysis tools
 #'
-#' The oolong package makes it very easy to create, administrate and evaluate typical automated content analysis tools by providing a framework for creating human-in-the-loop validation tests. For topic models, oolong can generate tests such as word intrusion test and topic intrusion test (Chang et al.). For dictionary-based methods, oolong can generate standardized interface for making gold standard ('Ground truth') data. There are only two core functions of this package: \code{\link{create_oolong}} and \code{\link{summarize_oolong}}.
+#' The oolong package makes it very easy to create, administrate and evaluate typical automated content analysis tools by providing a framework for creating human-in-the-loop validation tests. For topic models, oolong can generate tests such as word intrusion test, topic intrusion test (Chang et al.) and word set intrusion test (Ying et al.) For dictionary-based methods, oolong can generate standardized interface for making gold standard ('Ground truth') data.
 #' @docType package
 #' @author Chung-hong Chan
 #' @name oolong
@@ -38,11 +38,13 @@ Oolong_test <- R6::R6Class(
 
 #' Generate an oolong test
 #'
-#' \code{create_oolong} generates an oolong test object that can either be used for validating a topic model or for creating ground truth (gold standard) of a text corpus. \code{wi} (word intrusion test), \code{ti} (topic intrusion test), \code{witi} (word and topic intrusion tests) and \code{gs} are handy wrappers to \code{create_oolong}. It is recommended to use these wrappers instead of \code{create_oolong}.
+#' \code{create_oolong} generates an oolong test object that can either be used for validating a topic model or for creating ground truth (gold standard) of a text corpus. \code{wi} (word intrusion test), \code{ti} (topic intrusion test), \code{witi} (word and topic intrusion tests), \code{wsi} (word set intrusion test) and \code{gs} are handy wrappers to \code{create_oolong}. It is recommended to use these wrappers instead of \code{create_oolong}.
 #'
 #' @section Usage:
 #'
-#' Use \code{ti}, \code{ti}, \code{witi} or \code{gs} to generate an oolong test of your choice. It is recommended to supply also \code{userid} (current coder).
[…]

### 2021-05-17 R/oolong_summary.R

@@ -6,15 +6,15 @@
 #' 
 #' Print function displays the following information:
 #' \describe{
-#'   \item{Mean model precision}{(tm) Higher value indicates better topic interpretability}
-#'   \item{Quantiles of model precision}{(tm) Higher value indicates better topic interpretability}
-#'   \item{P-value of the model precision}{(tm) Model precision's p-value calculated by one-sample binomial test and Fisher's Omnibus method.}
-#'   \item{Krippendorff's alpha}{(gs/tm) Krippendorff's Alpha, if more than one oolong object is analyzed.}
-#'   \item{K Precision}{(tm) Model precision for each topic.}
-#'   \item{Mean TLO}{(tm) Mean topic log odds, higher value indicates better interpretability}
-#'   \item{Median TLO}{(tm) Median topic log odds, higher value indicates better interpretability}
-#'   \item{Quantiles of TLO}{(tm) Quantiles of topic log odds}
-#'   \item{P-Value of the median TLO}{(tm) Median topic log odds's p-value calculated by permutation test.}
+#'   \item{Mean model precision}{(wi, wsi) Higher value indicates better topic interpretability}
+#'   \item{Quantiles of model precision}{(wi) Higher value indicates better topic interpretability}
+#'   \item{P-value of the model precision}{(wi) Model precision's p-value calculated by one-sample binomial test and Fisher's Omnibus method.}
+#'   \item{Krippendorff's alpha}{(wi, wsi, gs) Krippendorff's Alpha, if more than one oolong object is analyzed.}
+#'   \item{K Precision}{(wi, wsi) Model precision for each topic.}
+#'   \item{Mean TLO}{(ti) Mean topic log odds, higher value indicates better interpretability}
+#'   \item{Median TLO}{(ti) Median topic log odds, higher value indicates better interpretability}
+#'   \item{Quantiles of TLO}{(ti) Quantiles of topic log odds}
+#'   \item{P-Value of the median TLO}{(ti) Median topic log odds's p-value calculated by permutation test.}
 #'   \item{Correlation (average answer)}{(gs) Pearson's correlation between average answer and target value}
 #'   \item{Corrlation (content length)}{(gs) Pearson's correlation between content length and target value}
 #' }
[…]

### 2021-05-17 R/oolong_tm.R

@@ -57,10 +57,10 @@
     )
 )
 
-.ren_word_intrusion_test <- function(output, test_content, res) {
+.ren_word_intrusion_test <- function(output, test_content, res, prompt = "Which of the following is an intruder word?") {
     .ren_choices <- function(test_content, res) {
         shiny::renderUI({
-            shiny::radioButtons("intruder", label = "Which of the following is an intruder word?", choices = test_content$candidates[[res$current_row]], selected = res$intruder[res$current_row])
+            shiny::radioButtons("intruder", label = prompt, choices = test_content$candidates[[res$current_row]], selected = res$intruder[res$current_row])
         })
     }
     .ren_topic_bar <- function(test_content, res) {
@@ -99,6 +99,10 @@
     output$current_topic <- .ren_topic_bar(test_content, res)
     output$text_content <- .ren_text_content(test_content, res)
     return(output)
+}
+
+.ren_word_set_intrusion_test <- function(output, test_content, res, prompt = "Which of the following is an intruder word set?") {
+    .ren_word_intrusion_test(output = output, test_content = test_content, res = res, prompt = prompt)
 }
 
 ### It must take a UI and render function. For new test_content type, please prepare a new pair of .UI_XXX_test (in cap) and .ren_xxx_test
@@ -214,7 +218,34 @@
     return(test_content)
 }
 
-.generate_test_content <- function(input_model, input_corpus = NULL, n_top_terms = 5, bottom_terms_percentile = 0.6, exact_n = NULL, frac = 0.01, n_top_topics = 3, n_topiclabel_words = 8, difficulty = 1, use_frex_words = FALSE, input_dfm = NULL, btm_dataframe = NULL, type = "witi") {
+.slice_sample <- function(x, n_topiclabel_words, n_correct_ws) {
+    res <- split(.safe_sample(x), ceiling(seq_along(x) / n_topiclabel_words))
+    names(res) <- NULL
+    labels <- purrr::map_chr(res, ~(paste(., collapse = ", ")))
+    .safe_sample(labels, n_correct_ws)
+}
+
+.generate_candidates_wsi <- function(i, terms, n_correct_ws = 3, n_topiclabel_words = 4, wsi_n_top_terms = 20) {
+    if (n_correct_ws * n_topiclabel_words > wsi_n_top_terms) {
[…]

### 2021-05-17 tests/testthat/test-defensive_programming.R

@@ -53,6 +53,16 @@ test_that("Can't launch $do_topic_intrusion_test() when no test content", {
     expect_error(x$do_topic_intrusion_test())
 })
 
+test_that("Can't launch $do_word_set_intrusion_test() when no test content", {
+    x <- create_oolong(abstracts_stm)
+    expect_error(x$do_word_set_intrusion_test())
+})
+
+test_that("Can't launch $do_word_intrusion_test() when no test content", {
+    x <- wsi(abstracts_stm)
+    expect_error(x$do_word_intrusion_test())
+})
+
 test_that("hash function", {
     expect_true(is.null(.safe_hash(NULL)))
     expect_type(.safe_hash(abstracts_stm), "character")

### 2021-05-17 tests/testthat/test-generate_test_content.R

@@ -37,3 +37,12 @@ test_that("generate_test_content type", {
     x <- oolong:::.generate_test_content(abstracts_stm, input_corpus = abstracts$text, type = 'ti')
     expect_null(x$word)
 })
+
+test_that("generate_test_content wsi", {
+    x <- oolong:::.generate_test_content(abstracts_stm, input_corpus = abstracts$text, n_topiclabel_words = 4, type = 'wsi')
+    expect_null(x$topic)
+    expect_null(x$words)
+    expect_false(is.null(x$wsi))
+    expect_error(oolong:::.generate_test_content(abstracts_stm, n_correct_ws = 10, n_topiclabel_words = 8, type = 'wsi'))
+    expect_error(oolong:::.generate_test_content(abstracts_stm, n_correct_ws = 10, n_topiclabel_words = 8, wsi_n_top_terms = 100,  type = 'wsi'), NA)
+})

### 2021-05-17 tests/testthat/test-printing.R

@@ -10,6 +10,11 @@ genius_topic <- function(obj1) {
     return(obj1)
 }
 
+genius_wsi <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$wsi$answer <- obj1$.__enclos_env__$private$test_content$wsi$intruder
+    return(obj1)
+}
+
 test_that("gs_creation", {
     ## output1 <- capture_output({ x <- create_oolong(input_corpus = abstracts$text); x }, print = TRUE)
     ## expect_true(stringr::str_detect(output1, "gold standard generation"))
@@ -35,4 +40,28 @@ test_that("check_calculation_topic_intrusion_multiobject (Printing)", {
 
 test_that("ti only", {
     expect_snapshot(create_oolong(input_model = abstracts_stm, input_corpus = abstracts$text, type = "ti"))
+})
+
+test_that("wsi only", {
+    expect_snapshot(create_oolong(input_model = abstracts_stm, input_corpus = abstracts$text, type = "wsi", wsi_n_top_terms = 100))
+})
+
+test_that("check_calculation_wsi_multiobject (printing)", {
+    obj1 <- wsi(abstracts_stm)
+    obj2 <- clone_oolong(obj1)
+    obj3 <- clone_oolong(obj1)
+    ## Mocking coding
+    obj1 <- genius_wsi(obj1)
+    obj1$lock()
+    obj2 <- genius_wsi(obj2)
+    obj2$.__enclos_env__$private$test_content$wsi$answer[1] <- "wronganswer"
+    obj2$lock()
+    obj3 <- genius_wsi(obj3)
+    obj3$.__enclos_env__$private$test_content$wsi$answer[1:4] <- "wronganswer"
+    obj3$lock()
+    res <- summarize_oolong(obj1, obj2, obj3)
+    expect_snapshot(res)
+    ### Single object
+    res <- summarize_oolong(obj1)
+    expect_snapshot(res)
 })

### 2021-05-17 tests/testthat/test-seededlda.R

@@ -68,4 +68,6 @@ test_that("UI", {
     expect_error(ti(abstracts_unseededlda, abstracts$text), NA)
     expect_error(wi(abstracts_seededlda), NA)
     expect_error(wi(abstracts_unseededlda), NA)
+    expect_error(wsi(abstracts_seededlda), NA)
+    expect_error(wsi(abstracts_unseededlda), NA)
 })

### 2021-05-17 tests/testthat/test-ui.R
fix a bug of ti when input_corpus is NULL, ref #49

@@ -33,7 +33,10 @@ test_that("wi basic", {
 
 test_that("witi basic", {
     skip_on_cran()
-    expect_error(witi(abstracts_stm, abstracts$text), NA)    
+    expect_error(witi(abstracts_stm, abstracts$text), NA)
+    ## We need to talk about how to handle these two.
+    expect_error(witi(abstracts_stm), NA)
+    expect_error(witi(abstracts_warplda), NA)
     expect_error(witi(abstracts_warplda, abstracts$text))
     expect_error(witi(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm), NA)
     expect_error(witi(abstracts_btm, abstracts$text))

### 2021-05-22 deploy.Rmd
adding tests

In oolong 0.3.22, functions for deploying oolong tests were added (`export_oolong`, `revert_oolong` etc.). These functions make it possible for the coders to conduct validation tests online using their browser, rather than having to install R on their computer.

The basic workflow is simple: 1) create an oolong test object as usual; 2) deploy the test online and obtain the URL to the test; 3) ask your coders to conduct the test online and send back the data file; 4) revert back the data file to an oolong object.

### 2021-05-23 deploy.Rmd
Complete deploy

@@
 
-The basic workflow is simple: 1) create an oolong test object as usual; 2) deploy the test online and obtain the URL to the test; 3) ask your coders to conduct the test online and send back the data file; 4) revert back the data file to an oolong object.
+The basic workflow is simple: 1) create the oolong test object as usual; 2) deploy the test online and obtain the URL to the test; 3) ask your coders to conduct the test online and send back the data file; 4) revert back from the data file to an oolong object.
+
+# Create an oolong test
+
+Please note that one cannot deploy oolong test objects with *both* word and topic intrusion tests, i.e.
+those created using `witi()` online.
+If you need to do both tests, you need to deploy them as two seperate instances: one created using `wi()` and another created using `ti()`.
+
+In this guide, we assume you want to deploy a word set intrusion test online.
+
+```{r}
+library(oolong)
+wsi_test <- wsi(abstracts_stm)
+wsi_test
+```
+
+# Deploy the test online
+
+First, you need to export the oolong test object as a stand alone Shiny app. This stand alone Shiny app will be in a directory.
+
+```{r}
+export_oolong(wsi_test, dir = "./wsi_test", use_full_path = FALSE)
+```
+
+The directory has only two files
+
+```{r}
+fs::dir_tree("./wsi_test")
+```
+
+This structure is called ["Single-file Shiny app."](https://shiny.rstudio.com/articles/app-formats.html) Experienced Shiny users might have their preferred method of deploying this app to whatever Shiny server they can master.
+
+For less experienced users, the simplest way to deploy this app online is to use [shinyapps.io](https://www.shinyapps.io/) (free tier available with 25 hours of computational time per month).
+Please register for an account at shinyapps.io and configure rsconnect.
+Please refer to [this guide](https://shiny.rstudio.com/articles/shinyapps.html) for more information.
+Please remember to configure the tokens.
+
+```r
+## replace <ACCOUNT>, <TOKEN>, <SECRET> with the information from your profile on Shinyapps.io: click Your name -> Tokens
+rsconnect::setAccountInfo(name="<ACCOUNT>", token="<TOKEN>", secret="<SECRET>")
+```
+
+For RStudio users, the simplest way to deploy the app to shinyapps.io is to first launch the app.
+
+```{r, eval = FALSE}
+library(shiny)
+runApp("./wsi_test")
+```
+
+And then click the **Publish** button at the right corner of the launched window.
+
+You will be asked for the title of the app, just give it a name, e.g. *wsi_test*. You probably can keep other default settings and push the **Publish** button to initialize the deployment process.
+
+<img src="figures/deploying_shinyappsio.png" align="center" height="400" />
+
+If there is no hiccup, you will get a URL to your deployed oolong test. Something like: *https://yourname.shinyapps.io/wsi_test/*
+
+# Conduct the test
+
+You can give the URL to your coders and they conduct the test with their browser online.
+The only difference of the deployed version is that, there will be a userid prompt and download button after the coding.
+
+<img src="figures/oolong_download.png" align="center"/>
+
+You should instruct your coders to download the data file after coding and return it to you. ^[Future versions might provide permanent storage]
+
+# Revert
+
+You can then obtain a locked oolong object from the original oolong and the downloaded data file.
+`revert_oolong` will do verfications with the original oolong object to make sure no error and no cheating.
+
+```{r, include = FALSE}
+wsi_test <- readRDS(system.file("extdata", "wsi_test.RDS", package = "oolong"))
+```
+
+```r
+revert_oolong(wsi_test, "oolong_2021-05-22 20 51 26 Hadley Wickham.RDS")
+```
+
+```{r, echo = FALSE}
+revert_oolong(wsi_test, system.file("extdata", "hadley.RDS", package = "oolong"))
+```
+
+```{r, include = FALSE}
+unlink("./wsi_test", recursive = TRUE)
+```

### 2021-05-23 R/oolong_shiny.R

@@ -278,6 +278,7 @@ deploy_oolong <- function(oolong) {
 #' @param oolong an oolong object to be exported. Please note that the "witi" type, i.e. oolong object with both word and topic intrusion tests, cannot be exported. Also the object must not be locked and ever coded.
 #' @param dir character string, the directory to be exported. Default to a temporary directory
 #' @param verbose logical, whether to display information after exporting
+#' @param use_full_path logical, whether to expand dir into full path
 #' @return directory exported, invisible
 #' @examples
 #' # Please try this example in interactive R sessions only.
@@ -288,14 +289,17 @@ deploy_oolong <- function(oolong) {
 #' }
 #' @author Chung-hong Chan
 #' @export
-export_oolong <- function(oolong, dir = base::tempdir(), verbose = TRUE) {
+export_oolong <- function(oolong, dir = base::tempdir(), verbose = TRUE, use_full_path = TRUE) {
     .mobilize_defend(oolong)
     if (!dir.exists(dir)) {
         dir.create(dir)
     }
+    if (use_full_path) {
+        dir <- base::path.expand(dir)
+    }
     file.copy(system.file("app", "app.R", package = "oolong"), dir, overwrite = TRUE)
     saveRDS(oolong, file = paste0(dir, "/oolong.RDS"))
-    .cp(verbose, "The Shiny has been written to the directory: ", base::path.expand(dir))
-    .cp(verbose, "You can test the app with: shiny::runApp(\"", base::path.expand(dir), "\")")
+    .cp(verbose, "The Shiny has been written to the directory: ", dir)
+    .cp(verbose, "You can test the app with: shiny::runApp(\"", dir, "\")")
     invisible(dir)
 }

### 2021-05-23 tests/testthat/test-deploy.R

@@ -1,0 +1,77 @@
+
+genius_word <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    return(obj1)
+}
+
+genius_topic <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    return(obj1)
+}
+
+genius_wsi <- function(obj1) {
+    obj1$.__enclos_env__$private$test_content$wsi$answer <- obj1$.__enclos_env__$private$test_content$wsi$intruder
+    return(obj1)
+}
+
+
+test_that("preconditions witi", {
+    expect_error(deploy_oolong(witi(abstracts_stm, abstracts$text)))
+    expect_error(export_oolong(witi(abstracts_stm, abstracts$text)))
+})
+
+test_that("preconditions coded", {
+    x <- wi(abstracts_stm)
+    expect_error(deploy_oolong(x), NA)
+    expect_error(export_oolong(x, verbose = FALSE), NA)
+    x <- genius_word(x)
+    expect_error(deploy_oolong(x))
+    expect_error(export_oolong(x))
+    x <- ti(abstracts_stm, abstracts$text)
+    expect_error(deploy_oolong(x), NA)
+    expect_error(export_oolong(x, verbose = FALSE), NA)
+    x <- genius_topic(x)
+    expect_error(deploy_oolong(x))
+    expect_error(export_oolong(x, verbose = FALSE))
+    x <- wsi(abstracts_stm)
+    expect_error(deploy_oolong(x), NA)
+    expect_error(export_oolong(x, verbose = FALSE), NA)
+    x <- genius_wsi(x)
+    expect_error(deploy_oolong(x))
+    expect_error(export_oolong(x))
+    x <- gs(abstracts$text)
+    expect_error(deploy_oolong(x), NA)
+    expect_error(export_oolong(x, verbose = FALSE), NA)
+    x$.__enclos_env__$private$test_content$gold_standard$answer <- 1
+    expect_error(deploy_oolong(x))
+    expect_error(export_oolong(x))
+})
+
+test_that("preconditions locked", {
+    x <- wi(abstracts_stm)
+    x$lock(force = TRUE)
+    expect_error(deploy_oolong(x))
+    expect_error(export_oolong(x))
[…]

### 2021-05-23 deploy_gh.Rmd
Adding deploy features, fix #23

--- 2021-05-23 deploy.Rmd
@@
+---
+title: "Deploy"
+output: github_document
+author:
+  - Chung-hong Chan ^[University of Mannheim]
+---
+
+```{r, include = FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  fig.path = "man/vignettes/figures/README-",
+  out.width = "100%"
+  )
+set.seed(42)
+```
 In oolong 0.3.22, functions for deploying oolong tests were added (`export_oolong`, `revert_oolong` etc.).
@@
 
-<img src="figures/deploying_shinyappsio.png" align="center" height="400" />
+<img src="vignettes/figures/deploying_shinyappsio.png" align="center" height="400" />
 
@@
 
-<img src="figures/oolong_download.png" align="center"/>
+<img src="vignettes/figures/oolong_download.png" align="center"/>
 

### 2021-05-23 R/oolong_summary_tm.R

@@ -21,7 +21,7 @@
     all(purrr::map_lgl(list(...), ~ .check_finished(.)))
 }
 
-### check whether the oolong object is in a new state. (i.e. Not yet coded in either word and topic tests.)
+### check whether the oolong object is in a new state. (i.e. Not yet coded in either word, topic and wsi tests.)
 .check_new <- function(oolong) {
     all(purrr::map_lgl(oolong$.__enclos_env__$private$test_content, ~is.null(.) | (!is.null(.) & all(is.na(.$answer)))))
 }

### 2021-05-23 tests/testthat/test-printing.R

@@ -65,3 +65,13 @@ test_that("check_calculation_wsi_multiobject (printing)", {
     res <- summarize_oolong(obj1)
     expect_snapshot(res)
 })
+
+test_that("export printing", {
+    skip_on_cran()
+    skip_on_ci()
+    obj1 <- wsi(abstracts_stm)
+    newdir <- "~/oolong_testing"
+    expect_snapshot(export_oolong(obj1, dir = newdir, verbose = TRUE, use_full_path = FALSE))
+    expect_snapshot(export_oolong(obj1, dir = newdir, verbose = FALSE, use_full_path = FALSE))
+    unlink(newdir, recursive = TRUE)
+})

### 2021-05-23 tests/testthat/test-ui.R

@@ -74,7 +74,7 @@ test_that("gs basic", {
 
 test_that("correct passing of n_top_terms",{
     skip_on_cran()
-    for (i in sample(2:10)) {
+    for (i in sample(2:10, 5)) {
         z <- witi(abstracts_stm, abstracts$text, n_top_terms = i)
         expect_equal(length(z$.__enclos_env__$private$test_content$word$candidates[[1]]), i + 1)
         z <- wi(abstracts_stm, abstracts$text, n_top_terms = i)
@@ -84,7 +84,7 @@ test_that("correct passing of n_top_terms",{
 
 test_that("correct passing of n_top_topics", {
     skip_on_cran()
-    for (i in sample(2:10)) {
+    for (i in sample(2:10, 3)) {
         z <- witi(abstracts_stm, abstracts$text, n_top_topics = i)
         expect_equal(length(z$.__enclos_env__$private$test_content$topic$candidates[[1]]), i + 1)
         z <- ti(abstracts_stm, abstracts$text, n_top_topics = i)
@@ -94,7 +94,7 @@ test_that("correct passing of n_top_topics", {
 
 test_that("correct passing of n_topiclabel_words", {
     skip_on_cran()
-    for (i in sample(2:10)) {
+    for (i in sample(2:10, 3)) {
         z <- witi(abstracts_stm, abstracts$text, n_topiclabel_words = i)
         topic_label <- z$.__enclos_env__$private$test_content$topic$topic_labels[[1]][1]
         expect_equal(length(strsplit(topic_label, ", ")[[1]]), i)
@@ -106,7 +106,7 @@ test_that("correct passing of n_topiclabel_words", {
 
 test_that("correct passing of n_topiclabel_words (wsi)", {
     skip_on_cran()
-    for (g in sample(2:10)) {
+    for (g in sample(2:10, 3)) {
         az <- wsi(abstracts_stm, n_topiclabel_words = g, wsi_n_top_terms = 50)
         ws_topic_label <- az$.__enclos_env__$private$test_content$wsi$candidates[[1]][1]
         expect_equal(length(strsplit(ws_topic_label, ", ")[[1]]), g)
@@ -124,7 +124,7 @@ test_that("correct passing of construct", {
 
 test_that("correct passing of exact_n", {
     skip_on_cran()
-    for (i in sample(5:90, size = 10)) {
+    for (i in sample(5:90, size = 3)) {
[…]

### 2021-05-26 README.Rmd
Complete deploy
finalize naming

--- 2020-11-12 README.Rmd
@@
 [![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
-[![zenodo](https://zenodo.org/badge/224468858.svg)](https://zenodo.org/badge/latestdoi/224468858)
 [![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
+[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
 <!-- badges: end -->
@@
 
-Please refer to the [overview](overview_gh.md) for an introduction to this package. If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
+Please refer to the [overview](overview_gh.md) for an introduction to this package.
+If you need to deeploy the test online, please refer to the [Deployment Vignette](deploy_gh.md).
+If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
 
@@
 
-Chan et al., (2020).
+Chan C-h.
+& Sältzer M., (2020).
 oolong: An R package for validating  automated content analysis tools.

### 2021-05-26 vig_body.Rmd
fix a bug of ti when input_corpus is NULL, ref #49
finalize naming

@@
 ### Mock this process
-oolong_test$.__enclos_env__$private$test_content$word$answer <- oolong_test$.__enclos_env__$private$test_content$word$intruder
-oolong_test$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
+oolong_test$.__enclos_env__$private$test_content$wi$answer <- oolong_test$.__enclos_env__$private$test_content$wi$intruder
+oolong_test$.__enclos_env__$private$test_content$wi$answer[1] <- "wronganswer"
 ```
@@
 genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
     return(obj1)
@@
 genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
     return(obj1)
@@
 oolong_test <- genius_word(genius_topic(oolong_test))
-oolong_test$.__enclos_env__$private$test_content$topic$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$topic$candidates[[2]], 1)
+oolong_test$.__enclos_env__$private$test_content$ti$answer[2] <- sample(oolong_test$.__enclos_env__$private$test_content$ti$candidates[[2]], 1)
 oolong_test$lock()
@@
 ### Just word intrusion test.
-oolong_test <- ti(abstracts_warplda, userid = "Lionel")
+oolong_test <- wi(abstracts_warplda, userid = "Lionel")
 oolong_test
@@
 ```{r, include = FALSE}
-oolong_test$.__enclos_env__$private$test_content$gold_standard <- 
+oolong_test$.__enclos_env__$private$test_content$gs <- 
 structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
@@
 ```{r, include = FALSE}
-trump$.__enclos_env__$private$test_content$gold_standard <- 
+trump$.__enclos_env__$private$test_content$gs <- 
 structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 
@@
 
-trump2$.__enclos_env__$private$test_content$gold_standard <- 
+trump2$.__enclos_env__$private$test_content$gs <- 
 structure(list(case = 1:20, text = c("Thank you Eau Claire, Wisconsin. \n#VoteTrump on Tuesday, April 5th!\nMAKE AMERICA GREAT AGAIN! https://t.co/JI5JqwHnMC", 

### 2021-05-26 R/oolong_data_misc.R

@@ -44,7 +44,7 @@
 #' @importFrom quanteda print corpus
 NULL
 
-utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'avg_answer'))
+utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'avg_answer', 'abstracts_stm', 'abstracts'))
 
 ### print the ... if boolean_test is true
 .cp <- function(boolean_test, ...) {
@@ -79,13 +79,6 @@ utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'a
          )
 }
 
-## For future update, to notify users about old version and run update_oolong.
-.check_version <- function(private) {
-    ## if (private$meta$`package-version` < "0.4") {
-    ##     cli::cli_alert_warning("This object was created using an old version of oolong. Please update this object using update_oolong().")
-    ## }
-}
-
 .sym_flip <- function(bool) {
     ifelse(bool, cli::symbol$tick, cli::symbol$cross)
 }
@@ -96,3 +89,4 @@ utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'a
     }
     return(digest::digest(x, algo = "sha1"))
 }
+

### 2021-05-26 tests/testthat/test-printing.R

@@ -75,3 +75,16 @@ test_that("export printing", {
     expect_snapshot(export_oolong(obj1, dir = newdir, verbose = FALSE, use_full_path = FALSE))
     unlink(newdir, recursive = TRUE)
 })
+
+test_that("update", {
+    skip_on_cran()
+    y <- readRDS("../testdata/oolong_tm_prev4.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/oolong_gs_prev4.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/oolong_gs_prev4_locked.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/massive_oolong_old.RDS")
+    expect_snapshot_error(print(y))
+    expect_snapshot(update_oolong(y))
+})

### 2021-05-26 R/oolong_shiny.R
Merge #56 and close #50
Also provide update_oolong and check_oolong

@@ -1,31 +1,31 @@
-.code_oolong <- function(test_content, ui = .UI_WORD_INTRUSION_TEST, .ren = .ren_word_intrusion_test) {
-    shiny::runGadget(.gen_shinyapp(test_content = test_content, ui = ui, .ren = .ren, hash = NULL))
+.code_oolong <- function(test_items, ui = .UI_WORD_INTRUSION_TEST, .ren = .ren_word_intrusion_test) {
+    shiny::runGadget(.gen_shinyapp(test_items = test_items, ui = ui, .ren = .ren, hash = NULL))
 }
 
-.do_oolong_test <- function(test_content, ui = .UI_WORD_INTRUSION_TEST, .ren = .ren_word_intrusion_test) {
-    test_content$answer <- .code_oolong(test_content, ui = ui, .ren = .ren)
-    return(test_content)
+.do_oolong_test <- function(test_items, ui = .UI_WORD_INTRUSION_TEST, .ren = .ren_word_intrusion_test) {
+    test_items$answer <- .code_oolong(test_items, ui = ui, .ren = .ren)
+    return(test_items)
 
 }
 
-.gen_shinyserver <- function(test_content, .ren = .ren_word_intrusion_test, hash = NULL) {
+.gen_shinyserver <- function(test_items, .ren = .ren_word_intrusion_test, hash = NULL) {
     function(input, output, session) {
-        res <- shiny::reactiveValues(intruder = test_content$answer, current_row = 1)
-        output <- .ren(output, test_content, res, hash = hash)
+        res <- shiny::reactiveValues(intruder = test_items$answer, current_row = 1)
+        output <- .ren(output, test_items, res, hash = hash)
         shiny::observeEvent(input$confirm, {
             res$intruder[res$current_row] <- input$intruder
             res$current_row <- res$current_row + 1
-            if (res$current_row > nrow(test_content)) {
+            if (res$current_row > nrow(test_items)) {
                 res$current_row <- 1
             }
-            output <- .ren(output, test_content, res, hash = hash)
+            output <- .ren(output, test_items, res, hash = hash)
         })
         shiny::observeEvent(input$nextq, {
             res$current_row <- res$current_row + 1
-            if (res$current_row > nrow(test_content)) {
+            if (res$current_row > nrow(test_items)) {
                 res$current_row <- 1
             }
-            output <- .ren(output, test_content, res, hash = hash)
+            output <- .ren(output, test_items, res, hash = hash)
         })
         shiny::observeEvent(input$ff, {
[…]

### 2021-05-26 R/oolong_summary_gs.R

@@ -32,7 +32,7 @@
 
 .summarize_oolong_gs <- function(..., target_value = NULL, plot = TRUE) {
     obj_list <- list(...)
-    answers <- purrr::map_dfc(obj_list, ~.$.__enclos_env__$private$test_content$gold_standard$answer)
+    answers <- purrr::map_dfc(obj_list, ~.$.__enclos_env__$private$test_content$gs$answer)
     colnames(answers) <- paste0("answer", seq_len(ncol(answers)))
     avg_answer <- apply(answers, 1, mean)
     answers$avg_answer <- avg_answer

### 2021-05-26 tests/testthat/test-defensive_programming.R

@@ -1,12 +1,12 @@
 ##context("Defensive program")
 
 genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
     return(obj1)
 }
 
 genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
     return(obj1)
 }
 
@@ -52,26 +52,26 @@ test_that("cloning all types", {
     ## pure wi
     x <- wi(abstracts_stm)
     expect_error(clone_oolong(x), NA)
-    x$.__enclos_env__$private$test_content$word$answer[1] <- "x"
+    x$.__enclos_env__$private$test_content$wi$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## pure ti
     x <- ti(abstracts_stm, abstracts$text)
     expect_error(clone_oolong(x), NA)
-    x$.__enclos_env__$private$test_content$topic$answer[1] <- "x"
+    x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## witi
     x <- witi(abstracts_stm, abstracts$text)
     expect_error(clone_oolong(x), NA)
-    x$.__enclos_env__$private$test_content$topic$answer[1] <- "x"
+    x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
     x <- witi(abstracts_stm, abstracts$text)
     expect_error(clone_oolong(x), NA)
-    x$.__enclos_env__$private$test_content$word$answer[1] <- "x"
+    x$.__enclos_env__$private$test_content$wi$answer[1] <- "x"
     expect_error(clone_oolong(x))
     x <- witi(abstracts_stm, abstracts$text)
     expect_error(clone_oolong(x), NA)
-    x$.__enclos_env__$private$test_content$word$answer[1] <- "x"
-    x$.__enclos_env__$private$test_content$topic$answer[1] <- "x"
[…]

### 2021-05-26 tests/testthat/test-printing.R

@@ -1,12 +1,12 @@
 ## context("Prining objects")
 
 genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
     return(obj1)
 }
 
 genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
     return(obj1)
 }
 
@@ -74,4 +74,17 @@ test_that("export printing", {
     expect_snapshot(export_oolong(obj1, dir = newdir, verbose = TRUE, use_full_path = FALSE))
     expect_snapshot(export_oolong(obj1, dir = newdir, verbose = FALSE, use_full_path = FALSE))
     unlink(newdir, recursive = TRUE)
+})
+
+test_that("update", {
+    skip_on_cran()
+    y <- readRDS("../testdata/oolong_tm_prev4.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/oolong_gs_prev4.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/oolong_gs_prev4_locked.RDS")
+    expect_snapshot(update_oolong(y))
+    y <- readRDS("../testdata/massive_oolong_old.RDS")
+    expect_snapshot_error(print(y))
+    expect_snapshot(update_oolong(y))
 })

### 2021-05-26 tests/testthat/test-revert.R

@@ -6,7 +6,8 @@ test_that("case in vignette", {
 })
 
 massive_oolong <- readRDS("../testdata/massive_oolong.RDS")
-all_downloads_rds <- list.files("../testdata/downloaded/", full.names = TRUE)
+all_downloads_rds <- list.files("../testdata/downloaded", full.names = TRUE)
+
 
 test_that("big_revert", {
     expect_error(purrr::map(all_downloads_rds, ~revert_oolong(massive_oolong, .)), NA)

### 2021-05-26 tests/testthat/test-summarize_oolong.R

@@ -1,12 +1,12 @@
 ## context("summarize_oolong")
 
 genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
     return(obj1)
 }
 
 genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
     return(obj1)
 }
 
@@ -22,7 +22,7 @@ test_that("Correct UI", {
     obj1$lock()
     res1 <- summarize_oolong(obj1)
     expect_true(res1$type == "tm")
-    obj2$.__enclos_env__$private$test_content$gold_standard$answer <- sample(1:5, size = 20, replace = TRUE)
+    obj2$.__enclos_env__$private$test_content$gs$answer <- sample(1:5, size = 20, replace = TRUE)
     obj2$lock()
     res2 <- summarize_oolong(obj2, target_value = rnorm(n = 20))
     expect_true(res2$type == "gs")
@@ -36,10 +36,10 @@ test_that("check_calculation_word_intrusion_multiobject", {
     obj1 <- genius_word(obj1)
     obj1$lock()
     obj2 <- genius_word(obj2)
-    obj2$.__enclos_env__$private$test_content$word$answer[1] <- "wronganswer"
+    obj2$.__enclos_env__$private$test_content$wi$answer[1] <- "wronganswer"
     obj2$lock()
     obj3 <- genius_word(obj3)
-    obj3$.__enclos_env__$private$test_content$word$answer[1:4] <- "wronganswer"
+    obj3$.__enclos_env__$private$test_content$wi$answer[1:4] <- "wronganswer"
     obj3$lock()
     res <- summarize_oolong(obj1, obj2, obj3)
     expect_length(res$rater_precision, 3)
@@ -109,7 +109,7 @@ test_that("Forcibly locking", {
     ex1$lock()
     ex2 <- genius_word(ex2)
     ex2 <- genius_topic(ex2)
-    ex2$.__enclos_env__$private$test_content$topic$answer[1] <- NA
[…]

### 2021-05-26 tests/testthat/test-topicmodels.R

@@ -1,34 +1,34 @@
 ## context("Support for topicmodels")
 
 genius_word <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$word$answer <- obj1$.__enclos_env__$private$test_content$word$intruder
+    obj1$.__enclos_env__$private$test_content$wi$answer <- obj1$.__enclos_env__$private$test_content$wi$intruder
     return(obj1)
 }
 
 genius_topic <- function(obj1) {
-    obj1$.__enclos_env__$private$test_content$topic$answer <- obj1$.__enclos_env__$private$test_content$topic$intruder
+    obj1$.__enclos_env__$private$test_content$ti$answer <- obj1$.__enclos_env__$private$test_content$ti$intruder
     return(obj1)
 }
 
 test_that("generate_test_content", {
     skip_on_cran()
     x <- oolong:::.generate_test_content(abstracts_topicmodels)
-    expect_null(x$topic)
+    expect_null(x$ti)
     x <- oolong:::.generate_test_content(abstracts_topicmodels, quanteda::corpus(abstracts$text))
-    expect_false(is.null(x$topic))
+    expect_false(is.null(x$ti))
 })
 
 test_that("check_complete", {
     skip_on_cran()
     x <- oolong:::.generate_test_content(abstracts_topicmodels)
     expect_false(oolong:::.check_test_content_complete(x))
-    x$word$answer <- 1
+    x$wi$answer <- 1
     expect_true(oolong:::.check_test_content_complete(x))
     y <- oolong:::.generate_test_content(abstracts_topicmodels, abstracts$text)
     expect_false(oolong:::.check_test_content_complete(y))
-    y$topic$answer <- 1
+    y$ti$answer <- 1
     expect_false(oolong:::.check_test_content_complete(y))
-    y$word$answer <- 1
+    y$wi$answer <- 1
     expect_true(oolong:::.check_test_content_complete(y))
     z <- create_oolong(abstracts_topicmodels)
     expect_error(z$lock())

### 2021-05-27 overview_gh.Rmd
naive bayes support, merge #41 fix #43

@@
 `abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
-Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM` and seeded LDA models from `seededlda`.
+Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM`, and seeded LDA models from `seededlda`.
+Although not strictly a topic model, Naive Bayes models from `quanteda.textmodels` are also supported.
+See the section on [Naive Bayes](#about-naive-bayes) for more information.
 
@@
 Please refer to the vignette about BTM.
+
+## About Naive Bayes
+
+Naive Bayes model is a supervised machine learning model. This package supports Naive Bayes models trained using `quanteda.textmodels`.
+
+Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classical [20 newgroups] dataset.
+
+```r
+tokens(newsgroup5$text, remove_punct = TRUE, remove_symbols = TRUE, remove_numbers = TRUE, remove_url = TRUE, spilit_hyphens = TRUE) %>% tokens_wordstem %>% tokens_remove(stopwords("en")) %>% dfm(tolower = TRUE) %>% dfm_trim(min_termfreq = 3, max_docfreq = 0.06, docfreq_type = "prop") -> newsgroup_dfm
+docvars(newsgroup_dfm, "group") <- newsgroup5$title
+newsgroup_nb <- textmodel_nb(newsgroup_dfm, docvars(newsgroup_dfm, "group"), distribution = "Bernoulli")
+```
+
+You can still generate word intrusion and word set intrusion tests.
+
+```{r}
+wi(newsgroup_nb)
+```
+
+```{r}
+wsi(newsgroup_nb)
+```
 

### 2021-05-27 R/oolong.R

@@ -60,7 +60,7 @@ Oolong_test <- R6::R6Class(
 #'   \item{\code{$turn_gold()}}{(gs) convert the oolong object into a quanteda compatible corpus.}
 #' }
 #' For more details, please see the overview vignette: \code{vignette("overview", package = "oolong")}
-#' @param input_model (wi, ti, witi, wsi) a STM, WarpLDA, topicmodels, KeyATM, seededlda or BTM object; if it is NULL, create_oolong assumes that you want to create gold standard.
+#' @param input_model (wi, ti, witi, wsi) a STM, WarpLDA, topicmodels, KeyATM, seededlda, textmodel_nb, or BTM object; if it is NULL, create_oolong assumes that you want to create gold standard.
 #' @param input_corpus (wi, ti, witi, wsi, gs) if input_model is not null, it should be the corpus (character vector or quanteda::corpus object) to generate the model object. If input_model and input_corpus are not NULL, topic intrusion test cases are generated. If input_model is a BTM object, this argument is ignored. If input_model is null, it generates gold standard test cases.
 #' @param n_top_terms (wi, witi) integer, number of top topic words to be included in the candidates of word intrusion test. 
 #' @param bottom_terms_percentile (wi, witi) double, a term is considered to be an word intruder when its theta less than the percentile of this theta, must be within the range of 0 to 1
@@ -115,7 +115,7 @@ create_oolong <- function(input_model = NULL, input_corpus = NULL, n_top_terms =
     }
     if (!is.null(input_model)) {
         if (!.is_topic_model(input_model)) {
-            stop("input_model is not a topic model. If you want to create gold standard with an input_corpus, use: create_oolong(input_corpus = input_corpus)")
+            stop("input_model is not a topic model. If you want to create gold standard with an input_corpus, use: create_oolong(input_corpus = input_corpus) or gs(input_corpus)")
         }
     }
     if (length(userid) > 1) {

### 2021-05-27 R/oolong_data_misc.R

@@ -39,6 +39,13 @@
 #' This is a random sample of 2000 tweets from @realdonaldtrump account before his assumption of duty as the president of the United States.
 "trump2k"
 
+#' Naive Bayes model trained on 20 newsgroups data
+#'
+#' This is a Naive Bayes model (of the class 'textmodel_nb') trained on 20 newsgroups data.
+#' @references
+#'   Lang, K. (1995). Newsweeder: Learning to filter netnews. In Machine Learning Proceedings 1995 (pp. 331-339). Morgan Kaufmann.
+"newsgroup_nb"
+
 #' @importFrom stats cooks.distance cor.test lm median pchisq quantile sd predict
 #' @importFrom utils head
 #' @importFrom quanteda print corpus

### 2021-05-27 R/oolong_formats.R

@@ -1,6 +1,6 @@
 
 .is_topic_model <- function(x) {
-    if (any(class(x) %in% c("WarpLDA", "STM", "BTM", "keyATM_output","textmodel_lda"))) {
+    if (any(class(x) %in% c("WarpLDA", "STM", "BTM", "keyATM_output","textmodel_lda", "textmodel_nb"))) {
         return(TRUE)
     }
     if (is.null(attr(class(x), "package"))) {
@@ -25,6 +25,8 @@
         class(output) <- append(class(output), "input_model_s3_warplda")
     } else if ("textmodel_lda" %in% class(input_model)) {
         class(output) <- append(class(output), "input_model_s3_seededlda")
+    } else if ("textmodel_nb" %in% class(input_model)) {
+        class(output) <- append(class(output), "input_model_s3_nb")
     } else if ("STM" %in% class(input_model)) {
         class(output) <- append(class(output), "input_model_s3_stm")
     } else if ("BTM" %in% class(input_model)) {
@@ -33,8 +35,7 @@
         class(output) <- append(class(output), "input_model_s3_keyatm")
     } else if ("topicmodels" == attr(class(input_model), "package")) {
         class(output) <- append(class(output), "input_model_s3_topicmodels")
-    }
-    
+    }    
     return(output)
 }
 

### 2021-05-27 abstract.R

@@ -1,123 +1,0 @@
-require(tidyverse)
-require(quanteda)
-require(stm)
-require(oolong)
-devtools::load_all()
-
-## abstracts <- readRDS("~/dev/jcmc/finalsample.RDS")
-## set.seed(46709394)
-## abstracts %>% sample_n(2500) %>% mutate(text = abstract) %>% select(text) -> abstracts
-
-## usethis::use_data(abstracts, overwrite = TRUE)
-
-
-dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 3, max_docfreq = 500) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
-
-usethis::use_data(abstracts_dfm, overwrite = TRUE)
-
-abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm_data
-
-abstracts_stm <- stm(abstracts_stm_data$documents, abstracts_stm_data$vocab, data =abstracts_stm_data$meta, K = 20, seed = 46709394)
-
-usethis::use_data(abstracts_stm, overwrite = TRUE)
-
-require(text2vec)
-lda_model <- LDA$new(n_topics = 20, doc_topic_prior = 0.1, topic_word_prior = 0.01)
-
-theta <- lda_model$fit_transform(x = abstracts_dfm, convergence_tol = 0.001, n_check_convergence = 25)
-
-abstracts_warplda <- lda_model
-
-usethis::use_data(abstracts_warplda, overwrite = TRUE)
-
-lsa_model <- LSA$new(n_topics = 20)
-
-###
-require(topicmodels)
-
-abstracts_tm <- convert(abstracts_dfm, to = "topicmodels")
-
-abstracts_topicmodels <- LDA(abstracts_tm, k = 20)
-
-usethis::use_data(abstracts_topicmodels, overwrite = TRUE)
-
-require(BTM)
-
-### Use the quanteda method suggested by Benoit.
-### https://github.com/quanteda/quanteda/issues/1404
-
-## TODO: removal of dense terms. 
[…]

### 2021-05-27 rawdata/trump.R

@@ -1,0 +1,7 @@
+devtools::load_all()
+
+oolong_test <- readRDS('trump_coded.RDS')
+
+oolong_test$lock()
+
+oolong_test$turn_gold()

### 2021-05-27 trump.R

@@ -1,7 +1,0 @@
-devtools::load_all()
-
-oolong_test <- readRDS('trump_coded.RDS')
-
-oolong_test$lock()
-
-oolong_test$turn_gold()

### 2021-05-27 R/oolong_shiny.R
testing shinytest on CI, ref #10

@@ -13,7 +13,6 @@
         res <- shiny::reactiveValues(intruder = test_items$answer, current_row = 1)
         output <- .ren(output, test_items, res, hash = hash)
         shiny::observeEvent(input$confirm, {
-            print(input$intruder)
             if (!is.null(input$intruder)) {
                 res$intruder[res$current_row] <- input$intruder
                 res$current_row <- res$current_row + 1

### 2021-05-29 deploy.Rmd
Bump version; update NEWS; ready for CRAN

@@
 those created using `witi()` online.
-If you need to do both tests, you need to deploy them as two seperate instances: one created using `wi()` and another created using `ti()`.
+If you need to do both tests, you need to deploy them as two separate instances: one created using `wi()` and another created using `ti()`.
 
@@
 You can then obtain a locked oolong object from the original oolong and the downloaded data file.
-`revert_oolong` will do verfications with the original oolong object to make sure no error and no cheating.
+`revert_oolong` will do verifications with the original oolong object to make sure no error and no cheating.
 

### 2021-05-29 R/oolong_shiny.R

@@ -241,7 +241,7 @@
 
 #' Deploy an oolong test
 #' 
-#' In most of the time, you should not use this function. You should write the deployable version of your app into a directory using \code{export_oolong} instead. Please refer to the deployment guide for more details.
+#' In most of the time, you should not use this function. You should write the deployable version of your app into a directory using \code{export_oolong} instead. Please refer to \code{vignette("deploy", package = "oolong")} for more details.
 #' @param oolong an oolong object to be deployed. Please note that the "witi" type, i.e. oolong object with both word and topic intrusion tests, cannot be deployed. Also the object must not be locked and ever coded.
 #' @return Nothing, it launches a deployable version of the coding interface
 #' @examples
@@ -272,7 +272,7 @@ deploy_oolong <- function(oolong) {
 
 #' Export a deployable Shiny app from an oolong object into a directory
 #' 
-#' This function exports your oolong test into a launched Shiny app that is ideal for online deployment. Deploying the Shiny app online allows coders to conduct the test online with their browser, rather than having to install R on their own computer. In constrast to the testing interfaces launched with methods such as \code{$do_word_intrusion_test()}, the deployable version provides data download after the coder finished coding. Downloaded data can then revert back to a locked oolong object using \code{revert_oolong}. Further version might provide solutions to permanent storage. The deployable Shiny app will be in a directory. The Shiny app is both launchable with shiny::runApp() and deployable with rsconnect::deployApp(). See the deployment guide for more details.
+#' This function exports your oolong test into a launched Shiny app that is ideal for online deployment. Deploying the Shiny app online allows coders to conduct the test online with their browser, rather than having to install R on their own computer. In contrast to the testing interfaces launched with methods such as \code{$do_word_intrusion_test()}, the deployable version provides data download after the coder finished coding. Downloaded data can then revert back to a locked oolong object using \code{revert_oolong}. Further version might provide solutions to permanent storage. The deployable Shiny app will be in a directory. The Shiny app is both launchable with shiny::runApp() and deployable with rsconnect::deployApp(). Please refer to \code{vignette("deploy", package = "oolong")} for more details.
 #' @param oolong an oolong object to be exported. Please note that the "witi" type, i.e. oolong object with both word and topic intrusion tests, cannot be exported. Also the object must not be locked and ever coded.
 #' @param dir character string, the directory to be exported. Default to a temporary directory
 #' @param verbose logical, whether to display information after exporting

### 2021-05-31 overview_gh.Rmd
testing shinytest on CI, ref #10
Bump version; update NEWS; ready for CRAN
Make abstracts_keyatm the 'default' topic model to save space; various fixes for CRAN

@@
 
-`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package.
+`abstracts_keyatm` is an example topic model trained with the data `abstracts` using the `keyATM` package.
 Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM`, and seeded LDA models from `seededlda`.
@@
 library(oolong)
-library(stm)
+library(keyATM)
 library(quanteda)
@@
 ```{r example}
-abstracts_stm
+abstracts_keyatm
 ```
@@
 ```{r createtest}
-oolong_test <- wi(abstracts_stm, userid = "Hadley")
+oolong_test <- wi(abstracts_keyatm, userid = "Hadley")
 oolong_test
@@
 ```{r wsi1}
-oolong_test <- wsi(abstracts_stm, userid = "Garrett")
+oolong_test <- wsi(abstracts_keyatm, userid = "Garrett")
 oolong_test
@@
 
-For example, `abstracts_stm` was generated with the corpus `abstracts$text`
+For example, `abstracts_keyatm` was generated with the corpus `abstracts$text`
 
@@
 ```{r createtest2}
-oolong_test <- ti(abstracts_stm, abstracts$text, userid = "Julia")
+oolong_test <- ti(abstracts_keyatm, abstracts$text, userid = "Julia")
 oolong_test
@@
 
+Preprocess and create a document-feature matrix
+
+```{r, eval = FALSE}
+dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 3, max_docfreq = 500) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
+```
+
 Train a topic model.
@@
 ```{r step0, eval = FALSE}
-dfm(abstracts$text, tolower = TRUE, stem = TRUE, remove = stopwords('english'), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, remove_hyphens = TRUE) %>% dfm_trim(min_docfreq = 5, max_docfreq = 1000) %>% dfm_select(min_nchar = 3, pattern = "^[a-zA-Z]+$", valuetype = "regex") -> abstracts_dfm
-docvars(abstracts_dfm, "title") <- abstracts$title
-abstracts_dfm %>% convert(to = "stm", omit_empty = FALSE) -> abstracts_stm
-abstracts_stm <- stm(abstracts_stm$documents, abstracts_stm$vocab, data =abstracts_stm$meta, K = 10, seed = 42)
+require(keyATM)
+abstracts_keyatm <- keyATM(keyATM_read(abstracts_dfm), no_keyword_topics = 0, keywords = abstracts_dictionary, model = "base", options = list(seed = 46709394))
 ```
@@
 ```{r step1}
-oolong_test_rater1 <- witi(abstracts_stm, abstracts$text, userid = "Yihui")
+oolong_test_rater1 <- witi(abstracts_keyatm, abstracts$text, userid = "Yihui")
 ```
@@
 
-Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classical [20 newgroups] dataset.
+Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classic [20 newsgroups] dataset.
 

### 2021-05-31 R/oolong_data_misc.R

@@ -1,7 +1,7 @@
 
 #' Abstracts of communication journals dataset
 #'
-#' This is a random sample of all abstracts of papers published in high-impact communication journals from 2000 to 2017. The one ends with "dfm" is the same data in quanteda::dfm (document-feature matrix) format. abstracts_dictionary is a list of terms that can be used for semisupervised techniques such as keyATM.
+#' This is a random sample of all abstracts of papers published in high-impact communication journals from 2000 to 2017. abstracts_dictionary is a list of terms that can be used for semisupervised techniques such as keyATM.
 #' @references
 #'   Chan, C-h, & Grill, C. (2020). [The Highs in Communication Research: Research Topics With High Supply, High Popularity, and High Prestige in High-Impact Journals.](https://doi.org/10.1177/0093650220944790) Communication Research.
 "abstracts"
@@ -15,17 +15,13 @@
 #' Topic models trained with the abstracts dataset.
 #'
 #' These are topic models trained with different topic model packages.
-"abstracts_stm"
-
-#' @rdname abstracts_stm
-"abstracts_warplda"
-
-#' @rdname abstracts_stm
-"abstracts_btm"
-
-#' @rdname abstracts_stm
 "abstracts_keyatm"
 
+#' @rdname abstracts_keyatm
+"abstracts_warplda"
+
+#' @rdname abstracts_keyatm
+"abstracts_btm"
 
 #' AFINN dictionary
 #'
@@ -51,7 +47,7 @@
 #' @importFrom quanteda print corpus
 NULL
 
-utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'avg_answer', 'abstracts_stm', 'abstracts'))
+utils::globalVariables(c('cookd', 'diffxy', 'index', 'meanxy', 'word_length', 'avg_answer', 'abstracts_keyatm', 'abstracts'))
 
 ### print the ... if boolean_test is true
 .cp <- function(boolean_test, ...) {

### 2021-05-31 R/oolong_update.R

@@ -42,7 +42,7 @@ update_oolong <- function(oolong, verbose = TRUE) {
     .cstop(!.check_oolong(oolong$.__enclos_env__$private), "This oolong object does not need to be updated.")
     if ("oolong_test_tm" %in% class(oolong)) {
         ## generate a dummy oolong object
-        new_oolong <- create_oolong(abstracts_stm)
+        new_oolong <- create_oolong(abstracts_keyatm)
         new_oolong$.__enclos_env__$private$finalized <- oolong$.__enclos_env__$private$finalized
         new_oolong$.__enclos_env__$private$test_content <- oolong$.__enclos_env__$private$test_content
         ## renaming test_content

### 2021-05-31 tests/testthat/test-defensive_programming.R

@@ -19,10 +19,10 @@ test_that("precondiction", {
 
 test_that("locking", {
     ## premature locking
-    x <- create_oolong(abstracts_stm)
+    x <- create_oolong(abstracts_keyatm)
     expect_error(x$lock())
     expect_error(x$lock(force = TRUE), NA)
-    x <- create_oolong(abstracts_stm, abstracts$text)
+    x <- create_oolong(abstracts_keyatm, abstracts$text)
     expect_error(x$lock())
     ## error when only word intrusion test is done.
     x <- genius_word(x)
@@ -32,16 +32,16 @@ test_that("locking", {
 })
 
 test_that("cloning", {
-    x <- create_oolong(abstracts_stm)
+    x <- create_oolong(abstracts_keyatm)
     expect_error(clone_oolong(x), NA)
     x <- genius_word(x)
     ## Cannot clone a partially coded object.
     expect_error(clone_oolong(x))
-    x <- create_oolong(abstracts_stm)
+    x <- create_oolong(abstracts_keyatm)
     x$lock(force = TRUE)
     expect_error(clone_oolong(x))
     ## Cloned object is not sharing the same private space.
-    x <- create_oolong(abstracts_stm)
+    x <- create_oolong(abstracts_keyatm)
     y <- clone_oolong(x)
     x$lock(force = TRUE)
     expect_true(x$.__enclos_env__$private$finalized)
@@ -50,31 +50,31 @@ test_that("cloning", {
 
 test_that("cloning all types", {
     ## pure wi
-    x <- wi(abstracts_stm)
+    x <- wi(abstracts_keyatm)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$wi$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## pure ti
-    x <- ti(abstracts_stm, abstracts$text)
+    x <- ti(abstracts_keyatm, abstracts$text)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## witi
-    x <- witi(abstracts_stm, abstracts$text)
+    x <- witi(abstracts_keyatm, abstracts$text)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
[…]

### 2021-05-31 tests/testthat/test-multiple_objs.R

@@ -11,7 +11,7 @@ genius_topic <- function(obj1) {
 }
 
 test_that("defensive programming", {
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj2 <- clone_oolong(obj1)
     ### Not lock
     expect_error(summarize_oolong(obj1))
@@ -21,10 +21,10 @@ test_that("defensive programming", {
     expect_error(summarize_oolong(obj1, obj2))
     ### Testing checking hash.
     set.seed(1212112)
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj2 <- clone_oolong(obj1)
     set.seed(12121999)
-    obj3 <- create_oolong(abstracts_stm)
+    obj3 <- create_oolong(abstracts_keyatm)
     obj1 <- genius_word(obj1)
     obj2 <- genius_word(obj2)
     obj3 <- genius_word(obj3)
@@ -36,7 +36,7 @@ test_that("defensive programming", {
     ## obj2 is a clone of obj1
     expect_error(summarise_oolong(obj1, obj2), NA)
     ## Warning about premature locking
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj1$lock(force = TRUE)
     expect_warning(summarize_oolong(obj1))
 })

### 2021-05-31 tests/testthat/test-revert.R

@@ -8,7 +8,6 @@ test_that("case in vignette", {
 massive_oolong <- readRDS("../testdata/massive_oolong.RDS")
 all_downloads_rds <- list.files("../testdata/downloaded", full.names = TRUE)
 
-
 test_that("big_revert", {
     expect_error(purrr::map(all_downloads_rds, ~revert_oolong(massive_oolong, .)), NA)
     all_res <- purrr::map(all_downloads_rds, ~revert_oolong(massive_oolong, .))

### 2021-05-31 tests/testthat/test-summarize_oolong.R

@@ -16,7 +16,7 @@ genius_wsi <- function(obj1) {
 }
 
 test_that("Correct UI", {
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj2 <- create_oolong(input_corpus = trump2k, exact_n = 20)
     obj1 <- genius_word(obj1)
     obj1$lock()
@@ -29,7 +29,7 @@ test_that("Correct UI", {
 })
 
 test_that("check_calculation_word_intrusion_multiobject", {
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj2 <- clone_oolong(obj1)
     obj3 <- clone_oolong(obj1)
     ## Mocking coding
@@ -43,7 +43,7 @@ test_that("check_calculation_word_intrusion_multiobject", {
     obj3$lock()
     res <- summarize_oolong(obj1, obj2, obj3)
     expect_length(res$rater_precision, 3)
-    expect_length(res$k_precision, 20)
+    expect_length(res$k_precision, 10)
     ### Single object
     res <- summarize_oolong(obj1)
     expect_length(res$rater_precision, 1)
@@ -51,14 +51,14 @@ test_that("check_calculation_word_intrusion_multiobject", {
 
 
 test_that("check_calculation_word_intrusion_single_object", {
-    obj1 <- create_oolong(abstracts_stm)
+    obj1 <- create_oolong(abstracts_keyatm)
     obj1 <- genius_word(obj1)
     obj1$lock()
     expect_error(summarize_oolong(obj1), NA)
 })
 
 test_that("check_calculation_witi_single_object", {
-    obj1 <- create_oolong(abstracts_stm, abstracts$text)
+    obj1 <- create_oolong(abstracts_keyatm, abstracts$text)
     obj1 <- genius_word(obj1)
     obj1 <- genius_topic(obj1)
     obj1$lock()
@@ -66,7 +66,7 @@ test_that("check_calculation_witi_single_object", {
 })
 
 test_that("check_calculation_witi_multiobject", {
-    obj1 <- create_oolong(abstracts_stm, abstracts$text, exact_n = 10)
+    obj1 <- create_oolong(abstracts_keyatm, abstracts$text, exact_n = 10)
     obj2 <- clone_oolong(obj1)
     obj1 <- genius_word(obj1)
[…]

### 2021-05-31 tests/testthat/test-ui.R

@@ -22,7 +22,6 @@ as.data.frame.tokens <- function(x) {
 }
 abstracts_df <- as.data.frame.tokens(toks_q)
 
-
 test_that("wi basic", {
     skip_on_cran()
     expect_error(wi(abstracts_stm), NA)

### 2021-09-27 overview_gh.Rmd
Update also overview Vig to refect Ying et al.

@@
 | function | purpose                                                                                                                           |
-|---------:|:---------------------------------------------------------------------------------------------------------------------------------------|
+|---------:|:----------------------------------------------------------------------------------------------------------------------------------|
 |   `wi()` | validating a topic model with [word intrusion test](#word-intrusion-test) (Chang et al., 2008)                                    |
-|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test) (Chang et al., 2008; aka "T8WSI" in Ying et al. forthcoming) |
+|   `ti()` | validating a topic model with [topic intrusion test](#topic-intrusion-test) (Chang et al., 2008; aka "T8WSI" in Ying et al. 2021) |
 | `witi()` | validating a topic model with [word intrusion test](#word-intrusion-test) and [topic intrusion test](#topic-intrusion-test)       |
-|  `wsi()` | validating a topic model with [word set intrusion test](#word-set-intrusion-test) (Ying et al. forthcoming)                              |
+|  `wsi()` | validating a topic model with [word set intrusion test](#word-set-intrusion-test) (Ying et al. 2021)                              |
 |   `gs()` | oolong test for [creating gold standard](#creating-gold-standard) (see Song et al., 2020)                                         |
@@
 
-Word set intrusion test is a variant of word intrusion test (Ying et al., forthcoming), in which multiple word sets generated from top terms of one topic are juxtaposed with one intruder word set generated similarly from another topic.
+Word set intrusion test is a variant of word intrusion test (Ying et al., 2021), in which multiple word sets generated from top terms of one topic are juxtaposed with one intruder word set generated similarly from another topic.
 In Ying et al., this test is called "R4WSI" because 4 word sets are displayed.
@@
 [link](https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models)
-2. Ying, L., Montgomery, J. M., & Stewart, B. M. (Forthcoming). Inferring concepts from topics: Towards procedures for validating topics as measures. Political Analysis.
+2.
+Ying, L., Montgomery, J.
+M., & Stewart, B.
+M.
+(2021).
+Inferring concepts from topics: Towards procedures for validating topics as measures.
+Political Analysis.
+[link](https://doi.org/10.1017/pan.2021.33)
 3.

### 2021-12-07 README.Rmd
Bump version; update NEWS; ready for CRAN
Replace png logo with svg logo

@@
 
-# oolong <img src="man/figures/oolong_logo.png" align="right" height="200" />
+# oolong <img src="man/figures/oolong_logo.svg" align="right" height="200" />
 
@@
 Please refer to the [overview](overview_gh.md) for an introduction to this package.
-If you need to deeploy the test online, please refer to the [Deployment Vignette](deploy_gh.md).
+If you need to deploy the test online, please refer to the [Deployment Vignette](deploy_gh.md).
 If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

### 2022-06-28 vig_body.Rmd
Fix #67
Exclude 'abstracts_warplda' from `data` because it is R6. It creates
problem when 'text2vec' (a suggested package) is not installed
together with the main package, e.g. `install.packages("oolong")`.

@@
 $\alpha < 0.001$.
-
-### About Warp LDA
-
-There is a subtle difference between the support for `stm` and for `text2vec`.
-
-`abstracts_warplda` is a Warp LDA object trained with the same dataset as the `abstracts_stm`
-
-```{r warplda}
-abstracts_warplda
-```
-
-All the API endpoints are the same, except the one for the creation of topic intrusion test cases. You must supply also the `input_dfm`.
-
-```{r warplda2}
-### Just word intrusion test.
-oolong_test <- wi(abstracts_warplda, userid = "Lionel")
-oolong_test
-```
-
-```{r warplda3}
-abstracts_dfm
-```
-
-```{r warplda4, , message = FALSE, results = 'hide', warning = FALSE}
-oolong_test <- witi(abstracts_warplda, abstracts$text, input_dfm = abstracts_dfm, userid = "Mara")
-```
-
-```{r warplda5}
-oolong_test
-```
 

### 2023-06-09 README.Rmd
Update GHA and add maintainence update

@@
 [![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
+[![R-CMD-check](https://github.com/chainsawriot/oolong/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/chainsawriot/oolong/actions/workflows/R-CMD-check.yaml)
 <!-- badges: end -->

### 2023-06-09 README.Rmd
Remove Travis badge in README [no ci]

--- 2021-12-07 README.Rmd
@@
 <!-- badges: start -->
-[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
 [![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)

### 2023-06-09 R/oolong_shiny.R
Fix #70 [no ci]

@@ -155,7 +155,7 @@
         })
     } else {
         output$done_button <- shiny::renderUI({
-            shiny::actionButton(inputId = "done", label = "Finish", width = "40%", class = "btn-info btn-lg")
+            shiny::actionButton(inputId = "done", label = "Exit", width = "40%", class = "btn-info btn-lg")
         })
     }
     return(output)
@@ -198,7 +198,7 @@
         })
     } else {
         output$done_button <- shiny::renderUI({
-            shiny::actionButton(inputId = "done", label = "Finish", class = "btn-info btn-lg")
+            shiny::actionButton(inputId = "done", label = "Exit", class = "btn-info btn-lg")
         })
     }
     return(output)
@@ -244,7 +244,7 @@
         })
     }  else {
         output$done_button <- shiny::renderUI({
-            shiny::actionButton(inputId = "done", label = "Finish", class = "btn-info btn-lg")
+            shiny::actionButton(inputId = "done", label = "Exit", class = "btn-info btn-lg")
         })
     }
     return(output)

### 2023-06-09 overview_gh.Rmd

@@
 
-After the coding, you need to first lock the test. Then, you can look at the model precision by printing the oolong test.
+You can pause the test by clicking the "Exit" button.
+Your progress will be recorded in the object.
+If you want to save your progress, just save the object (e.g.
+`saveRDS(oolong_test, "oolong_test.RDS")`).
+To resume the test, launch the test again.
+
+After the coding (all items are coded), you need to press the "Exit" button to quit the coding interface and then lock the test. Then, you can look at the model precision by printing the oolong test.
 

### 2023-08-24 README.Rmd
Switch to semantic branch name

--- 2021-12-07 README.Rmd
@@
 <!-- badges: start -->
-[![Travis build status](https://travis-ci.org/chainsawriot/oolong.svg?branch=master)](https://travis-ci.org/chainsawriot/oolong)
-[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/master/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=master)
+[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/v0.5/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=v0.5)
 [![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)
 [![CRAN status](https://www.r-pkg.org/badges/version/oolong)](https://CRAN.R-project.org/package=oolong)
-[![R-CMD-check](https://github.com/chainsawriot/oolong/workflows/R-CMD-check/badge.svg)](https://github.com/chainsawriot/oolong/actions)
 <!-- badges: end -->

### 2023-10-03 vig_body.Rmd
Correct all docs [no ci]
Fix #76

@@
 
-H0: MP is not better than 1/ n\_top\_terms
+H0: MP is not better than 1/ (n\_top\_terms + 1)
 
-H1: MP is better than 1/ n\_top\_terms
+H1: MP is better than 1/ (n\_top\_terms + 1)
 
@@
 
-Create an oolong object, clone it for another coder. According to Song et al. (Forthcoming), you should at least draw 1% of your data.
+Create an oolong object, clone it for another coder. According to Song et al. (2020), you should at least draw 1% of your data.
 
@@
 Song et al.
-[Forthcoming] suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.
+(2020) suggest Krippendorff's Alpha > 0.7 as an acceptable cut-off.
 

### 2023-12-22 README.Rmd
Transfer ownership

@@
 <!-- badges: start -->
-[![Codecov test coverage](https://codecov.io/gh/chainsawriot/oolong/branch/v0.5/graph/badge.svg)](https://codecov.io/gh/chainsawriot/oolong?branch=v0.5)
+[![Codecov test coverage](https://codecov.io/gh/gesistsa/oolong/branch/v0.5/graph/badge.svg)](https://codecov.io/gh/gesistsa/oolong?branch=v0.5)
 [![joss stataus](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62/status.svg)](https://joss.theoj.org/papers/6e535564e7142d705f4f3d68b18dac62)

### 2023-12-22 deploy_gh.Rmd
Make abstracts_keyatm the 'default' topic model to save space; various fixes for CRAN
Transfer ownership

@@
 author:
-  - Chung-hong Chan ^[University of Mannheim]
+  - Chung-hong Chan ^[GESIS]
 ---
@@
 library(oolong)
-wsi_test <- wsi(abstracts_stm)
+wsi_test <- wsi(abstracts_keyatm)
 wsi_test

### 2023-12-26 README.Rmd
Add pkgdown fix #79
Declutter

@@
 
-# oolong <img src="man/figures/oolong_logo.svg" align="right" height="200" />
+# oolong <img src="man/figures/oolong_logo.png" align="right" width="120" />
 
@@
 
-Please refer to the [overview](overview_gh.md) for an introduction to this package.
-If you need to deploy the test online, please refer to the [Deployment Vignette](deploy_gh.md).
-If you use BTM, please refer to the [BTM Vignette](btm_gh.md).
+Please refer to the [overview](https://gesistsa.github.io/oolong/articles/overview.html) for an introduction to this package.
+If you need to deploy the test online, please refer to the [Deployment Vignette](https://gesistsa.github.io/oolong/articles/deploy.html).
+If you use BTM, please refer to the [BTM Vignette](https://gesistsa.github.io/oolong/articles/btm.html).
 

### 2024-02-09 R/oolong.R
Fix #81

@@ -71,21 +71,21 @@ Oolong_test <- R6::R6Class(
 #' @return an oolong test object.
 #' @examples
 #' ## Creation of oolong test with only word intrusion test
-#' data(abstracts_keyatm)
+#' data(abstracts_seededlda)
 #' data(abstracts)
-#' oolong_test <- wi(input_model = abstracts_keyatm, userid = "Hadley")
+#' oolong_test <- wi(input_model = abstracts_seededlda, userid = "Hadley")
 #' ## Creation of oolong test with both word intrusion test and topic intrusion test
-#' oolong_test <- witi(input_model = abstracts_keyatm, input_corpus = abstracts$text, userid = "Julia")
+#' oolong_test <- witi(input_model = abstracts_seededlda, input_corpus = abstracts$text, userid = "Julia")
 #' ## Creation of oolong test with topic intrusion test
-#' oolong_test <- ti(input_model = abstracts_keyatm, input_corpus = abstracts$text, userid = "Jenny")
+#' oolong_test <- ti(input_model = abstracts_seededlda, input_corpus = abstracts$text, userid = "Jenny")
 #' ## Creation of oolong test with word set intrusion test
-#' oolong_test <- wsi(input_model = abstracts_keyatm, userid = "Garrett")
+#' oolong_test <- wsi(input_model = abstracts_seededlda, userid = "Garrett")
 #' ## Creation of gold standard
 #' oolong_test <- gs(input_corpus = trump2k, userid = "Yihui")
 #' ## Using create_oolong(); not recommended
-#' oolong_test <- create_oolong(input_model = abstracts_keyatm,
+#' oolong_test <- create_oolong(input_model = abstracts_seededlda,
 #' input_corpus = abstracts$text, userid = "JJ")
-#' oolong_test <- create_oolong(input_model = abstracts_keyatm,
+#' oolong_test <- create_oolong(input_model = abstracts_seededlda,
 #' input_corpus = abstracts$text, userid = "Mara", type = "ti")
 #' oolong_test <- create_oolong(input_corpus = abstracts$text, userid = "Winston", type = "gs")
 #' @author Chung-hong Chan, Marius Sältzer

### 2024-02-09 R/oolong_data_misc.R

@@ -17,7 +17,7 @@
 #' These are topic models trained with different topic model packages.
 "abstracts_seededlda"
 
-#' @rdname abstracts_keyatm
+#' @rdname abstracts_seededlda
 "abstracts_btm"
 
 #' AFINN dictionary

### 2024-02-09 tests/testthat/test-defensive_programming.R

@@ -19,10 +19,10 @@ test_that("precondiction", {
 
 test_that("locking", {
     ## premature locking
-    x <- create_oolong(abstracts_keyatm)
+    x <- create_oolong(abstracts_seededlda)
     expect_error(x$lock())
     expect_error(x$lock(force = TRUE), NA)
-    x <- create_oolong(abstracts_keyatm, abstracts$text)
+    x <- create_oolong(abstracts_seededlda, abstracts$text)
     expect_error(x$lock())
     ## error when only word intrusion test is done.
     x <- genius_word(x)
@@ -32,16 +32,16 @@ test_that("locking", {
 })
 
 test_that("cloning", {
-    x <- create_oolong(abstracts_keyatm)
+    x <- create_oolong(abstracts_seededlda)
     expect_error(clone_oolong(x), NA)
     x <- genius_word(x)
     ## Cannot clone a partially coded object.
     expect_error(clone_oolong(x))
-    x <- create_oolong(abstracts_keyatm)
+    x <- create_oolong(abstracts_seededlda)
     x$lock(force = TRUE)
     expect_error(clone_oolong(x))
     ## Cloned object is not sharing the same private space.
-    x <- create_oolong(abstracts_keyatm)
+    x <- create_oolong(abstracts_seededlda)
     y <- clone_oolong(x)
     x$lock(force = TRUE)
     expect_true(x$.__enclos_env__$private$finalized)
@@ -50,31 +50,31 @@ test_that("cloning", {
 
 test_that("cloning all types", {
     ## pure wi
-    x <- wi(abstracts_keyatm)
+    x <- wi(abstracts_seededlda)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$wi$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## pure ti
-    x <- ti(abstracts_keyatm, abstracts$text)
+    x <- ti(abstracts_seededlda, abstracts$text)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
     ## witi
-    x <- witi(abstracts_keyatm, abstracts$text)
+    x <- witi(abstracts_seededlda, abstracts$text)
     expect_error(clone_oolong(x), NA)
     x$.__enclos_env__$private$test_content$ti$answer[1] <- "x"
     expect_error(clone_oolong(x))
[…]

### 2024-02-09 tests/testthat/test-generate_test_content.R

@@ -1,48 +1,48 @@
 ## context("check helper functions")
 
 test_that("generate_test_content", {
-    x <- oolong:::.generate_test_content(abstracts_keyatm)
+    x <- oolong:::.generate_test_content(abstracts_seededlda)
     expect_null(x$ti)
-    x <- oolong:::.generate_test_content(abstracts_keyatm, quanteda::corpus(abstracts$text))
+    x <- oolong:::.generate_test_content(abstracts_seededlda, quanteda::corpus(abstracts$text))
     expect_false(is.null(x$ti))
 })
 
 test_that("check_complete", {
-    x <- oolong:::.generate_test_content(abstracts_keyatm)
+    x <- oolong:::.generate_test_content(abstracts_seededlda)
     expect_false(oolong:::.check_test_content_complete(x))
     x$wi$answer <- 1
     expect_true(oolong:::.check_test_content_complete(x))
-    y <- oolong:::.generate_test_content(abstracts_keyatm, abstracts$text)
+    y <- oolong:::.generate_test_content(abstracts_seededlda, abstracts$text)
     expect_false(oolong:::.check_test_content_complete(y))
     y$ti$answer <- 1
     expect_false(oolong:::.check_test_content_complete(y))
     y$wi$answer <- 1
     expect_true(oolong:::.check_test_content_complete(y))
-    z <- create_oolong(abstracts_keyatm)
+    z <- create_oolong(abstracts_seededlda)
     expect_error(z$lock())
 })
 
 test_that("K is too small", {
-    expect_error(oolong:::.generate_test_content(abstracts_keyatm, abstracts$text, n_top_topics = 20))
+    expect_error(oolong:::.generate_test_content(abstracts_seededlda, abstracts$text, n_top_topics = 20))
 })
 
 test_that("n_top_terms is considered #29", {
-    z <- oolong:::.generate_test_content(abstracts_keyatm, abstracts$text, n_top_terms = 10)
+    z <- oolong:::.generate_test_content(abstracts_seededlda, abstracts$text, n_top_terms = 10)
     expect_equal(length(z$wi$candidates[[1]]), 11)
 })
 
 test_that("generate_test_content type", {
-    x <- oolong:::.generate_test_content(abstracts_keyatm, input_corpus = abstracts$text, type = 'wi')
[…]

### 2024-02-09 tests/testthat/test-gold-standard.R

@@ -31,6 +31,6 @@ test_that("locking", {
 })
 
 test_that("type override input_model", {
-    x <- create_oolong(abstracts_keyatm, abstracts$text, type = "gs")
+    x <- create_oolong(abstracts_seededlda, abstracts$text, type = "gs")
     expect_true("oolong_test_gs" %in% class(x))
 })

### 2024-02-09 tests/testthat/test-seededlda.R

@@ -13,8 +13,6 @@ genius_topic <- function(obj1) {
 ## seeded lda
 
 test_that("seeded lda: generate_test_content", {
-    skip_on_cran()
-    skip_if_not(exists("abstracts_seededlda"))
     x <- oolong:::.generate_test_content(abstracts_seededlda)
     expect_null(x$ti)
     x <- oolong:::.generate_test_content(abstracts_seededlda, quanteda::corpus(abstracts$text))
@@ -22,8 +20,6 @@ test_that("seeded lda: generate_test_content", {
 })
 
 test_that("seeded lda: check_complete", {
-    skip_on_cran()
-    skip_if_not(exists("abstracts_seededlda"))
     x <- oolong:::.generate_test_content(abstracts_seededlda)
     expect_false(oolong:::.check_test_content_complete(x))
     x$wi$answer <- 1
@@ -40,7 +36,7 @@ test_that("seeded lda: check_complete", {
 
 test_that("unseeded lda: generate_test_content", {
     skip_on_cran()
-    skip_if_not(exists("abstracts_seededlda"))
+    skip_if_not(exists("abstracts_unseededlda"))
     x <- oolong:::.generate_test_content(abstracts_unseededlda)
     expect_null(x$ti)
     x <- oolong:::.generate_test_content(abstracts_unseededlda, quanteda::corpus(abstracts$text))
@@ -49,7 +45,7 @@ test_that("unseeded lda: generate_test_content", {
 
 test_that("unseeded lda: check_complete", {
     skip_on_cran()
-    skip_if_not(exists("abstracts_seededlda"))
+    skip_if_not(exists("abstracts_unseededlda"))
     x <- oolong:::.generate_test_content(abstracts_unseededlda)
     expect_false(oolong:::.check_test_content_complete(x))
     x$wi$answer <- 1
@@ -66,7 +62,7 @@ test_that("unseeded lda: check_complete", {
 
 ## ui
 test_that("UI", {
-    skip_if_not(exists("abstracts_seededlda"))
+    skip_if_not(exists("abstracts_unseededlda"))
     expect_error(witi(abstracts_seededlda, abstracts$text), NA)
     expect_error(witi(abstracts_unseededlda, abstracts$text), NA)
     expect_error(ti(abstracts_seededlda, abstracts$text), NA)

### 2024-02-09 tests/testthat/apps/ti/app.R
Fix #81 (#84)
* WIP

* Fix #81

* Fix doc

* Fix test

@@ -1,5 +1,5 @@
 library(oolong)
 
-x <- ti(abstracts_keyatm, abstracts$text, exact_n = 10)
+x <- ti(abstracts_seededlda, abstracts$text, exact_n = 10)
 
 x$do_topic_intrusion_test()

### 2024-02-09 tests/testthat/apps/wi/app.R

@@ -1,5 +1,5 @@
 library(oolong)
 
-x <- wi(abstracts_keyatm)
+x <- wi(abstracts_seededlda)
 
 x$do_word_intrusion_test()

### 2024-02-09 tests/testthat/test-multiple_objs.R

@@ -11,7 +11,7 @@ genius_topic <- function(obj1) {
 }
 
 test_that("defensive programming", {
-    obj1 <- create_oolong(abstracts_keyatm)
+    obj1 <- create_oolong(abstracts_seededlda)
     obj2 <- clone_oolong(obj1)
     ### Not lock
     expect_error(summarize_oolong(obj1))
@@ -21,10 +21,10 @@ test_that("defensive programming", {
     expect_error(summarize_oolong(obj1, obj2))
     ### Testing checking hash.
     set.seed(1212112)
-    obj1 <- create_oolong(abstracts_keyatm)
+    obj1 <- create_oolong(abstracts_seededlda)
     obj2 <- clone_oolong(obj1)
     set.seed(12121999)
-    obj3 <- create_oolong(abstracts_keyatm)
+    obj3 <- create_oolong(abstracts_seededlda)
     obj1 <- genius_word(obj1)
     obj2 <- genius_word(obj2)
     obj3 <- genius_word(obj3)
@@ -36,8 +36,7 @@ test_that("defensive programming", {
     ## obj2 is a clone of obj1
     expect_error(summarise_oolong(obj1, obj2), NA)
     ## Warning about premature locking
-    obj1 <- create_oolong(abstracts_keyatm)
+    obj1 <- create_oolong(abstracts_seededlda)
     obj1$lock(force = TRUE)
     expect_warning(summarize_oolong(obj1))
 })
-

### 2024-06-17 methodshub.qmd
MH Example

---
title: oolong - Create Validation Tests for Automated Content Analysis
format:
  html:
    embed-resources: true
  gfm: default
---

## Description

<!-- - Provide a brief and clear description of the method, its purpose, and what it aims to achieve. Add a link to a related paper from social science domain and show how your method can be applied to solve that research question.   -->

Intended to create standard human-in-the-loop validity tests for typical automated content analysis such as topic modeling and dictionary-based methods. This package offers a standard workflow with functions to prepare, administer and evaluate a human-in-the-loop validity test. This package provides functions for validating topic models using word intrusion, topic intrusion (Chang et al. 2009,  <https://papers.nips.cc/paper/3700-reading-tea-leaves-how-humans-interpret-topic-models>) and word set intrusion (Ying et al. 2021) [<doi:10.1017/pan.2021.33>](https://doi.org/10.1017/pan.2021.33) tests. This package also provides functions for generating gold-standard data which are useful for validating dictionary-based methods. The default settings of all generated tests match those suggested in Chang et al. (2009) and Song et al. (2020) [<doi:10.1080/10584609.2020.1723752>](https://doi.org/10.1080/10584609.2020.1723752).

## Keywords

* Validity
* Text Analysis
* Topic Model

## Science Usecase(s)

<!-- - Include usecases from social sciences that would make this method applicable in a certain scenario.  -->
<!-- The use cases or research questions mentioned should arise from the latest social science literature cited in the description. -->

This package was used in the literature to valid topic models and prediction models trained on text data, e.g. [Rauchfleisch et al. (2023)](10.1080/17512786.2022.2110928), [Rothut, et al. (2023)](https://doi.org/10.1177/14614448231164409), [Eisele, et al. (2023)](https://doi.org/10.1080/19312458.2023.2230560).

## Repository structure

This repository follows [the standard structure of an R package](https://cran.r-project.org/doc/FAQ/R-exts.html#Package-structure).

## Environment Setup

With R installed:

```r
install.packages("oolong")
```

<!-- ## Hardware Requirements (Optional) -->
<!-- - The hardware requirements may be needed in specific cases when a method is known to require more memory/compute power.  -->
<!-- - The method need to be executed on a specific architecture (GPUs, Hadoop cluster etc.) -->

## Input Data

<!-- - The input data has to be a Digital Behavioral Data (DBD) Dataset -->
<!-- - You can provide link to a public DBD dataset. GESIS DBD datasets (https://www.gesis.org/en/institute/digital-behavioral-data) -->

The input data has to be a topic model or prediction model trained on text data. For example, one can train a topic model from the text data (tweets from Donald trump) included in the package by:

```r
library(seededlda)
library(quanteda)
trump_corpus <- corpus(trump2k)
tokens(trump_corpus, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE,
       split_hyphens = TRUE, remove_url = TRUE) %>% tokens_tolower() %>%
    tokens_remove(stopwords("en")) %>% tokens_remove("@*")  -> trump_toks

model <- textmodel_lda(x = dfm(trump_toks), k = 8, verbose = TRUE)
```

## Sample Input and Output Data

<!-- - Show how the input data looks like through few sample instances -->
<!-- - Providing a sample output on the sample input to help cross check  -->

A sample input is a model trained on text data, e.g.

```{r}
#| message: false
library(oolong)
library(seededlda)
abstracts_seededlda
```

The sample output is an oolong S3 object.

## How to Use

Please refer to the [overview of this package](https://gesistsa.github.io/oolong/articles/overview.html) for a comprehensive introduction of all test types.

Suppose there is a topic model trained on some text data called `abstracts_seededlda`, which is included in the package.

```{r}
library(oolong)
abstracts_seededlda
```

Suppose one would like to conduct a word intrusion test (Chang et al. 2009) to validate this topic model. This test can be generated by the `wi()` function.

```{r}
oolong_test <- wi(abstracts_seededlda, userid = "Hadley")
oolong_test
```

One can then conduct the test following the instruction displayed, i.e. `oolong_test$$do_word_intrusion_test()`.

```r
oolong_test$do_word_intrusion_test()
```

One should see a graphic interface like the following and conduct the test.

<img src="man/figures/oolong_demo.gif" align="center" height="400" />

After the test, one can finalize the test by locking the test.

```{r}
#| include: false
### Mock this process
oolong_test$.__enclos_env__$private$test_content$wi$answer <- oolong_test$.__enclos_env__$private$test_content$wi$intruder
oolong_test$.__enclos_env__$private$test_content$wi$answer[1] <- "wronganswer"
```

```{r}
oolong_test$lock()
```

And then obtain the result of the test. For example:

```{r}
oolong_test
```

## Contact Details

Maintainer: Chung-hong Chan <chainsawtiney@gmail.com>

Issue Tracker: [https://github.com/gesistsa/oolong/issues](https://github.com/gesistsa/oolong/issues)

## Publication

1. Chan, C. H., & Sältzer, M. (2020). oolong: An R package for validating automated content analysis tools. The Journal of Open Source Software: JOSS, 5(55), 2461. https:://doi.org/10.21105/joss.02461

<!-- ## Acknowledgements -->
<!-- - Acknowledgements if any -->

<!-- ## Disclaimer -->
<!-- - Add any disclaimers, legal notices, or usage restrictions for the method, if necessary. -->
